---
title: "beach_fib_average_annual"
author: "Tina Tran"
date: "November 18, 2025"
format: html
editor: visual
format: 
  html:
    embed-resources: true
    code-fold: true
    toc: true
execute:
  warning: false
  message: false
theme: "minty"
df-print: kable
---

# Exploratory Data Analysis For Beach FIB Only

This document includes the exploratory data analysis (EDA) of beach FIB concentrations on an annual and monthly basis.

```{r, message = false, warning = false}
# Load libraries 
library(dplyr)
library(ggplot2)
library(tidyverse)
library(ggridges)
library(here)
library(lubridate)
library(slider)
library(scales)
library(janitor)
```

## **Heal The Bay Brand Colors** 

This code creates a color gradient for the graphs based on the Heal The Bay (HTB)'s brand colors. It creates 18 types of colors based on the 5 given brand colors.

```{r, message = false, warning = false}
htb_colors <- c(
  "E. Coli" = "#40B4EB",
  "Enterococcus" = "#2D94C8",
  "Total Coliforms" = "#8FA9B9",
  "Fecal Coliforms" = "#1479A9")
```

# Annual Beach FIB EDA

## **Mutating Beach Data Frames**

The data was mutated to add a year and month column for analysis. The mean, median, and variance was calculated for the log 10 transformed FIB concentrations grouped by each motioning station and year.

```{r}
# Read the data file
beach_data_2014_2024 <- read.csv(here("data","clean_master_beach_data_2014_2024.csv")) 

# Mutate the Beach Data 
beach_clean <- beach_data_2014_2024 |>
  mutate(result_log = log10(result), # log 10 transform the data
         sampledate = as.Date(sampledate), # change from chr to date
          year = year(sampledate), 
          month = month(sampledate, label = TRUE, abbr = TRUE))

# Creating a summary of the annual mean log results of each fib parameter for each station
beach_annual <- beach_clean |>
  group_by(stationname, parameter, year) |>
  summarise(
    annual_mean_log = mean(result_log, na.rm = TRUE),
    annual_median_log = median(result_log, na.rm = TRUE),
    annual_variance_log = var(result_log, na.rm = TRUE),
    n_samples = n(),
    .groups = "drop")
```

```{r}
# Read in the Precipitation Data

```

## Mean Annual Average FIB Concentrations

### Annual Average E.Coli Trends Across All Sites

```{r}
# Create a new dataframe for only yearly e.coli concentrations
annual_ecoli <- beach_annual |>
  filter(parameter == "E. Coli")

# Create box plot
beach_ecoli_annual_plot <- ggplot(annual_ecoli,
  aes(x = factor(year), y = annual_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Average E. Coli Concentrations Across All Sites",
    x = "Year",
    y = "Annual Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_ecoli_annual_plot

# Save the Plot 
#ggsave(here("outputs", "beach_fib_average_annually", #"beach_ecoli_annual_plot.png"),
#  plot = beach_ecoli_annual_plot, width = 15, height = 6, dpi = 400)
```

### Annual Average Enterococcus Trends Across All Sites

```{r}
annual_enterococcus <- beach_annual |>
  filter(parameter == "Enterococcus")

# Create box plot
beach_entero_annual_plot <- ggplot(annual_enterococcus,
  aes(x = factor(year), y = annual_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Average Enterococcus Concentrations Across All Sites",
    x = "Year",
    y = "Annual Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_entero_annual_plot

# Save the Plot 
#ggsave(here("outputs", "beach_fib_average_annually", #"beach_entero_annual_plot.png"),
#  plot = beach_entero_annual_plot, width = 15, height = 6, dpi = 400)
```

### Annual Average Total Coliforms Trends Across All Sites

```{r}
annual_total_coliforms <- beach_annual |>
  filter(parameter == "Total Coliforms")

# Create box plot
beach_tot_annual_plot <- ggplot(annual_total_coliforms,
  aes(x = factor(year), y = annual_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Average Total Coliforms Concentrations Across All Sites",
    x = "Year",
    y = "Annual Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_tot_annual_plot

# Save the Plot 
#ggsave(here("outputs", "beach_fib_average_annually", #"beach_tot_annual_plot.png"),
#  plot = beach_tot_annual_plot, width = 15, height = 6, dpi = 400)
```

### Annual Average Fecal Coliforms Trends Across All Sites

```{r}
annual_fecal_coliforms <- beach_annual |>
  filter(parameter == "Fecal Coliforms")

# Create box plot
beach_fec_annual_plot <- ggplot(annual_fecal_coliforms,
  aes(x = factor(year), y = annual_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Average Fecal Coliforms Concentrations Across All Sites",
    x = "Year",
    y = "Annual Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_fec_annual_plot

# Save the Plot 
#ggsave(here("outputs", "beach_fib_average_annually", #"beach_fec_annual_plot.png"),
#  plot = beach_fec_annual_plot, width = 15, height = 6, dpi = 400)
```

# Beach FIB Average Monthly on a Year-to-Year Basis

Average all the beaches each month for each year. Then analyze on a year to year basis and have it be 1 year at a time.

## **2014 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2014 <- beach_clean |> 
  filter(year == 2014)

# Create the average values of each month in the year 2014
beach_monthly_2014 <- beach_2014 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2014_box <- ggplot(beach_monthly_2014,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2014)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2014_box

# Save the Plot 
#ggsave(filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2014_plot.png"),
#  plot = beach_monthly_2014_box, width = 21, height = 12, dpi = 400)
```

## **2015 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2015 <- beach_clean |> 
  filter(year == 2015)

# Create the average values of each month in the year 2014
beach_monthly_2015 <- beach_2015 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2015_box <- ggplot(beach_monthly_2015,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2015)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2015_box

# Save the Plot 
#ggsave(filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2015_plot.png"),
#  plot = beach_monthly_2015_box, width = 21, height = 12, dpi = 400)
```

## **2016 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2016 <- beach_clean |> 
  filter(year == 2016)

# Create the average values of each month in the year 2014
beach_monthly_2016 <- beach_2016 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2016_box <- ggplot(beach_monthly_2016,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2016)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2016_box

# Save the Plot 
#ggsave(filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2016_plot.png"),
#  plot = beach_monthly_2016_box, width = 21, height = 12, dpi = 400)
```

## **2017 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2017 <- beach_clean |> 
  filter(year == 2017)

# Create the average values of each month in the year 2014
beach_monthly_2017 <- beach_2017 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2017_box <- ggplot(beach_monthly_2017,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2017)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2017_box

# Save the Plot 
#ggsave(filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2017_plot.png"),
#  plot = beach_monthly_2017_box, width = 21, height = 12, dpi = 400)
```

## **2018 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2018 <- beach_clean |> 
  filter(year == 2018)

# Create the average values of each month in the year 2014
beach_monthly_2018 <- beach_2018 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2018_box <- ggplot(beach_monthly_2018,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2018)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2018_box

# Save the Plot 
#ggsave(filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2018_plot.png"),
#  plot = beach_monthly_2018_box, width = 21, height = 12, dpi = 400)
```

## **2019 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2019 <- beach_clean |> 
  filter(year == 2019)

# Create the average values of each month in the year 2014
beach_monthly_2019 <- beach_2019 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2019_box <- ggplot(beach_monthly_2019,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2019)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2019_box

# Save the Plot 
#ggsave(filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2019_plot.png"),
#  plot = beach_monthly_2019_box, width = 21, height = 12, dpi = 400)
```

## **2020 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2020 <- beach_clean |> 
  filter(year == 2020)

# Create the average values of each month in the year 2014
beach_monthly_2020 <- beach_2020 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2020_box <- ggplot(beach_monthly_2020,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2020)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2020_box

# Save the Plot 
#ggsave( filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2020_plot.png"),
#  plot = beach_monthly_2020_box, width = 21, height = 12, dpi = 400)
```

## **2021 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2021 <- beach_clean |> 
  filter(year == 2021)

# Create the average values of each month in the year 2014
beach_monthly_2021 <- beach_2021 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2021_box <- ggplot(beach_monthly_2021,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2021)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2021_box

# Save the Plot 
#ggsave( filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2021_plot.png"),
#  plot = beach_monthly_2021_box, width = 21, height = 12, dpi = 400)
```

## **2022 Yearly Box Plot**

### **Mean**

```{r}
#Create New Data Frame 
beach_2022 <- beach_clean |> 
  filter(year == 2022)

# Create the average values of each month in the year 2014
beach_monthly_2022 <- beach_2022 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)

```

```{r}
# Create box plot
beach_monthly_2022_box <- ggplot(beach_monthly_2022,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2022)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2022_box

# Save the Plot 
#ggsave( filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2022_plot.png"),
#  plot = beach_monthly_2022_box, width = 21, height = 12, dpi = 400)
```

## **2023 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2023 <- beach_clean |> 
  filter(year == 2023)

# Create the average values of each month in the year 2014
beach_monthly_2023 <- beach_2023 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2023_box <- ggplot(beach_monthly_2023,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2023)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2023_box

# Save the Plot 
#ggsave( filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2023_plot.png"),
#  plot = beach_monthly_2023_box, width = 21, height = 12, dpi = 400)
```

## **2024 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2024 <- beach_clean |> 
  filter(year == 2024)

# Create the average values of each month in the year 2014
beach_monthly_2024 <- beach_2024 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2024_box <- ggplot(beach_monthly_2024,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2024)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2024_box

# Save the Plot 
#ggsave( filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2024_plot.png"),
#  plot = beach_monthly_2024_box, width = 21, height = 12, dpi = 400)
```
