---
title: "EDA For Beach FIB V Rain"
author: "Tina Tran"
date: "November 19, 2025"
format: html
editor: visual
format: 
  html:
    embed-resources: true
    code-fold: true
    toc: true
execute:
  warning: false
  message: false
theme: "minty"
df-print: kable
---

# Exploratory Data Analysis For Beach FIB v Rain

```{r}
# Load libraries 
library(dplyr)
library(ggplot2)
library(tidyverse)
library(ggridges)
library(here)
library(lubridate)
library(slider)
library(scales)
library(janitor)
library(patchwork)
```

## **Heal The Bay Brand Colors**

This code assigns the the following colors to each FIB parameter: E. Coli, Enterococcus, Total Coliforms, and Fecal Coliforms. It also creates another data frame to create the HTB gradient.

```{r}
htb_colors <- c(
  "E. Coli" = "#40B4EB",
  "Enterococcus" = "#2D94C8",
  "Total Coliforms" = "#8FA9B9",
  "Fecal Coliforms" = "#1479A9")

# HTB Gradient 
htb_gradient <- colorRampPalette(htb_colors)(11)
htb_gradient 


# Color Gradient for Graphs that are not FIB Parameters
htb_brand_colors <- colorRampPalette(c("#263746", "#005CB9", "#40B4E5", "#00B6B6", "#8ACFCF"))
htb_brand_colors(34)
```

## Mutate FIB Concentration & Precipitation Data

```{r}
# Read the data file
beach_data_2014_2024 <- read.csv(here("data","clean_master_beach_data_2014_2024.csv")) 

# Mutate the Beach Data 
beach_clean <- beach_data_2014_2024 |>
  mutate(result_log = log10(result), # log 10 transform the data
         sample_date = as.Date(sample_date), # change from chr to date
          year = year(sample_date),  # extract year from sampledate
          month = month(sample_date, label = TRUE, abbr = TRUE)) # extract month from sampledate

# Creating a summary of the annual log results of each fib parameter for each station
beach_annual <- beach_clean |>
  group_by(station_name, parameter, year, beach_name) |>
  summarise(
    annual_mean_log = mean(result_log, na.rm = TRUE),
    annual_median_log = median(result_log, na.rm = TRUE),
    annual_variance_log = var(result_log, na.rm = TRUE),
    n_samples = n(),
    .groups = "drop")

# Count Sample numbers for 99 stations
station_count <- beach_clean |>
  count(station_name)
```

```{r}
# Read in the Precipitation Data
precip_2014_2024 <- read.csv(here("data","precipitation_clean_2014_2024.csv")) 

# Mutate the Precip Data
precip_clean <- precip_2014_2024 |>
  mutate(date = as.Date(date), # Change date from chr to date
         year = year(date), # extract the year from the date
         day = day(date), # extract the day from the date
         month = month(date, label = TRUE, abbr = TRUE), # extract month from the date
         wet = prcp_in > 0.1) # defines wet weather as >0.1 inches

# Separate wet vs dry data
wet_weather <- precip_clean |>  filter(wet == TRUE)

dry_weather <- precip_clean |> filter(wet == FALSE)


# Total the Annual Precipitation Each Year 
precip_annual <- precip_clean |>
  group_by(year) |>
  summarise(
    total_rain_in = sum(prcp_in, na.rm = TRUE),
    .groups = "drop")

# Join the Precipi Data with the FIB Concentrations Annual Data
join_prcp_fib_data <- beach_annual |>
  left_join(precip_annual, by = "year")


join_fib_prcp_bin <- join_prcp_fib_data |>
  mutate(rain_bin = cut(total_rain_in,
                        breaks = 4, 
                        labels = c("Low", "Moderate", "High", "Very High")))


# Create a summary of the precipitation for each year 
rain_summary_table <- precip_clean|>
  group_by(year) |>
summarize(var=var(prcp_in),
            min_rain = min(prcp_in),
            IQ25_rain = quantile(prcp_in, probs = 0.25), 
            mean_rain = mean(prcp_in),
            median_rain = median(prcp_in),
            IQ75_rain = quantile(prcp_in, probs = 0.75),
            max_rain = max(prcp_in))
rain_summary_table 
```

# Precipitation

## Total Annual Precipitation

This code calculates the total annual rainfall in each year from 2014-2024.

```{r}
# Calculate the average total rainfall over the 10 years
mean_total_rain <- precip_annual |> 
  summarise(mean_rain_event = mean(total_rain_in), na.rm = TRUE) |>
  pull(mean_rain_event) # this extracts the numeric valye of the mean rain event so that it can be plotted in ggplot

# Plot the total precipitation for each year 
rain_bar <- ggplot(precip_annual, 
                   aes(x = factor(year), y = total_rain_in)) +
  geom_col(fill = "#1479A9") + 
  geom_hline(yintercept = mean_total_rain, linetype = "dashed", linewidth = 1, color = "black")+ # average 10-yr rain
  labs(#title = "Total Annual Precipitation (2014–2024)",
    x = "Year",
    y = "Total Rainfall (inches)") +
  theme_minimal(base_size = 14)+
  theme(plot.title = element_text(face = "bold", hjust = 0.5),
    axis.title.x = element_text(face = "bold", size = 12),
    axis.title.y = element_text(face = "bold"),
    legend.position = "none", 
    panel.grid = element_blank())
print(rain_bar)

# Calculate the overall mean precipitation for all 10 years
overall_mean_rain <- precip_clean |> 
  summarise(mean_rain_Event = mean(prcp_in), na.rm = TRUE)
overall_mean_rain

# Save the plot
  # Save the PNG 
#ggsave(filename = here("outputs", "precip_only", 
#                       "total_rain_bar.png"),
#  plot = rain_bar, width = 9, height = 5,dpi = 400)

```

## Monthly Average Rainfall

This code will sum the amount of rainfall for each month for each year from 2014-2024.

```{r}
# Create the data frame
precip_monthly <- precip_clean |>
  group_by(year,month) |> # group the data by year and month
  summarise(total_rain_in = sum(prcp_in, na.rm = TRUE), # sum the precip total
    .groups = "drop")

# Creating the graph for the data
precip_monthly_plot <- ggplot(precip_monthly,
  aes(x = total_rain_in, fill = factor(year), y = factor(year))) +
  geom_col() +
  facet_wrap(~ month, ncol = 12) +
  scale_fill_manual(values = htb_gradient) +
  labs(x = "Total Rainfall (inches)", y = "Year",
    fill = "Year") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(angle = 90, vjust = 0.5),
    panel.grid = element_blank())
precip_monthly_plot

# Save the bar graph
#ggsave(here("outputs", "precip_only", "monthly_precip.png"), 
     # plot = precip_monthly_plot, width = 14, height = 8, dpi = 500)
```

## Wet Period Analysis

**Read the Wet Period & Dry Period Data Into the Script**

```{r}
# Wet Period Dataset
# Read the file
beach_data_wet_period <- read.csv(here("data","beach_data_wet_period.csv")) 

# Edit the data
beach_wet_fib <- beach_data_wet_period |>
  mutate(result_log = log10(result), # log10 the results
         sample_date = as.numeric(as.Date(sample_date)), # make sample date into a date
         year = year(as.Date(sample_date))) # extract year out of the sample_date

# Double checking how many unique parameters there are (4 total)
unique(beach_wet_fib$parameter)



# Dry Period Dataset
# Read the file
beach_data_dry_period <- read.csv(here("data","beach_data_dry_period.csv")) 

# Edit the data
beach_dry_fib <- beach_data_dry_period |>
  mutate(result_log = log10(result), # log10 the results
         sample_date = as.numeric(as.Date(sample_date)),  # make sample date into a date
         year = year(as.Date(sample_date))) # extract year out of the sample_date

# Double checking how many unique parameters there are (4 total)
unique(beach_dry_fib$parameter)
```

### **Enterococcus EDA - Wet**

```{r}
# Create a separate data set for Enterococcus
wet_fib_enterococcus <- beach_wet_fib |>
  filter(parameter == "Enterococcus")

# Checking how many unit types exist 
unique(wet_fib_enterococcus$unit)
# 2 exist - "MPN/100ml" "CFU/100ml"

# Checking to see how many beaches sampled for Enterococcus
unique(wet_fib_enterococcus$beach_name)
# 34 beaches appear


# Box and Whisker Plot for Enterococcus only For Each Beach
wet_fib_entero_plot <- wet_fib_enterococcus |>
  ggplot(aes(x = result_log, y = beach_name, fill = beach_name)) +
  geom_boxplot(show.legend = FALSE) + # no legend
  scale_fill_manual(values = htb_brand_colors(length(unique(wet_fib_enterococcus$beach_name)))) + # fill based on brand colors 
  facet_wrap(~ year, ncol = 11) + # have 11 columns for each year
  labs(title = "Wet Period Enterococcus Concentrations", 
       x = "Log 10 Transformed Enterococcus Concentration",
       y = "Beach Name") +
  theme_minimal(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"), # bold the text
    panel.grid.minor = element_blank(), # remove the minor grid marks
    panel.grid.major.y = element_blank(), # remove the major grid marks for y-axis
    panel.background = element_rect(fill = "white", color = NA))
print(wet_fib_entero_plot)

# Save the plot
# ggsave(here("outputs", "wet_fib_entero_plot.png"), width = 25, height = 15, dpi = 400)
```

### **E.Coli EDA - Wet**

```{r}
# Created a separate data frame for E.Coli Data
wet_fib_ecoli <- beach_wet_fib |>
  filter(parameter == "E. Coli") 

# Checking how many unit types exist 
unique(wet_fib_ecoli$unit)
# 1 exist - "MPN/100ml" 

# Check How Many Beaches Sampled E.Coli 
unique(wet_fib_ecoli$beach_name)
# 28 beaches that have e.coli data 

# Box and Whisker Plot for E. Coli only For Each Beach
wet_fib_ecoli_plot <- wet_fib_ecoli |>
  ggplot(aes(x = result_log, y = beach_name, fill = beach_name)) +
  geom_boxplot(show.legend = FALSE) + # no legend
  scale_fill_manual(values = htb_brand_colors(length(unique(wet_fib_ecoli$beach_name)))) + # fill based on brand colors 
  facet_wrap(~ year, ncol = 11) + # have 11 columns for each year
  labs(title = "Wet Period E. Coli Concentrations",
       x = "Log 10 Transformed E.Coli Concentration", 
       y = "Beach Name") +
  theme_minimal(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"), # bold the text
    panel.grid.minor = element_blank(), # remove the minor grid marks
    panel.grid.major.y = element_blank(), # remove the major grid marks for y-axis
    panel.background = element_rect(fill = "white", color = NA))
print(wet_fib_ecoli_plot)

# Save the plot
# ggsave(here("outputs", "wet_fib_ecoli_plot.png"), width = 25, height = 15, dpi = 400)
```

### **Total Coliforms EDA - Wet**

```{r}
# Created a separate data frame for Total Coliforms data
wet_fib_total_coliforms <- beach_wet_fib |>
  filter(parameter == "Total Coliforms") 

# Checking how many unit types exist 
unique(wet_fib_total_coliforms$unit)
# 2 exist - "MPN/100ml" "CFU/100ml" 

# Check How Many Beaches Sampled Total Coliforms 
unique(wet_fib_total_coliforms$beach_name)
# 34 beaches that have total coliforms data 

# Box and Whisker Plot for Total Coliforms only For Each Beach
wet_fib_tot_coli_plot <- wet_fib_total_coliforms |>
  ggplot(aes(x = result_log, y = beach_name,fill = beach_name)) +
  geom_boxplot(show.legend = FALSE) + # no legend
  scale_fill_manual(values = htb_brand_colors(length(unique(wet_fib_total_coliforms$beach_name)))) + # fill based on brand colors 
  facet_wrap(~ year, ncol = 11) + # have 11 columns for each year
  labs(title = "Wet Period Total Coliforms Concentrations",
  x = "Log 10 Transformed Total Coliforms Concentration",
  y = "Beach Name") +
  theme_minimal(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"), # bold the text
    panel.grid.minor = element_blank(), # remove the minor grid marks
    panel.grid.major.y = element_blank(), # remove the major grid marks for y-axis
    panel.background = element_rect(fill = "white", color = NA))
print(wet_fib_tot_coli_plot)

# Save the plot
#ggsave(here("outputs", "wet_fib_tot_coli_plot.png"), width = 25, height = 15, dpi = 400)
```

### **Fecal Coliforms EDA - Wet**

```{r}
# Created a separate data frame for Fecal Coliforms data 
wet_fib_fecal_coliforms <- beach_wet_fib |>
  filter(parameter == "Fecal Coliforms") 

# Checking how many unit types exist 
unique(wet_fib_fecal_coliforms$unit)
# 2 exist - "MPN/100ml" "CFU/100ml" 

# Check How Many Beaches Sampled Fecal Coliforms
unique(wet_fib_fecal_coliforms$beach_name)
# 33 beaches that have total coliforms data 

# Box and Whisker Plot for Fecal Coliforms only For Each Beach
wet_fib_fec_coli_plot <- wet_fib_fecal_coliforms |>
  ggplot(aes(x = result_log, y = beach_name,fill = beach_name)) + 
  geom_boxplot(show.legend = FALSE) + # no legend
  scale_fill_manual(values = htb_brand_colors(length(unique(wet_fib_fecal_coliforms$beach_name)))) + # fill based on brand colors 
  facet_wrap(~ year, ncol = 11) + # have 11 columns for each year
  labs(title = "Wet Period Fecal Coliforms Concentrations",
       x = "Log 10 Transformed Fecal Coliforms Concentration",
    y = "Beach Name") +
  theme_minimal(base_size = 14) +
  theme(
   strip.text = element_text(face = "bold"), # bold the text
    panel.grid.minor = element_blank(), # remove the minor grid marks
    panel.grid.major.y = element_blank(), # remove the major grid marks for y-axis
    panel.background = element_rect(fill = "white", color = NA))
print(wet_fib_fec_coli_plot)

# Save the plot
#ggsave(here("outputs", "wet_fib_fec_coli_plot.png"), width = 25, height = 15, dpi = 400)
```

## Dry Period Analysis

### **Enterococcus EDA - Dry**

```{r}
# Create a separate data set for Enterococcus Data
dry_fib_enterococcus <- beach_dry_fib |>
  filter(parameter == "Enterococcus")

# Checking how many unit types exist 
unique(dry_fib_enterococcus$unit)
# 2 exist - "MPN/100ml" "CFU/100ml"

# Checking to see how many beaches sampled for Enterococcus
unique(dry_fib_enterococcus$beach_name)
# 34 beaches appear


# Box and Whisker Plot for Enterococcus only For Each Beach
dry_fib_entero_plot <- dry_fib_enterococcus |>
  ggplot(aes(x = result_log, y = beach_name,fill = beach_name)) +
  geom_boxplot(show.legend = FALSE) + # no legend
  scale_fill_manual(values = htb_brand_colors(length(unique(dry_fib_enterococcus$beach_name)))) + # fill based on brand colors 
  facet_wrap(~ year, ncol = 11) + # have 11 columns for each year
  labs(title = "Dry Period Enterococcus Concentrations",
       x = "Log 10 Transformed Enterococcus Concentration",
    y = "Beach Name") +
  theme_minimal(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"), # bold the text
    panel.grid.minor = element_blank(), # remove the minor grid marks
    panel.grid.major.y = element_blank(), # remove the major grid marks for y-axis
    panel.background = element_rect(fill = "white", color = NA))
print(dry_fib_entero_plot)

# Save the plot
#ggsave(here("outputs", "dry_fib_entero_plot.png"), width = 25, height = 15, dpi = 400)
```

### **E.Coli EDA - Dry**

```{r}
# Created a separate data frame for E.Coli Data
dry_fib_ecoli <- beach_dry_fib |>
  filter(parameter == "E. Coli") 

# Checking how many unit types exist 
unique(dry_fib_ecoli$unit)
# 1 exist - "MPN/100ml" 

# Check How Many Beaches Sampled E.Coli 
unique(dry_fib_ecoli$beach_name)
# 28 beaches that have e.coli data 

# Box and Whisker Plot for E. Coli only For Each Beach
dry_fib_ecoli_plot <- dry_fib_ecoli |>
  ggplot(aes(x = result_log, y = beach_name, fill = beach_name)) +
  geom_boxplot(show.legend = FALSE) + # no legend
  scale_fill_manual(values = htb_brand_colors(length(unique(dry_fib_ecoli$beach_name)))) + # fill based on brand colors 
  facet_wrap(~ year, ncol = 11) + # have 11 columns for each year
  labs(title = "Dry Period E. Coli Concentrations",
       x = "Log 10 Transformed E.Coli Concentration",
    y = "Beach Name") +
  theme_minimal(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"), # bold the text
    panel.grid.minor = element_blank(), # remove the minor grid marks
    panel.grid.major.y = element_blank(), # remove the major grid marks for y-axis
    panel.background = element_rect(fill = "white", color = NA))
print(dry_fib_ecoli_plot)

# Save the plot
#ggsave(here("outputs", "dry_fib_ecoli_plot.png"), width = 25, height = 15, dpi = 400)
```

### **Total Coliforms EDA - Dry**

```{r}
# Created a separate data frame for Total Coliforms data
dry_fib_total_coliforms <- beach_dry_fib |>
  filter(parameter == "Total Coliforms") 

# Checking how many unit types exist 
unique(dry_fib_total_coliforms$unit)
# 2 exist - "MPN/100ml" "CFU/100ml" 

# Check How Many Beaches Sampled Total Coliforms 
unique(dry_fib_total_coliforms$beach_name)
# 34 beaches that have total coliforms data 

# Box and Whisker Plot for Total Coliforms only For Each Beach
dry_fib_tot_coli_plot <- dry_fib_total_coliforms |>
  ggplot(aes(x = result_log, y = beach_name,fill = beach_name)) +
  geom_boxplot(show.legend = FALSE) + # no legend
  scale_fill_manual(values = htb_brand_colors(length(unique(dry_fib_total_coliforms$beach_name)))) + # fill based on brand colors 
  facet_wrap(~ year, ncol = 11) + # have 11 columns for each year
  labs(title = "Dry Period Total Coliforms Concentrations",
       x = "Log 10 Transformed Total Coliforms Concentration",
    y = "Beach Name") +
  theme_minimal(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"), # bold the text
    panel.grid.minor = element_blank(), # remove the minor grid marks
    panel.grid.major.y = element_blank(), # remove the major grid marks for y-axis
    panel.background = element_rect(fill = "white", color = NA))
print(dry_fib_tot_coli_plot)

# Save the plot
#ggsave(here("outputs", "dry_fib_tot_coli_plot.png"), width = 25, height = 15, dpi = 400)
```

### **Fecal Coliforms EDA - Dry**

```{r}
# Created a separate data frame for Fecal Coliforms data 
dry_fib_fecal_coliforms <- beach_dry_fib |>
  filter(parameter == "Fecal Coliforms") 

# Checking how many unit types exist 
unique(dry_fib_fecal_coliforms$unit)
# 2 exist - "MPN/100ml" "CFU/100ml" 

# Check How Many Beaches Sampled Fecal Coliforms
unique(dry_fib_fecal_coliforms$beach_name)
# 33 beaches that have total coliforms data 

# Box and Whisker Plot for Fecal Coliforms only For Each Beach
dry_fib_fec_coli_plot <- dry_fib_fecal_coliforms |>
  ggplot(aes(x = result_log, y = beach_name,fill = beach_name)) +
  geom_boxplot(show.legend = FALSE) + # no legend
  scale_fill_manual(values = htb_brand_colors(length(unique(dry_fib_fecal_coliforms$beach_name)))) + # fill based on brand colors 
  facet_wrap(~ year, ncol = 11) + # have 11 columns for each year
  labs(x = "Log 10 Transformed Fecal Coliforms Concentration",
    y = "Beach Name") +
  theme_minimal(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold"), # bold the text
    panel.grid.minor = element_blank(), # remove the minor grid marks
    panel.grid.major.y = element_blank(), # remove the major grid marks for y-axis
    panel.background = element_rect(fill = "white", color = NA))
print(dry_fib_fec_coli_plot)

# Save the plot
#ggsave(here("outputs", "dry_fib_fec_coli_plot.png"), width = 25, height = #15, dpi = 400)
```

# Hydrographs

[**Goal:**]{.underline} Create a hydrograph to understand changes in precipitation in relation to FIB concentrations throughout the 10 years (2014-2024) across 99 monitoring sites.

```{r}
# Create 4 new datasets where FIB data is joined with precipitation by date
# E.Coli
ecoli_precip <- beach_clean |> 
  filter(parameter == "E. Coli") |>
  left_join(precip_clean, by = c("sample_date" = "date", 
                                 "year" = "year",
                                 "month" = "month")) 
# Check
glimpse(ecoli_precip) #24,375 rows, 25 columns


# Enterococcus
entero_precip <- beach_clean |>
  filter(parameter == "Enterococcus") |>
  left_join(precip_clean, by = c("sample_date" = "date", 
                                 "year" = "year",
                                 "month" = "month")) 
# Check
glimpse(entero_precip) #69,307 rows, 25 columns


# Fecal Coliforms
fecal_precip <- beach_clean |>
  filter(parameter == "Fecal Coliforms") |>
  left_join(precip_clean, by = c("sample_date" = "date", 
                                 "year" = "year",
                                 "month" = "month")) 
# Check
glimpse(fecal_precip) #44,686 rows, 25 columns


# Total Coliforms
total_precip <- beach_clean |>
  filter(parameter == "Total Coliforms") |>
  left_join(precip_clean, by = c("sample_date" = "date", 
                                 "year" = "year",
                                 "month" = "month")) 
# Check
glimpse(total_precip) #70,127 rows, 25 columns
```

## E. Coli

This code creates a hydrograph for the E. coli concentrations for each monitoring station (n = 99). The x axis is the sample date, the y-axis on the left is the log10 concentration of E. coli, and the y-axis on the right is the precipitation amount in inches.

```{r}
# Create the graph 
# Maximum E. coli concentration
top_ecoli_line <- max(ecoli_precip$result_log, na.rm = TRUE)

# Scale precipitation to fit plot
scale_factor <- top_ecoli_line / max(ecoli_precip$prcp_in, na.rm = TRUE)


# Split data by station 
station_list <- split(ecoli_precip, ecoli_precip$station_name)

# Loop through each station 
walk(names(station_list), function(station) {
  
  # Extract that station's data
  station_df <- station_list[[station]] |>
    arrange(sample_date) # Ensures that the sampledate column is in chronological order
  
# Hydrograph
ecoli_hydrograph <- ggplot(station_df,
                           aes(x = sample_date)) +

  # E. coli concentrations
  geom_point(aes(y = result_log),
             color = "#40B4EB",
             size = 0.5,
             alpha = 0.6) +

  # Flipped precipitation spikes
  geom_segment(aes(
    x = sample_date,
    xend = sample_date,
    y = top_ecoli_line,
    yend = top_ecoli_line - prcp_in * scale_factor),
  color = "black", alpha = 0.5, linewidth = 0.3) +

  # Precipitation points
  geom_point(aes(
    y = top_ecoli_line - prcp_in * scale_factor),
  color = "black", size = 0.3, alpha = 0.5) +


  # Dual y-axis
  scale_y_continuous(
    name = expression(Log[10] ~ "E. Coli Concentration"),

    sec.axis = sec_axis(
      trans = ~ (top_ecoli_line - .) / scale_factor,
      name = "Daily Precipitation (in)")) +

  # Date formatting
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "%Y",
    expand = c(0, 0)) +

  # Theme
  labs(title = paste("E. Coli Hydrographs:", station),
    x = "Sample Date") +
  theme_minimal(base_size = 12) +
  theme( axis.text.x = element_text(
      angle = 45,
      hjust = 1,
      size = 6),

    axis.title.y = element_text(color = "black"),

    axis.title.y.right = element_text(
      color = "black"),
    panel.grid.minor = element_blank(),
    legend.position = "none")

print(ecoli_hydrograph)


# Save the plots
ggsave(filename = here("outputs", "hydrographs", "ecoli", paste0(gsub("[^A-Za-z0-9]", "_", station), "_ecoli_hydrograph.png")),
  plot = ecoli_hydrograph, width = 15, height = 8, dpi = 300)
})
```

## Enterococcus

This code creates a hydrograph for the E. coli concentrations for each monitoring station (n = 99). The x axis is the sample date, the y-axis on the left is the log10 concentration of Enterococcus, and the y-axis on the right is the precipitation amount in inches.

```{r}
# Create the graph 
# Maximum Enterococcus concentration
top_entero_line <- max(entero_precip$result_log, na.rm = TRUE)

# Scale precipitation to fit plot
scale_factor <- top_entero_line / max(entero_precip$prcp_in, na.rm = TRUE)


# Split data by station 
station_list <- split(entero_precip, entero_precip$station_name)

# Loop through each station 
walk(names(station_list), function(station) {
  
  # Extract that station's data
  station_df <- station_list[[station]] |>
    arrange(sample_date) # Ensures that the sampledate column is in chronological order
  
# Hydrograph
entero_hydrograph <- ggplot(station_df,
                           aes(x = sample_date)) +

  # E. coli concentrations
  geom_point(aes(y = result_log),
             color = "#2D94C8",
             size = 0.5,
             alpha = 0.6) +

  # Flipped precipitation spikes
  geom_segment(aes(
    x = sample_date,
    xend = sample_date,
    y = top_entero_line,
    yend = top_entero_line - prcp_in * scale_factor),
  color = "black", alpha = 0.5, linewidth = 0.3) +

  # Precipitation points
  geom_point(aes(
    y = top_entero_line - prcp_in * scale_factor),
  color = "black", size = 0.3, alpha = 0.5) +


  # Dual y-axis
  scale_y_continuous(
    name = expression(Log[10] ~ "Enterococcus Concentration"),

    sec.axis = sec_axis(
      trans = ~ (top_entero_line - .) / scale_factor,
      name = "Daily Precipitation (in)")) +

  # Date formatting
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "%Y",
    expand = c(0, 0)) +

  # Theme
  labs(title = paste("Enterococcus Hydrographs:", station),
    x = "Sample Date") +
  theme_minimal(base_size = 12) +
  theme( axis.text.x = element_text(
      angle = 45,
      hjust = 1,
      size = 6),

    axis.title.y = element_text(color = "black"),

    axis.title.y.right = element_text(
      color = "black"),
    panel.grid.minor = element_blank(),
    legend.position = "none")

print(entero_hydrograph)


# Save the plots
#ggsave(filename = here("outputs", "hydrographs", "enterococcus", paste0(gsub("[^A-Za-z0-9]", "_", station), "_entero_hydrograph.png")),
#  plot = entero_hydrograph, width = 15, height = 8, dpi = 300)
})
```

## Total Coliforms

This code creates a hydrograph for the E. coli concentrations for each monitoring station (n = 99). The x axis is the sample date, the y-axis on the left is the log10 concentration of total coliforms, and the y-axis on the right is the precipitation amount in inches.

```{r}
# Create the graph 
# Maximum Total Coliforms concentration
top_total_line <- max(total_precip$result_log, na.rm = TRUE)

# Scale precipitation to fit plot
scale_factor <- top_total_line / max(total_precip$prcp_in, na.rm = TRUE)


# Split data by station 
station_list <- split(total_precip, total_precip$station_name)

# Loop through each station 
walk(names(station_list), function(station) {
  
  # Extract that station's data
  station_df <- station_list[[station]] |>
    arrange(sample_date) # Ensures that the sampledate column is in chronological order
  
# Hydrograph
total_hydrograph <- ggplot(station_df,
                           aes(x = sample_date)) +

  # Total Coliforms concentrations
  geom_point(aes(y = result_log),
             color = "#8FA9B9",
             size = 0.5,
             alpha = 0.6) +

  # Flipped precipitation spikes
  geom_segment(aes(
    x = sample_date,
    xend = sample_date,
    y = top_total_line,
    yend = top_total_line - prcp_in * scale_factor),
  color = "black", alpha = 0.5, linewidth = 0.3) +

  # Precipitation points
  geom_point(aes(
    y = top_total_line - prcp_in * scale_factor),
  color = "black", size = 0.3, alpha = 0.5) +


  # Dual y-axis
  scale_y_continuous(
    name = expression(Log[10] ~ "Total Coliforms Concentration"),

    sec.axis = sec_axis(
      trans = ~ (top_total_line - .) / scale_factor,
      name = "Daily Precipitation (in)")) +

  # Date formatting
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "%Y",
    expand = c(0, 0)) +

  # Theme
  labs(title = paste("Total Coliforms Hydrographs:", station),
    x = "Sample Date") +
  theme_minimal(base_size = 12) +
  theme( axis.text.x = element_text(
      angle = 45,
      hjust = 1,
      size = 6),

    axis.title.y = element_text(color = "black"),

    axis.title.y.right = element_text(
      color = "black"),
    panel.grid.minor = element_blank(),
    legend.position = "none")

print(total_hydrograph)


# Save the plots
#ggsave(filename = here("outputs", "hydrographs", "total_coliforms", paste0(gsub("[^A-Za-z0-9]", "_", station), "_total_hydrograph.png")),
#  plot = total_hydrograph, width = 15, height = 8, dpi = 300)
})
```

## Fecal Coliforms

This code creates a hydrograph for the E. coli concentrations for each monitoring station (n = 99). The x axis is the sample date, the y-axis on the left is the log10 concentration of fecal coliforms, and the y-axis on the right is the precipitation amount in inches.

```{r}
# Create the graph 
# Maximum Fecal Coliforms concentration
top_fecal_line <- max(fecal_precip$result_log, na.rm = TRUE)

# Scale precipitation to fit plot
scale_factor <- top_fecal_line / max(fecal_precip$prcp_in, na.rm = TRUE)


# Split data by station 
station_list <- split(fecal_precip, fecal_precip$station_name)

# Loop through each station 
walk(names(station_list), function(station) {
  
  # Extract that station's data
  station_df <- station_list[[station]] |>
    arrange(sample_date) # Ensures that the sampledate column is in chronological order
  
# Hydrograph
fecal_hydrograph <- ggplot(station_df,
                           aes(x = sample_date)) +

  # Fecal Coliforms concentrations
  geom_point(aes(y = result_log),
             color = "#1479A9",
             size = 0.5,
             alpha = 0.6) +

  # Flipped precipitation spikes
  geom_segment(aes(
    x = sample_date,
    xend = sample_date,
    y = top_fecal_line,
    yend = top_fecal_line - prcp_in * scale_factor),
  color = "black", alpha = 0.5, linewidth = 0.3) +

  # Precipitation points
  geom_point(aes(
    y = top_fecal_line - prcp_in * scale_factor),
  color = "black", size = 0.3, alpha = 0.5) +


  # Dual y-axis
  scale_y_continuous(
    name = expression(Log[10] ~ "Fecal Coliforms Concentration"),

    sec.axis = sec_axis(
      trans = ~ (top_fecal_line - .) / scale_factor,
      name = "Daily Precipitation (in)")) +

  # Date formatting
  scale_x_date(
    date_breaks = "1 year",
    date_labels = "%Y",
    expand = c(0, 0)) +

  # Theme
  labs(title = paste("Fecal Coliforms Hydrographs:", station),
    x = "Sample Date") +
  theme_minimal(base_size = 12) +
  theme( axis.text.x = element_text(
      angle = 45,
      hjust = 1,
      size = 6),

    axis.title.y = element_text(color = "black"),

    axis.title.y.right = element_text(
      color = "black"),
    panel.grid.minor = element_blank(),
    legend.position = "none")

print(fecal_hydrograph)


# Save the plots
#ggsave(filename = here("outputs", "hydrographs", "fecal_coliforms", paste0(gsub("[^A-Za-z0-9]", "_", station), "_fecal_hydrograph.png")),
#  plot = fecal_hydrograph, width = 15, height = 8, dpi = 300)
})
```
