---
title: "EDA For Beach FIB V Rain"
author: "Tina Tran"
date: "November 19, 2025"
format: html
editor: visual
format: 
  html:
    embed-resources: true
    code-fold: true
    toc: true
execute:
  warning: false
  message: false
theme: "minty"
df-print: kable
---

# Exploratory Data Analysis For Beach FIB v Rain

```{r}
# Load libraries 
library(dplyr)
library(ggplot2)
library(tidyverse)
library(ggridges)
library(here)
library(lubridate)
library(slider)
library(scales)
library(janitor)
```

## **Heal The Bay Brand Colors**

This code assigns the the following colors to each FIB parameter: E. Coli, Enterococcus, Total Coliforms, and Fecal Coliforms. It also creates another data frame to create the HTB gradient.

```{r}
htb_colors <- c(
  "E. Coli" = "#40B4EB",
  "Enterococcus" = "#2D94C8",
  "Total Coliforms" = "#8FA9B9",
  "Fecal Coliforms" = "#1479A9")

# HTB Gradient 
htb_gradient <- colorRampPalette(htb_colors)(11)
htb_gradient 
```

## Mutate FIB Concentration & Precipitation Data

```{r}
# Read the data file
beach_data_2014_2024 <- read.csv(here("data","clean_master_beach_data_2014_2024.csv")) 

# Mutate the Beach Data 
beach_clean <- beach_data_2014_2024 |>
  mutate(result_log = log10(result), # log 10 transform the data
         sampledate = as.Date(sampledate), # change from chr to date
          year = year(sampledate),  # extract year from sampledate
          month = month(sampledate, label = TRUE, abbr = TRUE)) # extract month from sampledate

# Creating a summary of the annual log results of each fib parameter for each station
beach_annual <- beach_clean |>
  group_by(stationname, parameter, year, beachname) |>
  summarise(
    annual_mean_log = mean(result_log, na.rm = TRUE),
    annual_median_log = median(result_log, na.rm = TRUE),
    annual_variance_log = var(result_log, na.rm = TRUE),
    n_samples = n(),
    .groups = "drop")
```

```{r}
# Read in the Precipitation Data
precip_2014_2024 <- read.csv(here("data","precipitation_clean_2014_2024.csv")) 

# Mutate the Precip Data
precip_clean <- precip_2014_2024 |>
  mutate(date = as.Date(date), # Change date from chr to date
         year = year(date), # extract the year from the date
         month = month(date, label = TRUE, abbr = TRUE), # extract month from the date
         wet = prcp_in > 0.1) # defines wet weather as >0.1 inches

# Separate wet vs dry data
wet_weather <- precip_clean |>  filter(wet == TRUE)

dry_weather <- precip_clean |> filter(wet == FALSE)


# Total the Annual Precipitation Each Year 
precip_annual <- precip_clean |>
  group_by(year) |>
  summarise(
    total_rain_in = sum(prcp_in, na.rm = TRUE),
    .groups = "drop")

# Join the Precipi Data with the FIB Concentrations Annual Data
join_prcp_fib_data <- beach_annual |>
  left_join(precip_annual, by = "year")


join_fib_prcp_bin <- join_prcp_fib_data |>
  mutate(rain_bin = cut(total_rain_in,
                        breaks = 4, 
                        labels = c("Low", "Moderate", "High", "Very High")))
```

# Precipitation

## Total Annual Precipitation

```{r}
# Create a summary of the precipitation for each year 
rain_summary_table <- precip_clean|>
  group_by(year) |>
summarize(var=var(prcp_in),
            min_rain = min(prcp_in),
            IQ25_rain = quantile(prcp_in, probs = 0.25), 
            mean_rain = mean(prcp_in),
            median_rain = median(prcp_in),
            IQ75_rain = quantile(prcp_in, probs = 0.75),
            max_rain = max(prcp_in))
rain_summary_table 

# Calculate the average total rainfall over the 10 years
mean_total_rain <- precip_annual |> 
  summarise(mean_rain_event = mean(total_rain_in), na.rm = TRUE) |>
  pull(mean_rain_event) # this extracts the numeric valye of the mean rain event so that it can be plotted in ggplot

# Plot the total precipitation for each year 
rain_bar <- ggplot(precip_annual, 
                   aes(x = factor(year), y = total_rain_in)) +
  geom_col(fill = "#1479A9") + 
    geom_hline(yintercept = mean_total_rain, linetype = "dashed", linewidth = 1, color = "black")+
  labs(#title = "Total Annual Precipitation (2014–2024)",
    x = "Year",
    y = "Total Rainfall (inches)") +
  theme_bw(base_size = 14)
rain_bar

# Calculate the overall mean precipitation for all 10 years
overall_mean_rain <- precip_clean |> 
  summarise(mean_rain_Event = mean(prcp_in), na.rm = TRUE)
overall_mean_rain

```

## Monthly Average Rainfall

This code will total the amount of rainfall for each month for each year.

```{r}
# Create the data frame
precip_monthly <- precip_clean |>
  group_by(year,month) |> # group the data by year and month
  summarise(total_rain_in = sum(prcp_in, na.rm = TRUE), # sum the precip total
    .groups = "drop")

# Creating the graph for the data
precip_monthly_plot <- ggplot(precip_monthly,
  aes(x = total_rain_in, fill = factor(year), y = factor(year))) +
  geom_col() +
  facet_wrap(~ month, ncol = 12) +
  scale_fill_manual(values = htb_gradient) +
  labs(x = "Total Rainfall (inches)", y = "Year",
    fill = "Year") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(angle = 90, vjust = 0.5))
precip_monthly_plot

# Save the bar graph
#ggsave(here("outputs", "precip_only", "monthly_precip.png"), 
     # plot = precip_monthly_plot, width = 14, height = 8, dpi = 500)
```

# E. coli v Rain

**Question to answer:** **How does total rainfall relate to annual FIB concentrations?**

Each plot represents a monitoring station for a specific year. The annual median e.coli concentrations were calculated for each monitoring site per year, and joined to the precipitation data's total rainfall data in inches.

There is a lot of variability in the annual median e.coli concentrations and understanding its relationship with the rainfall visually.

```{r}
# Filter out E.coli
join_ecoli <- join_prcp_fib_data |>
  filter(parameter == "E. Coli")

ecoli_prcp_med_point <- ggplot(join_ecoli, 
    aes(x = total_rain_in,
        y = annual_median_log,
        color = factor(year),       # year shown as color
        shape = stationname)) +     # station shown as shape
  geom_point(alpha = 0.8, size = 3) +
  labs(
    title = "Annual Median E. Coli vs Rainfall by Year and Station",
    x = "Total Annual Rainfall (inches)",
    y = "Median Log10 E. Coli Concentration",
    color = "Year",
    shape = "Station"
  ) +
  theme_bw(base_size = 14)
ecoli_prcp_med_point
```

## Variance of E. Coli v Rain

```{r}
# Scatter Plot of annual variance E.Coli vs rainfall
ecoli_prcp_var_point <- ggplot(join_ecoli, 
    aes(x = total_rain_in,
        y = annual_variance_log)) +
  geom_point(alpha = 0.7, size = 2, color = "#40B4EB") +
  labs(
    title = "Annual Variance E. Coli Concentrations vs Total Rainfall",
    x = "Total Annual Rainfall (inches)",
    y = "Varaince Log10 E. Coli Concentration"
  ) +
  theme_bw(base_size = 14)
ecoli_prcp_var_point

# Note there are 5 NA values for variance because there was only 1 sample
```

Box plot vision create a min, IQ25, median, IQ75, max of the annual median values of each, group by year

## Enterococcus v Rain Hydrograph

```{r}
# Filter out Enterococcus
join_enterococcus <- join_prcp_fib_data |>
  filter(parameter == "Enterococcus")


# Scatter Plot of annual median Enterococcus vs Total rainfall
entero_prcp_med_point <- ggplot(join_enterococcus, 
    aes(x = total_rain_in,
        y = annual_median_log)) +
  geom_point(alpha = 0.7, size = 2, color = "#40B4EB") +
  labs(
    title = "Annual Median Enterococcus Concentrations vs Rainfall",
    x = "Total Annual Rainfall (inches)",
    y = "Median Log10 Enterococcus Concentration"
  ) +
  theme_bw(base_size = 14)
entero_prcp_med_point
```

## Total Coliforms v Rain Hydrograph

```{r}
# Filter out Total Coliforms
join_total_coliforms <- join_prcp_fib_data |>
  filter(parameter == "Total Coliforms")


# Scatter Plot of annual median Total Coliforms vs Total rainfall
tot_prcp_med_point <- ggplot(join_total_coliforms, 
    aes(x = total_rain_in,
        y = annual_median_log)) +
  geom_point(alpha = 0.7, size = 2, color = "#40B4EB") +
  labs(
    title = "Annual Median Total Coliforms Concentrations vs Rainfall",
    x = "Total Annual Rainfall (inches)",
    y = "Median Log10 Total Coliforms Concentration"
  ) +
  theme_bw(base_size = 14)
tot_prcp_med_point
```

## Fecal Coliforms v Rain Hydrograph

```{r}
# Filter out Enterococcus
join_fecal_coliforms <- join_prcp_fib_data |>
  filter(parameter == "Fecal Coliforms")


# Scatter Plot of annual median E.Coli vs rainfall
fec_prcp_med_point <- ggplot(join_fecal_coliforms, 
    aes(x = total_rain_in,
        y = annual_median_log)) +
  geom_point(alpha = 0.7, size = 2, color = "#40B4EB") +
  labs(
    title = "Annual Median Fecal Coliforms Concentrations vs Rainfall",
    x = "Total Annual Rainfall (inches)",
    y = "Median Log10 Fecal Coliforms Concentration") +
  theme_bw(base_size = 14)
fec_prcp_med_point
```
