---
title: "beach_fib_average_annual"
author: "Tina Tran"
date: "November 18, 2025"
format: html
editor: visual
format: 
  html:
    embed-resources: true
    code-fold: true
    toc: true
execute:
  warning: false
  message: false
theme: "minty"
df-print: kable
---

# Exploratory Data Analysis For Beach FIB Only

This document includes the exploratory data analysis (EDA) of beach FIB concentrations on an annual and monthly basis.

```{r, message = false, warning = false}
# Load libraries 
library(dplyr)
library(ggplot2)
library(tidyverse)
library(ggridges)
library(here)
library(lubridate)
library(slider)
library(scales)
library(janitor)
```

## **Heal The Bay Brand Colors**

This code assigns the the following colors to each FIB parameter: E. Coli, Enterococcus, Total Coliforms, and Fecal Coliforms.

```{r, message = false, warning = false}
htb_colors <- c(
  "E. Coli" = "#40B4EB",
  "Enterococcus" = "#2D94C8",
  "Total Coliforms" = "#8FA9B9",
  "Fecal Coliforms" = "#1479A9")
```

# Annual Beach FIB EDA

## **Mutating Beach Data Frames**

The data was mutated to add a year and month column for analysis. The mean, median, and variance was calculated for the log 10 transformed FIB concentrations grouped by each motioning station and year.

```{r}
# Read the data file
beach_data_2014_2024 <- read.csv(here("data","clean_master_beach_data_2014_2024.csv")) 

# Mutate the Beach Data 
beach_clean <- beach_data_2014_2024 |>
  mutate(result_log = log10(result), # log 10 transform the data
         sampledate = as.Date(sampledate), # change from chr to date
          year = year(sampledate),  # extract year from sampledate
          month = month(sampledate, label = TRUE, abbr = TRUE)) # extract month from sampledate

# Creating a summary of the annual mean log results of each fib parameter for each station
beach_annual <- beach_clean |>
  group_by(stationname, parameter, year) |>
  summarise(
    annual_mean_log = mean(result_log, na.rm = TRUE),
    annual_median_log = median(result_log, na.rm = TRUE),
    annual_variance_log = var(result_log, na.rm = TRUE),
    n_samples = n(),
    .groups = "drop")
```

```{r}
# Read in the Precipitation Data
precip_2014_2024 <- read.csv(here("data","precipitation_clean_2014_2024.csv")) 

# Mutate the Precip Data
precip_clean <- precip_2014_2024 |>
  mutate(date = as.Date(date), # Change date from chr to date
         year = year(date), # extract the year from the date
         month = month(date, label = TRUE, abbr = TRUE), # extract month from the date
         wet = prcp_in > 0.1) # defines wet weather as >0.1 inches

# Separate wet vs dry data
wet_weather <- precip_clean |>  
  filter(wet == TRUE)

dry_weather <- precip_clean |> 
  filter(wet == FALSE)


# Total the Annual Precipitation Each Year 
precip_annual <- precip_clean |>
  group_by(year) |>
  summarise(
    total_rain_in = sum(prcp_in, na.rm = TRUE),
    .groups = "drop")

# Join the Precipi Data with the FIB Concentrations Annual Data
join_prcp_fib_data <- beach_annual |>
  left_join(precip_annual, by = "year")


```

## Mean Annual Average FIB Concentrations

### E.Coli

#### Mean E.Coli Trends Across All Sites Annually

```{r}
# Create a new dataframe for only yearly e.coli concentrations
annual_ecoli <- beach_annual |>
  filter(parameter == "E. Coli")

# Create box plot
beach_ecoli_mean_annual_plot <- ggplot(annual_ecoli,
  aes(x = factor(year), y = annual_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Mean E. Coli Concentrations Across All Sites",
    x = "Year",
    y = "Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_ecoli_mean_annual_plot

# Save the Plot 
#ggsave(here("outputs", "beach_fib_average_annually", #"beach_ecoli_annual_plot.png"),
#  plot = beach_ecoli_annual_plot, width = 15, height = 6, dpi = 400)
```

#### Median E. Coli Concentration Across All Sites Annually

```{r}
# Create box plot
beach_ecoli_med_annual_plot <- ggplot(annual_ecoli,
  aes(x = factor(year), y = annual_median_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Median E. Coli Concentrations Across All Sites",
    x = "Year",
    y = "Median Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_ecoli_med_annual_plot

```

```{r}
# Summary Statistics
ecoli_summary_table <- annual_ecoli |>
  group_by(year) |>
  summarise(
    n = n(),
    min_ecoli = min(annual_median_log, na.rm = TRUE),
    IQ25_ecoli = quantile(annual_median_log, 0.25, na.rm = TRUE),
    mean_ecoli = mean(annual_median_log, na.rm = TRUE),
    median_ecoli = median(annual_median_log, na.rm = TRUE),
    IQ75_ecoli = quantile(annual_median_log, 0.75, na.rm = TRUE),
    max_ecoli = max(annual_median_log, na.rm = TRUE),
    var_ecoli = var(annual_median_log, na.rm = TRUE),
    .groups = "drop")
```

#### Rainfall v E.Coli

##### Median E.Coli v Precipitation

Each point represents the annual median E.coli concentration at each monitoring station for a particular year (n = 264).

```         
```

```         
```

### Enterococcus

#### Mean Enterococcus Trends Across All Sites Annually

```{r}
annual_enterococcus <- beach_annual |>
  filter(parameter == "Enterococcus")

# SUmmarize the number of samples for each year
yr_entero_samples <- annual_enterococcus |>
  group_by(year) |>
  summarise(
    total_samples = sum(n_samples),
    .groups = "drop")

# Find the annual log 10 transforemd enterococcus value
entro_threshold <- 104 # this is in MPN/100 mL
log_entro_threshold <- log10(entro_threshold) 

# Summarize the mean entrococcus value across all sizes
mean_total_entro <- annual_enterococcus |> 
  summarise(mean_yr_entero = mean(annual_mean_log), na.rm = TRUE) |>
  pull(mean_yr_entero) # this extracts the numeric valye of the mean log10 entro event so that it can be plotted in ggplot


# Create box plot
beach_entero_mean_annual_plot <- ggplot(annual_enterococcus,
  aes(x = factor(year), y = annual_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  geom_hline(yintercept = mean_total_entro, linetype = "dashed", linewidth = 1, color = "black")+
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Mean Enterococcus Concentrations Across All Sites",
    x = "Year",
    y = "Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_entero_mean_annual_plot

# Save the Plot 
#ggsave(here("outputs", "beach_fib_average_annually", #"beach_entero_annual_plot.png"),
#  plot = beach_entero_annual_plot, width = 15, height = 6, dpi = 400)
```

#### Median Enterococcus Concentration Across All Sites Annually

The enterococcus exceedance threshold is 104 MPN/100 mL.

```{r}
# Create box plot
beach_entero_med_annual_plot <- ggplot(annual_enterococcus,
  aes(x = factor(year), y = annual_median_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Median Enterococcus Concentrations Across All Sites",
    x = "Year",
    y = "Annual Median Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_entero_med_annual_plot

ggsave(here("outputs", "beach_fib_average_annually", "beach_entero_med_annual_plot.png"),
  plot = beach_entero_med_annual_plot, width = 15, height = 6, dpi = 400)
```

### Total Coliforms

#### Mean Total Coliforms Trends Across All Sites Annually

```{r}
annual_total_coliforms <- beach_annual |>
  filter(parameter == "Total Coliforms")

# Summarize the mean total coliform value across all sizes
mean_total_coli <- annual_total_coliforms |> 
  summarise(mean_yr_tot = mean(annual_mean_log), na.rm = TRUE) |>
  pull(mean_yr_tot) # this extracts the numeric valye of the mean log10 entro event so that it can be plotted in ggplot

# Create box plot
beach_tot_mean_annual_plot <- ggplot(annual_total_coliforms,
  aes(x = factor(year), y = annual_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  geom_hline(yintercept = mean_total_coli, linetype = "dashed", linewidth = 1, color = "black")+
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Mean Total Coliforms Concentrations Across All Sites",
    x = "Year",
    y = "Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_tot_mean_annual_plot

# Save the Plot 
#ggsave(here("outputs", "beach_fib_average_annually", #"beach_tot_annual_plot.png"),
#  plot = beach_tot_annual_plot, width = 15, height = 6, dpi = 400)
```

#### Median Total Coliforms Concentration Across All Sites Annually

```{r}
# Create box plot
beach_tot_med_annual_plot <- ggplot(annual_total_coliforms,
  aes(x = factor(year), y = annual_median_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Median Total Coliforms Concentrations Across All Sites",
    x = "Year",
    y = "Median Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_tot_med_annual_plot
```

### Fecal Coliforms

#### Mean Fecal Coliforms Trends Across All Sites Annually

```{r}
annual_fecal_coliforms <- beach_annual |>
  filter(parameter == "Fecal Coliforms")

# Create box plot
beach_fec_mean_annual_plot <- ggplot(annual_fecal_coliforms,
  aes(x = factor(year), y = annual_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Average Fecal Coliforms Concentrations Across All Sites",
    x = "Year",
    y = "Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_fec_mean_annual_plot

# Save the Plot 
#ggsave(here("outputs", "beach_fib_average_annually", #"beach_fec_annual_plot.png"),
#  plot = beach_fec_annual_plot, width = 15, height = 6, dpi = 400)
```

#### Median Fecal Coliforms Concentration Across All Sites Annually

```{r}
# Create box plot
beach_fec_med_annual_plot <- ggplot(annual_fecal_coliforms,
  aes(x = factor(year), y = annual_median_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Median Fecal Coliforms Concentrations Across All Sites",
    x = "Year",
    y = "Median Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_fec_med_annual_plot

```

# Beach FIB Average Monthly on a Year-to-Year Basis

Average all the beaches each month for each year. Then analyze on a year to year basis and have it be 1 year at a time.

## **2014 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2014 <- beach_clean |> 
  filter(year == 2014)

# Create the average values of each month in the year 2014
beach_monthly_2014 <- beach_2014 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2014_box <- ggplot(beach_monthly_2014,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2014)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2014_box

# Save the Plot 
#ggsave(filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2014_plot.png"),
#  plot = beach_monthly_2014_box, width = 21, height = 12, dpi = 400)
```

## **2015 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2015 <- beach_clean |> 
  filter(year == 2015)

# Create the average values of each month in the year 2014
beach_monthly_2015 <- beach_2015 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2015_box <- ggplot(beach_monthly_2015,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2015)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2015_box

# Save the Plot 
#ggsave(filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2015_plot.png"),
#  plot = beach_monthly_2015_box, width = 21, height = 12, dpi = 400)
```

## **2016 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2016 <- beach_clean |> 
  filter(year == 2016)

# Create the average values of each month in the year 2014
beach_monthly_2016 <- beach_2016 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2016_box <- ggplot(beach_monthly_2016,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2016)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2016_box

# Save the Plot 
#ggsave(filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2016_plot.png"),
#  plot = beach_monthly_2016_box, width = 21, height = 12, dpi = 400)
```

## **2017 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2017 <- beach_clean |> 
  filter(year == 2017)

# Create the average values of each month in the year 2014
beach_monthly_2017 <- beach_2017 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2017_box <- ggplot(beach_monthly_2017,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2017)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2017_box

# Save the Plot 
#ggsave(filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2017_plot.png"),
#  plot = beach_monthly_2017_box, width = 21, height = 12, dpi = 400)
```

## **2018 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2018 <- beach_clean |> 
  filter(year == 2018)

# Create the average values of each month in the year 2014
beach_monthly_2018 <- beach_2018 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2018_box <- ggplot(beach_monthly_2018,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2018)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2018_box

# Save the Plot 
#ggsave(filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2018_plot.png"),
#  plot = beach_monthly_2018_box, width = 21, height = 12, dpi = 400)
```

## **2019 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2019 <- beach_clean |> 
  filter(year == 2019)

# Create the average values of each month in the year 2014
beach_monthly_2019 <- beach_2019 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2019_box <- ggplot(beach_monthly_2019,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2019)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2019_box

# Save the Plot 
#ggsave(filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2019_plot.png"),
#  plot = beach_monthly_2019_box, width = 21, height = 12, dpi = 400)
```

## **2020 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2020 <- beach_clean |> 
  filter(year == 2020)

# Create the average values of each month in the year 2014
beach_monthly_2020 <- beach_2020 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2020_box <- ggplot(beach_monthly_2020,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2020)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2020_box

# Save the Plot 
#ggsave( filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2020_plot.png"),
#  plot = beach_monthly_2020_box, width = 21, height = 12, dpi = 400)
```

## **2021 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2021 <- beach_clean |> 
  filter(year == 2021)

# Create the average values of each month in the year 2014
beach_monthly_2021 <- beach_2021 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2021_box <- ggplot(beach_monthly_2021,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2021)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2021_box

# Save the Plot 
#ggsave( filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2021_plot.png"),
#  plot = beach_monthly_2021_box, width = 21, height = 12, dpi = 400)
```

## **2022 Yearly Box Plot**

### **Mean**

```{r}
#Create New Data Frame 
beach_2022 <- beach_clean |> 
  filter(year == 2022)

# Create the average values of each month in the year 2014
beach_monthly_2022 <- beach_2022 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)

```

```{r}
# Create box plot
beach_monthly_2022_box <- ggplot(beach_monthly_2022,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2022)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2022_box

# Save the Plot 
#ggsave( filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2022_plot.png"),
#  plot = beach_monthly_2022_box, width = 21, height = 12, dpi = 400)
```

## **2023 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2023 <- beach_clean |> 
  filter(year == 2023)

# Create the average values of each month in the year 2014
beach_monthly_2023 <- beach_2023 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2023_box <- ggplot(beach_monthly_2023,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2023)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2023_box

# Save the Plot 
#ggsave( filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2023_plot.png"),
#  plot = beach_monthly_2023_box, width = 21, height = 12, dpi = 400)
```

## **2024 Yearly Box Plot**

### Mean

```{r}
#Create New Data Frame 
beach_2024 <- beach_clean |> 
  filter(year == 2024)

# Create the average values of each month in the year 2014
beach_monthly_2024 <- beach_2024 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2024_box <- ggplot(beach_monthly_2024,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2024)",
    x = "Month",
    y = "Monthly Mean Log10 Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")
beach_monthly_2024_box

# Save the Plot 
#ggsave( filename = here("outputs", "beach_fib_average_monthly", #"beach_fib_monthly_2024_plot.png"),
#  plot = beach_monthly_2024_box, width = 21, height = 12, dpi = 400)
```
