---
title: "beach_fib_average_annual"
format: html
editor: visual
---

## Beach FIB Annual Analysis

```{r, message = false, warning = false}
# Load libraries 
library(dplyr)
library(ggplot2)
library(tidyverse)
library(ggridges)
library(here)
library(lubridate)
library(slider)
library(scales)
library(janitor)
```

**Heal The Bay Brand Colors For GGplot**

This code creates a color gradient for the graphs based on the Heal The Bay (HTB)'s brand colors. It creates 18 types of colors based on the 5 given brand colors.

```{r, message = false, warning = false}
htb_colors <- c(
  "E. Coli" = "#40B4EB",
  "Enterococcus" = "#2D94C8",
  "Total Coliforms" = "#8FA9B9",
  "Fecal Coliforms" = "#1479A9")
```

**Clean Data & Create Annual Data Frames**

```{r, message = false, warning = false}
# Read the file
beach_data_2014_2024 <- read.csv(here("data","clean_master_beach_data_2014_2024.csv")) 

# Clean the data
beach_clean <- beach_data_2014_2024 |>
  mutate(result_log = log10(result), # log 10 transform the data
         sampledate = as.Date(sampledate), # change from chr to date
          year = year(sampledate), 
          month = month(sampledate, label = TRUE, abbr = TRUE))

# Creating a summary of the annual mean log results of each fib parameter for each station
beach_annual <- beach_clean |>
  group_by(stationname, parameter, year) |>
  summarise(
    annual_mean_log = mean(result_log, na.rm = TRUE),
    n_samples = n(),
    .groups = "drop")
```

## Annual Average E.Coli Trends Across All Sites

```{r, message = false, warning = false}
# Create a new dataframe for only yearly e.coli concentrations
annual_ecoli <- beach_annual |>
  filter(parameter == "E. Coli")

# Create box plot
beach_ecoli_annual_plot <- ggplot(annual_ecoli,
  aes(x = factor(year), y = annual_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Average E. Coli Concentrations Across All Sites",
    x = "Year",
    y = "Annual Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave(here("outputs", "beach_fib_average_annually", "beach_ecoli_annual_plot.png"),
  plot = beach_ecoli_annual_plot, width = 15, height = 12, dpi = 400)
```

## Annual Average Enterococcus Trends Across All Sites

```{r, message = false, warning = false}
annual_enterococcus <- beach_annual |>
  filter(parameter == "Enterococcus")

# Create box plot
beach_entero_annual_plot <- ggplot(annual_enterococcus,
  aes(x = factor(year), y = annual_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Average Enterococcus Concentrations Across All Sites",
    x = "Year",
    y = "Annual Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave(here("outputs", "beach_fib_average_annually", "beach_entero_annual_plot.png"),
  plot = beach_entero_annual_plot, width = 15, height = 12, dpi = 400)
```

## Annual Average Total Coliforms Trends Across All Sites

```{r, message = false, warning = false}
annual_total_coliforms <- beach_annual |>
  filter(parameter == "Total Coliforms")

# Create box plot
beach_tot_annual_plot <- ggplot(annual_total_coliforms,
  aes(x = factor(year), y = annual_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Average Total Coliforms Concentrations Across All Sites",
    x = "Year",
    y = "Annual Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave(here("outputs", "beach_fib_average_annually", "beach_tot_annual_plot.png"),
  plot = beach_tot_annual_plot, width = 15, height = 12, dpi = 400)
```

## Annual Average Fecal Coliforms Trends Across All Sites

```{r, message = false, warning = false}
annual_fecal_coliforms <- beach_annual |>
  filter(parameter == "Fecal Coliforms")

# Create box plot
beach_fec_annual_plot <- ggplot(annual_fecal_coliforms,
  aes(x = factor(year), y = annual_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1, alpha = 0.6) +
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(title = "Annual Average Fecal Coliforms Concentrations Across All Sites",
    x = "Year",
    y = "Annual Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(
    strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave(here("outputs", "beach_fib_average_annually", "beach_fec_annual_plot.png"),
  plot = beach_fec_annual_plot, width = 15, height = 12, dpi = 400)
```
