---
title: "beach_fib_time_series"
format: html
editor: visual
---

## Beach FIB Timeseries Analysis

This code is creating a 10 year timeseries analysis for each beach to understand the trends between the wet and dry periods across 2014-2024.

```{r, message = false, warning = false}
# Load libraries 
library(dplyr)
library(ggplot2)
library(tidyverse)
library(ggridges)
library(here)
library(lubridate)
library(slider)
library(scales)
library(purrr)
library(janitor)
```

**Loading Data + Clean Data For This Timeseries Analysis**

```{r}
beach_clean <- read.csv(here("data", "clean_master_beach_data_2014_2024.csv")) |>
  mutate(log_result = log10(result),     # log 10 transformed the result column
         sampledate = as.Date(sampledate)) # make sampledate into a date from a chr

```

**Heal The Bay Brand Colors For GGplot**

This code creates a color gradient for the graphs based on the Heal The Bay (HTB)'s brand colors. It creates 18 types of colors based on the 5 given brand colors.

```{r}
htb_colors <- c(
  "E. coli" = "#40B4EB",
  "Enterococcus" = "#2D94C8",
  "Total Coliform" = "#8FA9B9",
  "Fecal Coliform" = "#1479A9")
```

**10 Year Time Series Analysis - One PNG Per Station (4 Parameters)**

```{r}
# Split data by station ----
station_list <- split(beach_clean, beach_clean$stationname)

# Loop through each station ----
walk(names(station_list), function(station) {
  
  # Extract that station's data
  station_df <- station_list[[station]] |>
    arrange(sampledate) # This code ensures that the sampledate column is in chronological order
  
  # Create the plot with 4 panels (one per parameter)
  station_plot <- ggplot(station_df, aes(x = sampledate, y = log_result, color = parameter)) +
    geom_line(aes(group = parameter), linewidth = 0.6, alpha = 0.8) +  # connect in date order
      scale_color_manual(values = htb_colors) +              # apply your custom brand palette
    geom_point(alpha = 0.6, size = 1.2) +
    facet_wrap(~ parameter, scales = "free_y", nrow = 2) +  # 4 panels
    scale_color_manual(values = htb_colors) +
    scale_x_date(
      date_breaks = "1 year",
      date_labels = "%Y"
    ) +
    labs(
      title = paste0("10-Year Time Series: ", station),
      x = "Date",
      y = expression(Log[10]*"(Concentration)"),
      color = "Parameter"
    ) +
    theme_bw(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 1),
      legend.position = "none",
      panel.spacing = unit(1, "lines")
    )
  
  # Save the PNG ----
 ggsave(
  filename = here("outputs", "beach_timeseries_all", paste0(gsub("[^A-Za-z0-9]", "_", station), "_timeseries.png")),
  plot = station_plot,
  width = 15,
  height = 10,
  dpi = 400)
  
  message("✅ Saved plot for: ", station)
})

```

**10 Year Time Series Analysis - One PNG Per Station Per Parameter**

```{r}
# Split data by station ----
station_list <- split(beach_clean, beach_clean$stationname)

# Loop through each station ----
walk(names(station_list), function(station) {
  
  # Extract that station’s data
  station_df <- station_list[[station]]
  
  # Split further by parameter ----
  parameter_list <- split(station_df, station_df$parameter)
  
  # Loop through each parameter for this station ----
  walk(names(parameter_list), function(param) {
    
    # Extract the subset for this parameter
    parameter_df <- parameter_list[[param]]
    
    # Create the plot ----
    station_param_plot <- ggplot(parameter_df, aes(x = sampledate, y = log_result)) +
      geom_point(color = htb_colors[param], alpha = 0.6, size = 1.2) +
      geom_line(color = htb_colors[param], linewidth = 0.8, aes(group = 1)) +  # Connect by date
      geom_smooth(method = "loess", se = FALSE, color = htb_colors[param], linewidth = 0.9) +
      scale_x_date(
        date_breaks = "1 year",
        date_labels = "%Y"
      ) +
      labs(
        title = paste0("10-Year Time Series: ", station, " (", param, ")"),
        x = "Date",
        y = expression(Log[10]*"(Concentration)")
      ) +
      theme_minimal(base_size = 12) +
      theme(
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1)
      )
    
    # Save PNG ----
    ggsave(
      filename = here(
        "outputs", "beach_timeseries_separate",
        paste0(
          gsub("[^A-Za-z0-9]", "_", station), "_",
          gsub("[^A-Za-z0-9]", "_", param), "_timeseries.png"
        )
      ),
      plot = station_param_plot,
      width = 12,
      height = 10,
      dpi = 400
    )
    
    message("✅ Saved plot for: ", station, " - ", param)
  })
})

```

The `echo: false` option disables the printing of code (only output is displayed).
