---
title: "beach_fib_time_series"
format: html
editor: visual
---

## Beach FIB Timeseries Analysis

This code is creating a 10 year timeseries analysis for each beach to understand the trends between the wet and dry periods across 2014-2024.

```{r, message = false, warning = false}
# Load libraries 
library(dplyr)
library(ggplot2)
library(tidyverse)
library(ggridges)
library(here)
library(lubridate)
library(slider)
library(scales)
library(purrr)
library(janitor)
```

**Loading Data + Clean Data For This Timeseries Analysis**

```{r}
beach_clean <- read.csv(here("data", "clean_master_beach_data_2014_2024.csv")) |>
  mutate(log_result = log10(result), # log 10 transformed the result column
         sampledate = as.Date(sampledate), # make sampledate into a date from a chr
         year = year(sampledate)) # New column with only year


# Quick data inspection
unique(beach_clean$stationname) # checking the number of stations in data
unique(beach_clean$beachname) # checking the number of beaches in data
unique(beach_clean$method) # checking the number of methods in data
unique(beach_clean$unit) # checking the number of units in data
```

**Heal The Bay Brand Colors For GGplot**

This code assigns the the following colors to each FIB parameter: E. Coli, Enterococcus, Total Coliforms, and Fecal Coliforms.

```{r}
htb_colors <- c(
  "E. Coli" = "#40B4EB",
  "Enterococcus" = "#2D94C8",
  "Total Coliforms" = "#8FA9B9",
  "Fecal Coliforms" = "#1479A9")
```

**10 Year Time Series Analysis - One PNG Per Station (4 Parameters)**

This code creates a 10 year time series line graph for each log10 transformed result value. Each png is corresponds to a **monitoring location (n = 82)** and it will contain 4 panels if data is available. Each panel represents a different FIB parameters: E.Coli, Enterococcus, Total Coliform, and Fecal Coliforms.

```{r}
# Split data by station 
station_list <- split(beach_clean, beach_clean$stationname)

# Loop through each station 
walk(names(station_list), function(station) {
  
  # Extract that station's data
  station_df <- station_list[[station]] |>
    arrange(sampledate) # Ensures that the sampledate column is in chronological order
  
  # Create the plot with 4 panels (one per parameter)
  station_plot <- ggplot(station_df, aes(x = sampledate, y = log_result, color = parameter)) +
    geom_line(aes(group = parameter), linewidth = 0.6, alpha = 0.8) +  # connect in date order
      scale_color_manual(values = htb_colors) + # apply brand colors
    geom_point(alpha = 0.6, size = 1.2) +
    facet_wrap(~ parameter, scales = "fixed", nrow = 2) +  # 4 panels
    scale_color_manual(values = htb_colors) +
    scale_x_date(
      date_breaks = "1 year",
      date_labels = "%Y") +
    labs(title = paste0("10-Year Time Series: ", station),
      x = "Year",
      y = expression(Log[10]*"(Concentration)")) +
    theme_bw(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 0.5),
      legend.position = "none",
      panel.spacing = unit(1, "lines"))
  
  # Save the PNG ----
# ggsave(
#  filename = here("outputs", "beach_timeseries_all", paste0(gsub("[^A-Za-z0-9]", "_", station), "_timeseries.png")),
#  plot = station_plot, width = 15, height = 10,dpi = 400)
  })

```

**10 Year Time Series Analysis - One PNG Per Beach Per Parameter**

This code creates a 10 year time series line graph for each log10 transformed result value. Each png is corresponds to a **beach location (n = 34)** and it will contain 4 panels if data is available. Each panel represents a different FIB parameters: E.Coli, Enterococcus, Total Coliform, and Fecal Coliforms.

```{r}
# Split data by beach 
beach_list <- split(beach_clean, beach_clean$beachname)

# Loop through each beach 
walk(names(beach_list), function(beach) {
  
  # Extract that station's data
  beach_df <- beach_list[[beach]] |>
    arrange(sampledate) # Ensures that the sampledate column is in chronological order
  
  # Create the plot with 4 panels (one per parameter)
  beach_plot <- ggplot(beach_df, aes(x = sampledate, y = log_result, color = parameter)) +
    geom_line(aes(group = parameter), linewidth = 0.6, alpha = 0.8) +  # connect in date order
      scale_color_manual(values = htb_colors) + # apply brand colors
    geom_point(alpha = 0.6, size = 1.2) +
    facet_wrap(~ parameter, scales = "fixed", nrow = 2) +  # 4 panels
    scale_x_date(
      date_breaks = "1 year",
      date_labels = "%Y") +
    labs(title = paste0("10-Year Time Series: ", beach),
      x = "Year",
      y = expression(Log[10]*"(Concentration)")) +
    theme_bw(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 0.5),
      legend.position = "none",
      panel.spacing = unit(1, "lines"))
  
  # Save the PNG 
# ggsave(
#  filename = here("outputs", "beach_timeseries_beachname", paste0(gsub("[^A-Za-z0-9]", "_", beach), "_timeseries.png")),
#  plot = beach_plot, width = 15, height = 10,dpi = 400)
  })
```

# Enterococcus Filtered Exceedances

This code creates a new dataframe and plots the exceedances of enterococcus concentrations that are **greater than or equal to 104 MPN/100 mL**. The CPN/100 mL units are treated the same as the MPN/100 mL units.

```{r}
# Create a new data frame of enterococcus concentrations that are exceeding the threshold
entero_only <- beach_clean |>
  filter(parameter == "Enterococcus", #extract only enterococcus
         result >= 104) # extract concentrations greater than or equal to 
```

# E. Coli Filtered Exceedances

This code creates a new dataframe and plots the exceedances of E. coli concentrations that are **greater than or equal to 235 MPN/100 mL**. The CPN/100 mL units are treated the same as the MPN/100 mL units.

```{r}
# Create a new data frame of e. coli concentrations that are exceeding the threshold
ecoli_only <- beach_clean |>
  filter(parameter == "E. Coli", #extract only e. coli
         result >= 235) # extract concentrations greater than or equal to 
```

# Total Coliforms Filtered Exceedances

This code creates a new dataframe and plots the exceedances of total coliforms concentrations that are **greater than or equal to 10,000 MPN/100 mL**. The CPN/100 mL units are treated the same as the MPN/100 mL units.

```{r}
# Create a new data frame of total coliforms concentrations that are exceeding the threshold
total_coli_only <- beach_clean |>
  filter(parameter == "Total Coliforms", #extract only total coliforms
         result >= 10000) # extract concentrations greater than or equal to 
```

# Fecal Coliforms Filtered Exceedances

This code creates a new dataframe and plots the exceedances of fecal coliforms concentrations that are **greater than or equal to 400 MPN/100 mL**. The CPN/100 mL units are treated the same as the MPN/100 mL units.

```{r}
# Create a new data frame of fecal coliforms concentrations that are exceeding the threshold
fecal_coli_only <- beach_clean |>
  filter(parameter == "Fecal Coliforms", #extract only fecal coliforms
         result >= 400) # extract concentrations greater than or equal to 
```

# Master Dataset for Exceedance Values

```{r}
# Combine the 4 datasets of the exceedance values of each FIB parameter into one main dataset. 
exceed_all <- bind_rows(entero_only, ecoli_only, 
                        total_coli_only, fecal_coli_only)

# Create the exceedance statistics for the date for all 10 years
exceed_stats <- exceed_all |>
  mutate(year = lubridate::year(sampledate)) |>
  group_by(parameter) |>
  summarise(
    total_exceed = n(),
    mean_exceed = mean(result, na.rm = TRUE),
    median_exceed = median(result, na.rm = TRUE),
    variance_exceed = var(result, na.rm = TRUE),
    min_exceed = min(result, na.rm = TRUE),
    max_exceed = max(result, na.rm = TRUE))
exceed_stats # print the table
    
# Create the exceedance statistics for the date for all 10 years
exceed_stats_yr <- exceed_all |>
  mutate(year = lubridate::year(sampledate)) |>
  group_by(parameter, year) |>
  summarise(
    total_exceed = n(),
    mean_exceed = mean(result, na.rm = TRUE),
    median_exceed = median(result, na.rm = TRUE),
    variance_exceed = var(result, na.rm = TRUE),
    min_exceed = min(result, na.rm = TRUE),
    max_exceed = max(result, na.rm = TRUE),
    .groups = "drop")
exceed_stats_yr 

```

```{r}
# Create bar graphs to understand the total amount of exceedances for each year

# E. Coli bar 
ecoli_exceed_bar <- ggplot(exceed_stats_yr, 
                           aes(x = year, y = total_exceed),
                           color = parmater) +
  geom_col() +
  scale_color_manual(values = htb_colors) +
  scale_x_date(date_breaks = "1 year",
      date_labels = "%Y") +  
  theme_bw(plot.title = element_text(face = "bold", 
                                     size = 14, hjust = 0.5), 
           axis.text.x = element_text(angle = 0, hjust = 0.5), 
           legend.position = "none")
ecoli_exceed_bar


##### To Be continued
    
    labs(title = paste0("10-Year Time Series: ", station),
      x = "Year",
      y = expression(Log[10]*"(Concentration)")) +
    theme_bw(base_size = 12) +
    
      panel.spacing = unit(1, "lines")
  
```
