---
title: "beach_fib_time_series"
format: 
  html:
    embed-resources: true
    code-line-numbers: true
    code-wrap: true
    code-fold: true
    toc: true
editor: visual
---

# Beach FIB Timeseries Analysis

This code is creating a 10 year timeseries analysis for each beach to understand the trends between the wet and dry periods across 2014-2024. The timeseries data are not connected with a line because the data is not continuous.

```{r, message = false, warning = false}
# Load libraries 
library(dplyr)
library(ggplot2)
library(tidyverse)
library(ggridges)
library(here)
library(lubridate)
library(slider)
library(scales)
library(purrr)
library(janitor)
```

**Loading Data + Clean Data For This Timeseries Analysis**

```{r}
# Clean the beach data and log transform the data
beach_clean <- read.csv(here("data", "clean_master_beach_data_2014_2024.csv")) |>
  mutate(log_result = log10(result), # log 10 transformed the result column
         sample_date = as.Date(sample_date), # make sampledate into a date from a chr
         year = year(sample_date), # New column with only year
         day = day(sample_date),
         month = month(sample_date, label = TRUE, 
                       abbr = TRUE))  # New column with month


# Quick data inspection
unique(beach_clean$station_name) # checking the number of stations in data
unique(beach_clean$beach_name) # checking the number of beaches in data
unique(beach_clean$method) # checking the number of methods in data
unique(beach_clean$unit) # checking the number of units in data
```

```{r}
# Count how many monitoring stations are at each beach 
count_beach <- beach_clean |>
  group_by(beach_name, station_name) |>
  count()
  #  summarise(num_stations = n_distinct(station_name))

# Double check that there are 99 monitoring stations
n_distinct(beach_clean$station_name)
```

**Heal The Bay Brand Colors For GGplot**

This code assigns the the following colors to each FIB parameter: E. Coli, Enterococcus, Total Coliforms, and Fecal Coliforms.

```{r}
htb_colors <- c(
  "E. Coli" = "#40B4EB",
  "Enterococcus" = "#2D94C8",
  "Total Coliforms" = "#8FA9B9",
  "Fecal Coliforms" = "#1479A9")
```

[**Exceedance Values**]{.underline}

-   Total Coliforms - 10,000 MPN/100 mL

-   Fecal Coliforms - 400 MPN/100 mL

-   Enterococcus - 104 MPN/100 mL

-   E. Coli - 235 MPN/100 mL

This code log10 transforms the exceedances threshold values for each FIB parameter, and then combines them into a data frame. This data frame will be used to create horizontal red lines in the following facet wrap graphs for each monitoring station and beach location.

```{r}
# Calculate Log 10 total coliform threshold
log_tc <- log10(10000)

#Calcualte log 10 of fecal coliform threshold
log_fc <- log10(400)

# Calculate log10 of enterococcus threshold
log_entero <- log10(104)

# Calculate log10 of e.coli threshold
log_ecoli <- log10(235)

# Create a dataframe with the log10 thresholds 
log_thresholds <- tibble::tibble(
  parameter = c("Total Coliforms",
                "Fecal Coliforms",
                "Enterococcus",
                "E. Coli"),
  threshold = c(log_tc, log_fc, log_entero, log_ecoli))
```

## **10 Year Time Series Analysis - One PNG Per Station (4 Parameters)**

This code creates a 10 year time series line graph for each log10 transformed result value. Each png is corresponds to a **monitoring location (n = 99)** and it will contain 4 panels if data is available. Each panel represents a different FIB parameters: E. Coli, Enterococcus, Total Coliforms, and Fecal Coliforms.

```{r, warning = FALSE, message = FALSE}
# Split data by station 
station_list <- split(beach_clean, beach_clean$station_name)

# Loop through each station 
walk(names(station_list), function(station) {
  
  # Extract that station's data
  station_df <- station_list[[station]] |>
    arrange(sample_date) # Ensures that the sampledate column is in chronological order
  
  # Create the plot with 4 panels (one per parameter)
  station_plot <- ggplot(station_df, 
                         aes(x = sample_date, 
                             y = log_result, 
                             color = parameter)) +
    geom_point(alpha = 0.6, size = 1.2) +
    geom_hline(data = log_thresholds,
             aes(yintercept = threshold),
             inherit.aes = FALSE,
             linetype = "dashed",
             color = "red",
             linewidth = 0.7) +
    scale_color_manual(values = htb_colors) + # apply brand colors
    facet_wrap(~ parameter, scales = "fixed", nrow = 2) +  # 4 panels
    scale_x_date(
      date_breaks = "1 year",
      date_labels = "%Y") +
    labs(title = paste0("10-Year Time Series: ", station),
      x = "Year",
      y = expression(Log[10]*"(Concentration)")) +
    theme_bw(base_size = 14) +
    theme(
      plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 0.5),
      legend.position = "none",
      panel.spacing = unit(1, "lines"))
  
  # Save the PNG 
#ggsave(filename = here("outputs", "beach_timeseries_all", #paste0(gsub("[^A-Za-z0-9]", "_", station), "_timeseries.png")),
#                       plot = station_plot, width = 15, 
#       height = 8,dpi = 400)
  
print(station_plot)})

```

## **10 Year Time Series Analysis - One PNG Per Beach Per Parameter**

This code creates a 10 year time series line graph for each log10 transformed result value. Each png is corresponds to a **beach location (n = 38)** and it will contain 4 panels if data is available. Each panel represents a different FIB parameters: E.Coli, Enterococcus, Total Coliform, and Fecal Coliforms.

```{r}
# Split data by beach 
beach_list <- split(beach_clean, beach_clean$beach_name)

# Loop through each beach 
walk(names(beach_list), function(beach) {
  
  # Extract that station's data
  beach_df <- beach_list[[beach]] |>
    arrange(sample_date) # Ensures that the sampledate column is in chronological order
  
  # Create the plot with 4 panels (one per parameter)
  beach_plot <- ggplot(beach_df, aes(x = sample_date, y = log_result, color = parameter)) +
    geom_point(alpha = 0.6, size = 1.2) +
    geom_hline(data = log_thresholds,
             aes(yintercept = threshold),
             inherit.aes = FALSE,
             linetype = "dashed",
             color = "red",
             linewidth = 0.7) +
      scale_color_manual(values = htb_colors) + # apply brand colors
    
    facet_wrap(~ parameter, scales = "fixed", nrow = 2) +  # 4 panels
    scale_x_date(
      date_breaks = "1 year",
      date_labels = "%Y") +
    labs(title = paste0("10-Year Time Series: ", beach),
      x = "Year",
      y = expression(Log[10]*"(Concentration)")) +
    theme_minimal(base_size = 12) +
    theme(strip.text = element_text(face = "bold", 
                                    size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    axis.title.x = element_text(face = "bold", size = 12),
    axis.title.y = element_text(face = "bold"),
    legend.position = "none", 
    panel.grid = element_blank())
  
  # Save the PNG 
ggsave(
  filename = here("outputs", "beach_timeseries_beachname", paste0(gsub("[^A-Za-z0-9]", "_", beach), 
                                                     "_timeseries.png")),
  plot = beach_plot, width = 12, height = 10,dpi = 400)
  
print(beach_plot)})
```

## 10 Year Enterococcus Graphs Only

This code was used to develop graphs for the final presentation that focuses only the 10-year timeseries of Enterococcus.

```{r}
# Filter the data to only enterococcus
beach_entero_clean <- beach_clean |>
  filter(parameter == "Enterococcus")

# Split data by beach 
beach_list_2 <- split(beach_entero_clean, beach_entero_clean$beach_name)

# Loop through each beach 
walk(names(beach_list_2), function(beach) {
  
  # Extract that station's data
  beach_df_2 <- beach_list_2[[beach]] |>
    arrange(sample_date) # Ensures that the sample_date column is in chronological order
  
  # Create the plot with enterococcus panels
  beach_plot_2 <- ggplot(beach_df_2, aes(x = sample_date, y = log_result)) +
geom_point(alpha = 0.6, size = 1.2, color = htb_colors["Enterococcus"])+
#geom_hline(yintercept = log_entero,
      #       inherit.aes = FALSE,
      #      linetype = "dashed",
      #      color = "red",
      #       linewidth = 0.7) +
    scale_x_date(breaks = seq(as.Date("2014-01-01"), 
               as.Date("2024-01-01"), 
               by = "1 year"),
  date_labels = "%Y") + 
    labs(title = paste0("10-Year Time Series: ", beach),
      x = "Year",
      y = expression(Log[10] * "(Concentration)")) +
    theme_minimal(base_size = 14) +
    theme(plot.title = element_text(face = "bold", 
                                    hjust = 0.5),
    axis.title.x = element_text(face = "bold", 
                                size = 12),
    axis.title.y = element_text(face = "bold",
                                size = 12),
    legend.position = "none", 
    panel.grid = element_blank())
  
  # Save the PNG 
ggsave(
  filename = here("outputs", "beach_timeseries_entero_only", paste0(gsub("[^A-Za-z0-9]", "_", beach), 
                                                     "_timeseries.png")),
  plot = beach_plot_2, width = 14, height = 7,dpi = 400)
  
print(beach_plot_2)})
```

# Exceedance Master Dataset

## **Exceedance Dataframes**

This code creates a new dataframe assigns the exceedances of Enterococcus (**greater than or equal to 104 MPN/100 mL**.), E. Coli (**greater than or equal to 235 MPN/100 mL)**, Total Coliforms (**greater than or equal to 10,000 MPN/100 mL)**, and Fecal Coliforms (**greater than or equal to 400 MPN/100 mL)** concentrations. The CPN/100 mL units are treated the same as the MPN/100 mL units.

There are a total of 17,889 observations of exceedances across all four parameters across 37 beaches, and 99 monitoring sites out of 208,495 samples collected.

**Precipitation Data**

```{r}
# Read in the Precipitation Data
precip_2014_2024 <- read.csv(here("data","precipitation_clean_2014_2024.csv")) 

# Mutate the Precip Data
precip_clean <- precip_2014_2024 |>
  mutate(date = as.Date(date), # Change date from chr to date
         year = year(date), # extract the year from the date
         day = day(date), # extract day from date
         month = month(date, label = TRUE, abbr = TRUE), # extract month from the date
         wet = prcp_in > 0.1) # defines wet weather as >0.1 inches

# Create the data frame
precip_monthly <- precip_clean |>
  group_by(year,month) |> # group the data by year and month
  summarise(total_rain_in = sum(prcp_in, na.rm = TRUE), # sum the precip total
    .groups = "drop")
```

This code creates a new data frame called "beach_exceed" which assigns a binomial value (1 - exceed, 0 - no exceedance) to each individal sample across all monitoring stations. The data is then joined with the clean precipitation data by month, day, and year. The goal of this data frame is to run a binomial logistic regression to

We know that precipitation varies depending on station and that exceedance values are also dependent on the local environment of the monitoring stations.

```{r}
# Create a new dataframe with the exceedance values & keep nonexceedance values
beach_exceed <- beach_clean |>
  mutate(exceed = case_when(
    parameter == "Enterococcus" & result >= 104 ~ 1,
    parameter == "E. Coli" & result >= 235 ~ 1,
    parameter == "Total Coliforms" & result >= 10000 ~ 1,
    parameter == "Fecal Coliforms" & result >= 400 ~1,
    TRUE ~ 0)) |>
  left_join(precip_clean, by = c("month", "day", "year"))

# Data Check
unique(beach_exceed$exceed)

# Count all exceedance values
exceed_count_all <- beach_exceed |>
  count(exceed) 

# Count exceedance & non-exceedance values by parameter
exceed_count <- beach_exceed |>
  group_by(parameter, exceed) |>
  count(exceed) |>
  ungroup()

# Create a new dataframe with only exceedance values 
exceed_all <- beach_exceed |>
  filter(exceed == "1")
```

## Graph Exceedances

#### Station Exceedance Timeseries

This code creates a facet wrap and graphs for each monitoring station for all 4 FIB parameters and their exceedance values.

```{r}
# Split data by station 
station_list_exceed <- split(exceed_all, exceed_all$station_name)

# Loop through each station 
walk(names(station_list_exceed), function(station) {
  
  # Extract that station's data
  station_df_exceed <- station_list_exceed[[station]] |>
    arrange(sample_date) # Ensures that the sampledate column is in chronological order
  
  # Create the plot with 4 panels (one per parameter)
  station_plot_exceed <- ggplot(station_df_exceed, aes(x = sample_date, y = log_result, color = parameter)) +
    geom_point(alpha = 0.6, size = 1.2) +
    geom_hline(data = log_thresholds,
             aes(yintercept = threshold),
             inherit.aes = FALSE,
             linetype = "dashed",
             color = "red",
             linewidth = 0.7) +
    scale_color_manual(values = htb_colors) + # apply brand colors
    facet_wrap(~ parameter, scales = "fixed", nrow = 2) +  # 4 panels
    scale_x_date(
      date_breaks = "1 year",
      date_labels = "%Y") +
    labs(title = paste0("10-Year Exceedance Time Series: ", station),
      x = "Year",
      y = expression(Log[10]*"(Concentration)")) +
    theme_bw(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", 
                                size = 14, hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 0.5),
      legend.position = "none",
      panel.spacing = unit(1, "lines"))
  
  # Save the PNG 
# ggsave(filename = here("outputs", #"beach_timeseries_exceedances", 
#  "station_exceed", 
#  paste0(gsub("[^A-Za-z0-9]", "_", station),
#         "_exceed_timeseries.png")),
#plot = station_plot_exceed, width = 15, height = 10,dpi = 400)
print(station_plot_exceed)  })
```

#### Beach Exceedance Timeseries

This code plots all 4 FIB parameters at the beach level.

```{r}
# Split data by beach 
beach_list_exceed <- split(exceed_all, exceed_all$beach_name)

# Loop through each beach 
walk(names(beach_list_exceed), function(beach) {
  
  # Extract that station's data
  beach_df_exceed <- beach_list_exceed[[beach]] |>
    arrange(sample_date) # Ensures that the sampledate column is in chronological order
  
  # Create the plot with 4 panels (one per parameter)
  beach_plot_exceed <- ggplot(beach_df_exceed, aes(x = sample_date, y = log_result, color = parameter)) +
    geom_point(alpha = 0.6, size = 1.2) +
    #geom_hline(data = log_thresholds,
    #         aes(yintercept = threshold),
    #         inherit.aes = FALSE,
    #         linetype = "dashed",
    #         color = "red",
    #         linewidth = 0.7) +
      scale_color_manual(values = htb_colors) + # apply brand colors
    facet_wrap(~ parameter, scales = "fixed", nrow = 2) +  # 4 panels
    scale_x_date(
      date_breaks = "1 year",
      date_labels = "%Y") +
    labs(title = paste0("10-Year Exceed Time Series: ", beach),
      x = "Year",
      y = expression(Log[10]*"(Concentration)")) +
    theme_bw(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 0.5),
      legend.position = "none",
      panel.spacing = unit(1, "lines"))
  
  # Save the PNG 
# ggsave(
#  filename = here("outputs", "beach_timeseries_exceedances",
#  "beach_exceed", paste0(gsub("[^A-Za-z0-9]", "_", beach), #"_exceed_timeseries.png")),
#  plot = beach_plot_exceed, width = 15, height = 10,dpi = 400)
print(beach_plot_exceed)  })
```

**Enterococcus Exceedances Only Per Beach**

```{r}
# Loop through each beach
walk(names(beach_list_exceed), function(beach) {
  
  # Extract that beach's data
 beach_df_exceed <- beach_list_exceed[[beach]] |>
    filter(parameter == "Enterococcus") |>
    arrange(sample_date) 
  
  # Create the Enterococcus time-series plot
  entero_exceedance_plot <- ggplot(beach_df_exceed,
                       aes(x = sample_date, y = log_result)) +
    geom_point(color = htb_colors[2], alpha = 0.7, 
               size = 1.3) +
    geom_hline(yintercept = 2.017033,
             linetype = "dashed",
             color = "red",
             linewidth = 0.7) +
    scale_x_date(
      date_breaks = "1 year",
      date_labels = "%Y") +
    labs(title = paste0("10-Year Enterococcus Exceedance: ", beach),
      x = "Year",
      y = expression(Log[10] * "(Concentration)")) +
    
    theme_bw(base_size = 12) +
    theme(plot.title = element_text(face = "bold", 
                                    size = 14, hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 0.5),
      legend.position = "none")
  
#Save the PNG if needed
#ggsave(filename = here("outputs",
#                      "beach_timeseries_exceedances",
#                      "entero_exceed",
#                  paste0(gsub("[^A-Za-z0-9]", "_", beach), #"_Entero_exceed_timeseries.png")),
#       plot = entero_exceedance_plot, width = 15, height = 10, # dpi = 400)
print(entero_exceedance_plot)})
```

**E. Coli Exceedances Only Per Beach**

```{r}
# Loop through each beach
walk(names(beach_list_exceed), function(beach) {
  
  # Extract that beach's data
 beach_df_exceed <- beach_list_exceed[[beach]] |>
    filter(parameter == "E. Coli") |>
    arrange(sample_date) 
  
  # Create the Enterococcus time-series plot
  ecoli_exceedance_plot <- ggplot(beach_df_exceed,
                       aes(x = sample_date, y = log_result)) +
    geom_point(color = htb_colors[1], alpha = 0.7, 
               size = 1.3) +
    geom_hline(yintercept = 2.371068,
             linetype = "dashed",
             color = "red",
             linewidth = 0.7) +
    scale_x_date(
      date_breaks = "1 year",
      date_labels = "%Y") +
    
    labs(title = paste0("10-Year E. Coli Exceedance: ", beach),
      x = "Year",
      y = expression(Log[10] * "(Concentration)")) +
    
    theme_bw(base_size = 12) +
    theme(plot.title = element_text(face = "bold", 
                                    size = 14, hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 0.5),
      legend.position = "none")
  
#Save the PNG if needed
ggsave(filename = here("outputs", "beach_timeseries_exceedances",
                       "ecoli_exceed",
                  paste0(gsub("[^A-Za-z0-9]", "_", beach), "_ecoli_exceed_timeseries.png")),
       plot = ecoli_exceedance_plot, width = 15, height = 10, dpi = 400)
print(ecoli_exceedance_plot)})
```

**Total Coliforms Exceedances Only Per Beach**

```{r}
# Loop through each beach
walk(names(beach_list_exceed), function(beach) {
  
  # Extract that beach's data
 beach_df_exceed <- beach_list_exceed[[beach]] |>
    filter(parameter == "Total Coliforms") |>
    arrange(sample_date) 
  
  # Create the Enterococcus time-series plot
  total_exceedance_plot <- ggplot(beach_df_exceed,
                       aes(x = sample_date, y = log_result)) +
    geom_point(color = htb_colors[3], alpha = 0.7, 
               size = 1.3) +
    geom_hline(yintercept = 4.000000,
             linetype = "dashed",
             color = "red",
             linewidth = 0.7) +
    scale_x_date(
      date_breaks = "1 year",
      date_labels = "%Y") +
    
    labs(title = paste0("10-Year Total Coliforms Exceedance: ", beach),
      x = "Year",
      y = expression(Log[10] * "(Concentration)")) +
    
    theme_bw(base_size = 12) +
    theme(plot.title = element_text(face = "bold", 
                                    size = 14, hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 0.5),
      legend.position = "none")
  
#Save the PNG if needed
#ggsave(filename = here("outputs", #"beach_timeseries_exceedances",
#                       "total_exceed",
#                  paste0(gsub("[^A-Za-z0-9]", "_", beach), #"_total_exceed_timeseries.png")),
#       plot = total_exceedance_plot, width = 15, 
#       height = 10, dpi = 400)
print(total_exceedance_plot)})
```

**Fecal Coliforms** **Exceedances Only Per Beach**

```{r}
# Loop through each beach
walk(names(beach_list_exceed), function(beach) {
  
  # Extract that beach's data
 beach_df_exceed <- beach_list_exceed[[beach]] |>
    filter(parameter == "Fecal Coliforms") |>
    arrange(sample_date) 
  
  # Create the Enterococcus time-series plot
  fecal_exceedance_plot <- ggplot(beach_df_exceed,
                       aes(x = sample_date, y = log_result)) +
    geom_point(color = htb_colors[4], alpha = 0.7, 
               size = 1.3) +
    geom_hline(yintercept = 2.602060,
             linetype = "dashed",
             color = "red",
             linewidth = 0.7) +
    scale_x_date(
      date_breaks = "1 year",
      date_labels = "%Y") +
    
    labs(title = paste0("10-Year Fecal Coliforms Exceedance: ", beach),
      x = "Year",
      y = expression(Log[10] * "(Concentration)")) +
    
    theme_bw(base_size = 12) +
    theme(plot.title = element_text(face = "bold", 
                                    size = 14, hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 0.5),
      legend.position = "none")
  
#Save the PNG if needed
ggsave(filename = here("outputs", "beach_timeseries_exceedances",
                       "fecal_exceed",
                  paste0(gsub("[^A-Za-z0-9]", "_", beach), "_fecal_exceed_timeseries.png")),
       plot = fecal_exceedance_plot, width = 15, height = 10, dpi = 400)
print(fecal_exceedance_plot)})
```

## Statistics on Exceedances

```{r}
# Create the exceedance statistics for the date for all 10 years
exceed_stats <- exceed_all |>
  mutate(year = lubridate::year(sample_date)) |>
  group_by(parameter) |>
  summarise(
    total_exceed = n(),
    mean_exceed = mean(result, na.rm = TRUE),
    median_exceed = median(result, na.rm = TRUE),
    variance_exceed = var(result, na.rm = TRUE),
    min_exceed = min(result, na.rm = TRUE),
    max_exceed = max(result, na.rm = TRUE))
exceed_stats # print the table
    
# Find how many beaches and stations total had exceedances
unique(exceed_all$beach_name)
unique(exceed_all$station_name)

```

```{r}
# Create the exceedance statistics for the date for all 10 years
exceed_stats_yr <- exceed_all |>
  mutate(year = lubridate::year(sample_date)) |>
  group_by(parameter, year) |>
  summarise(
    total_exceed = n(),
    mean_exceed = mean(result, na.rm = TRUE),
    median_exceed = median(result, na.rm = TRUE),
    variance_exceed = var(result, na.rm = TRUE),
    min_exceed = min(result, na.rm = TRUE),
    max_exceed = max(result, na.rm = TRUE),
    .groups = "drop")
exceed_stats_yr 

```

```{r}
# Create the boxplot
exceedance_box <- ggplot(exceed_stats_yr, aes(x = factor(year), y = total_exceed)) +
  geom_boxplot(alpha = 0.6, size = 1.0, fill = htb_colors[1]) +
  geom_point(alpha = 0.6, size = 1.5, color = htb_colors[2]) +
  labs(
    title = "Distribution of Exceedances by Year",
    x = "Year",
    y = "Exceedance Count"
  ) +
  theme_bw(12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(face = "bold", hjust = 0.5))

print(exceedance_box)

# Save the plot
#ggsave(
#  filename = here("outputs", "beach_timeseries_exceedances", #"annual_exceed_boxplot.png"),
#  plot = exceedance_box,
#  width = 10,
#  height = 6,
#  dpi = 400)
```

**Research Question: What beach had the highest total number of exceedances across all 10 years.**

```{r}
# Calculate the total exceedances for each beach by parameter
beach_exceed_stats_total <- exceed_all |>
  mutate(year = lubridate::year(sample_date)) |>
  group_by(parameter, beach_name) |>
  summarise(
    total_exceed = n(),
    mean_exceed = mean(result, na.rm = TRUE),
    median_exceed = median(result, na.rm = TRUE),
    variance_exceed = var(result, na.rm = TRUE),
    min_exceed = min(result, na.rm = TRUE),
    max_exceed = max(result, na.rm = TRUE),
    .groups = "drop")
beach_exceed_stats_total 


exceed_ranked_tables <- beach_exceed_stats_total |>
  group_by(parameter) |>
  arrange(parameter, desc(total_exceed)) |>
  mutate(rank = row_number()) |>
  select(parameter, rank, beach_name, total_exceed) |>
  ungroup()
exceed_ranked_tables
```

## Exceedance Percentages

**Goal:** This code shows **cumulative** exceedance for all four FIB parameters since any exceedance will trigger a beach advisory. X-axis represents monitoring sites and y-axis represents exceedance percentages. Yellow highlighted column visualizes the month with highest average exceedance percentages across the monitoring years.

```{r}
# Calculate the total exceedances for each beach by parameter
station_exceed_total <- exceed_all |>
  mutate(year = lubridate::year(sample_date)) |>
  group_by(station_name, month) |>
  summarise(
    total_exceed = n(),
    mean_exceed = mean(result, na.rm = TRUE),
    median_exceed = median(result, na.rm = TRUE),
    variance_exceed = var(result, na.rm = TRUE),
    min_exceed = min(result, na.rm = TRUE),
    max_exceed = max(result, na.rm = TRUE),
    .groups = "drop")
station_exceed_total 
```

## Simple Logit Binomial Model

**FIB Exceedance Data**

This code aggregates the monthly exceedances that occur across the 99 monitoring stations.

```{r}
# Calculate the monthly exceedance values 
monthly_exceed <- beach_exceed |>
  group_by(year, month, station_name) |>
  summarise(
    n = n(), # count samples 
    e = sum(exceed, na.rm = TRUE),
    exceed_pct = (e / n) * 100,
    .groups = "drop")

# Calculate total exceedance values
total_exceed <- beach_exceed |>
  group_by(station_name) |>
  summarise(n = n(), 
            e = sum(exceed, na.ra = TRUE),
            groups = "drop")
```

**FIB v Rain Statistics**

[**Equation**]{.underline}: Natural log (p/1-p) =β0​+β1​(rain)+β2​(station)

-   p represents the probability of an exceedance occuring that month

-   Caveat: This regression looks at exceedances per month, which is often in relation to reporting requirements and compliance. However, we know that FIB tends to spike between 3-5 days after a rain event.

The binomial logistic regressions was conducted to understand the relationship the odds an exceedance is to occur if there is zero rain compared to one inch of rain. The baseline scenario (𝛽0) uses a baseline station (B_10) by default in R, to calculate the intercept and the rain variable.

The outputs include an intercept value (-3.248290 +- 0.097580947) and total rain in inches (0.391650 +- 0.004568562).

[**General Interpretation**]{.underline}: When there is zero rain, the likelihood of an exceedance is low. When there is one inch of rain, the likelihood of exceedance is high.

Technical Interpretation:

**Log-odds that an exceedance is to occur is based on this equation:**

Log-odds of an exceedance occurring = -3.248290 + 0.391650x

-   x represents the total rain (in inches)

**Probability when 0 inches of Rain Occurs**

Probability = e\^-3.248290 /(1-e\^-3.248290)

**Probability when 1 inches of Rain Occurs**

For each additional inch of rainfall, the odds of exceedance for that month is 48%.

This was calculated using this equation e^0.391650^ + e^0.004568562^ .

```{r}
# Running the regression for all stations
exceed_glm <- glm(
  cbind(e, n - e) ~ total_rain_in + station_name,
  family = binomial(link = "logit"),
  data = monthly_exceed)
exceed_glm

# Create the table
exceed_glm_coef_table <- summary(exceed_glm)$coefficients

# Save as CSV
#write.csv(exceed_glm_coef_table,
#  here("data", "exceed_v_prcp_stat_coef.csv"),
#  row.names = TRUE)

# Find which station was used as a baseline scenario (B_10)
#monthly_exceed$station_name <- as.factor#(monthly_exceed$station_name)
#levels(monthly_exceed$station_name)
```

```{r}
pred_data$prob <- predict(
  exceed_glm,
  newdata = pred_data,
  type = "response"
)
ggplot() +
  geom_point(
    data = monthly_exceed,
    aes(total_rain_in, e/n),
    alpha = 0.4
  ) +
  geom_line(
    data = pred_data,
    aes(total_rain_in, prob),
    linewidth = 1.2
  ) +
  labs(
    x = "Monthly Rainfall (inches)",
    y = "Probability of Exceedance",
    title = "Predicted Probability of FIB Exceedance vs Rainfall"
  )
```

```{r}
# Calculate baseline probability %
(exp(-3.248290)/(1 + exp(-3.248290)))*100


# Calculate the probability an exceedance were to occur if there was a 1 in increase in total rain 
(exp(0.391650))*100
(exp(0.004568562))*100
  
```

### Top 10 Sites

These top 10 sites were based on Lili's analysis for the top 10 sites with the highest amount of exceedances. The top 10 sites included the following monitorinig stations:

1.   SMB-3-3
2.  MDRH-3
3.  MDRH-2
4.  MDRH-1
5.  CB-02
6.  SMB-MC-2
7.  SMB-3-4
8.  SMB-1-18
9.  SMB-2-7
10. SMB-1-12

```{r}
coef_df <- exceed_glm_coef_table |>
  as.data.frame() |>
    rownames_to_column(var = "term")


exceed_top_10 <- coef_df |>
  filter(term %in% c("station_nameSMB-3-3", 
                     "station_nameMDRH-3",
         "station_nameMDRH-2", "station_nameMDRH-1",
         "station_nameCB-02", "station_nameSMB-MC-2",
         "station_nameSMB-3-4", "station_nameSMB-1-18",
         "station_nameSMB-2-7", "station_nameSMB-1-12"))
exceed_top_10

```
