---
title: "beach_fib_average_monthly"
format: html
editor: visual
---

## Beach FIB Average Monthly

Average all the beaches each month for each year. Then analyze on a year to year basis and have it be 1 year at a time.

```{r, message = false, warning = false}
# Load libraries 
library(dplyr)
library(ggplot2)
library(tidyverse)
library(ggridges)
library(here)
library(lubridate)
library(slider)
library(scales)
library(janitor)
```

**Heal The Bay Brand Colors For GGplot**

This code creates a color gradient for the graphs based on the Heal The Bay (HTB)'s brand colors. It creates 18 types of colors based on the 5 given brand colors.

```{r, message = false, warning = false}
htb_colors <- c(
  "E. Coli" = "#40B4EB",
  "Enterococcus" = "#2D94C8",
  "Total Coliforms" = "#8FA9B9",
  "Fecal Coliforms" = "#1479A9")
```

```{r, message = false, warning = false}
# Read the file
beach_data_2014_2024 <- read.csv(here("data","clean_master_beach_data_2014_2024.csv")) 

# Clean the data
beach_clean <- beach_data_2014_2024 |>
  mutate(result_log = log10(result), # log 10 transform the data
         sampledate = as.Date(sampledate), # change from chr to date
         year = year(sampledate),
         month = month(sampledate, label = TRUE, abbr = TRUE))
```

## Yearly distribution boxplots

**2014 Yearly Box Plot**

```{r, message = false, warning = false}
#Create New Data Frame 
beach_2014 <- beach_clean |> 
  filter(year == 2014)

# Create the average values of each month in the year 2014
beach_monthly_2014 <- beach_2014 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2014_box <- ggplot(beach_monthly_2014,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2014)",
    x = "Month",
    y = "Monthly Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave(filename = here("outputs", "beach_fib_average_monthly", "beach_fib_monthly_2014_plot.png"),
  plot = beach_monthly_2014_box, width = 21, height = 12, dpi = 400)
```

**2015 Yearly Box Plot**

```{r, message = false, warning = false}
#Create New Data Frame 
beach_2015 <- beach_clean |> 
  filter(year == 2015)

# Create the average values of each month in the year 2014
beach_monthly_2015 <- beach_2015 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2015_box <- ggplot(beach_monthly_2015,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2015)",
    x = "Month",
    y = "Monthly Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave(filename = here("outputs", "beach_fib_average_monthly", "beach_fib_monthly_2015_plot.png"),
  plot = beach_monthly_2015_box, width = 21, height = 12, dpi = 400)
```

**2016 Yearly Box Plot**

```{r, message = false, warning = false}
#Create New Data Frame 
beach_2016 <- beach_clean |> 
  filter(year == 2016)

# Create the average values of each month in the year 2014
beach_monthly_2016 <- beach_2016 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2016_box <- ggplot(beach_monthly_2016,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2016)",
    x = "Month",
    y = "Monthly Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave(filename = here("outputs", "beach_fib_average_monthly", "beach_fib_monthly_2016_plot.png"),
  plot = beach_monthly_2016_box, width = 21, height = 12, dpi = 400)
```

**2017 Yearly Box Plot**

```{r, message = false, warning = false}
#Create New Data Frame 
beach_2017 <- beach_clean |> 
  filter(year == 2017)

# Create the average values of each month in the year 2014
beach_monthly_2017 <- beach_2017 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2017_box <- ggplot(beach_monthly_2017,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2017)",
    x = "Month",
    y = "Monthly Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave(filename = here("outputs", "beach_fib_average_monthly", "beach_fib_monthly_2017_plot.png"),
  plot = beach_monthly_2017_box, width = 21, height = 12, dpi = 400)
```

**2018 Yearly Box Plot**

```{r, message = false, warning = false}
#Create New Data Frame 
beach_2018 <- beach_clean |> 
  filter(year == 2018)

# Create the average values of each month in the year 2014
beach_monthly_2018 <- beach_2018 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2018_box <- ggplot(beach_monthly_2018,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2018)",
    x = "Month",
    y = "Monthly Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave(filename = here("outputs", "beach_fib_average_monthly", "beach_fib_monthly_2018_plot.png"),
  plot = beach_monthly_2018_box, width = 21, height = 12, dpi = 400)
```

**2019 Yearly Box Plot**

```{r, message = false, warning = false}
#Create New Data Frame 
beach_2019 <- beach_clean |> 
  filter(year == 2019)

# Create the average values of each month in the year 2014
beach_monthly_2019 <- beach_2019 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2019_box <- ggplot(beach_monthly_2019,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2019)",
    x = "Month",
    y = "Monthly Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave(filename = here("outputs", "beach_fib_average_monthly", "beach_fib_monthly_2019_plot.png"),
  plot = beach_monthly_2019_box, width = 21, height = 12, dpi = 400)
```

**2020 Yearly Box Plot**

```{r, message = false, warning = false}
#Create New Data Frame 
beach_2020 <- beach_clean |> 
  filter(year == 2020)

# Create the average values of each month in the year 2014
beach_monthly_2020 <- beach_2020 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2020_box <- ggplot(beach_monthly_2020,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2020)",
    x = "Month",
    y = "Monthly Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave( filename = here("outputs", "beach_fib_average_monthly", "beach_fib_monthly_2020_plot.png"),
  plot = beach_monthly_2020_box, width = 21, height = 12, dpi = 400)
```

**2021 Yearly Box Plot**

```{r, message = false, warning = false}
#Create New Data Frame 
beach_2021 <- beach_clean |> 
  filter(year == 2021)

# Create the average values of each month in the year 2014
beach_monthly_2021 <- beach_2021 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2021_box <- ggplot(beach_monthly_2021,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2021)",
    x = "Month",
    y = "Monthly Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave( filename = here("outputs", "beach_fib_average_monthly", "beach_fib_monthly_2021_plot.png"),
  plot = beach_monthly_2021_box, width = 21, height = 12, dpi = 400)
```

**2022 Yearly Box Plot**

```{r, message = false, warning = false}
#Create New Data Frame 
beach_2022 <- beach_clean |> 
  filter(year == 2022)

# Create the average values of each month in the year 2014
beach_monthly_2022 <- beach_2022 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2022_box <- ggplot(beach_monthly_2022,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2022)",
    x = "Month",
    y = "Monthly Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave( filename = here("outputs", "beach_fib_average_monthly", "beach_fib_monthly_2022_plot.png"),
  plot = beach_monthly_2022_box, width = 21, height = 12, dpi = 400)
```

**2023 Yearly Box Plot**

```{r, message = false, warning = false}
#Create New Data Frame 
beach_2023 <- beach_clean |> 
  filter(year == 2023)

# Create the average values of each month in the year 2014
beach_monthly_2023 <- beach_2023 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2023_box <- ggplot(beach_monthly_2023,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2023)",
    x = "Month",
    y = "Monthly Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave( filename = here("outputs", "beach_fib_average_monthly", "beach_fib_monthly_2023_plot.png"),
  plot = beach_monthly_2023_box, width = 21, height = 12, dpi = 400)
```

**2024 Yearly Box Plot**

```{r, message = false, warning = false}
#Create New Data Frame 
beach_2024 <- beach_clean |> 
  filter(year == 2024)

# Create the average values of each month in the year 2014
beach_monthly_2024 <- beach_2024 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2024_box <- ggplot(beach_monthly_2024,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2024)",
    x = "Month",
    y = "Monthly Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave( filename = here("outputs", "beach_fib_average_monthly", "beach_fib_monthly_2024_plot.png"),
  plot = beach_monthly_2024_box, width = 21, height = 12, dpi = 400)
```

```         
```
