---
title: "beach_fib_average_monthly"
format: html
editor: visual
---

## Beach FIB Average Monthly

Average all the beaches each month for each year. Then analyze on a year to year basis and have it be 1 year at a time.

```{r, message = false, warning = false}
# Load libraries 
library(dplyr)
library(ggplot2)
library(tidyverse)
library(ggridges)
library(here)
library(lubridate)
library(slider)
library(scales)
library(janitor)
```

**Heal The Bay Brand Colors For GGplot**

This code creates a color gradient for the graphs based on the Heal The Bay (HTB)'s brand colors. It creates 18 types of colors based on the 5 given brand colors.

```{r, message = false, warning = false}
htb_colors <- c(
  "E. Coli" = "#40B4EB",
  "Enterococcus" = "#2D94C8",
  "Total Coliforms" = "#8FA9B9",
  "Fecal Coliforms" = "#1479A9")
```

```{r, message = false, warning = false}
# Read the file
beach_data_2014_2024 <- read.csv(here("data","clean_master_beach_data_2014_2024.csv")) 

# Clean the data
beach_clean <- beach_data_2014_2024 |>
  mutate(result_log = log10(result), # log 10 transform the data
         sampledate = as.Date(sampledate), # change from chr to date
         year = year(sampledate),
         month = month(sampledate, label = TRUE, abbr = TRUE))
```

## Yearly distribution boxplots

**2014 Yearly Box Plot**

```{r, message = false, warning = false}
#Create New Data Frame 
beach_2014 <- beach_clean |> 
  filter(year == 2014)

# Create the average values of each month in the year 2014
beach_monthly_2014 <- beach_2014 |> 
  group_by(stationname, parameter, month) |> 
  summarise(monthly_mean_log = mean(result_log, na.rm = TRUE),
            n_samples = n(), .groups = "drop") # Ungroups the values to allow for plotting)
```

```{r}
# Create box plot
beach_monthly_2014_box <- ggplot(beach_monthly_2014,
  aes(x = month, y = monthly_mean_log, fill = parameter)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +   # boxplot
  geom_jitter(
    aes(color = parameter),
    position = position_jitter(width = 0.15, height = 0),
    size = 1,alpha = 0.6) +                                               # points
  facet_wrap(~ parameter, ncol = 2, scales = "free_y") +  # 4 panels
  scale_fill_manual(values = htb_colors) +
  scale_color_manual(values = htb_colors) +
  labs(
    title = "Monthly Average FIB Concentrations Across All Sites (2014)",
    x = "Month",
    y = "Monthly Mean Log₁₀ Concentration") +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "none")

# Save the Plot 
ggsave( filename = here("outputs", "beach_fib_average_monthly", "beach_fib_monthly_2014_plot.png"),
  plot = beach_monthly_2014_box, width = 15, height = 12, dpi = 400)
```

**2015 Yearly Box Plot**

```{r}

```

**2016 Yearly Box Plot**

**2017 Yearly Box Plot**

**2018 Yearly Box Plot**

**2019 Yearly Box Plot**

**2020 Yearly Box Plot**

**2021 Yearly Box Plot**

**2022 Yearly Box Plot**

**2023 Yearly Box Plot**

**2024 Yearly Box Plot**

# 

```{r}

```

## Box Plot Graphs for Each Station Monthly on a Year to Year Basis

```{r}
# Split data by station ----
station_list <- split(beach_monthly, beach_monthly$stationname)

# Loop through each station ----
walk(names(station_list), function(station) {
  
  # Extract that station's data
  station_df <- station_list[[station]] |>
    arrange(sampledate) # This code ensures that the sampledate column is in chronological order
  
  # Create the plot with 4 panels (one per parameter)
  station_plot <- ggplot(station_df, aes(x = sampledate, y = log_result, color = parameter)) +
    geom_line(aes(group = parameter), linewidth = 0.6, alpha = 0.8) +  # connect in date order
      scale_color_manual(values = htb_colors) +              # apply your custom brand palette
    geom_point(alpha = 0.6, size = 1.2) +
    facet_wrap(~ parameter, scales = "free_y", nrow = 2) +  # 4 panels
    scale_color_manual(values = htb_colors) +
    scale_x_date(
      date_breaks = "1 month",
      date_labels = "%M"
    ) +
    labs(
      title = paste0("10-Year Time Series: ", station),
      x = "Month",
      y = expression(Log[10]*"(Concentration)"),
      color = "Parameter"
    ) +
    theme_bw(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
      axis.text.x = element_text(angle = 0, hjust = 1),
      legend.position = "none",
      panel.spacing = unit(1, "lines")
    )
  
  # Save the PNG ----
 ggsave(
  filename = here("outputs", "beach_monthly_yty", paste0(gsub("[^A-Za-z0-9]", "_", station), "_timeseries.png")),
  plot = station_plot,
  width = 15,
  height = 10,
  dpi = 400)
  
  message("✅ Saved plot for: ", station)
}) # yty represents year to year
```

```{r}
```

### Yearly distribution boxplots

```{r}
annual_box <- ggplot(data_yr, aes(x = factor(year), y = new_avg_score)) +
  geom_boxplot() +
  labs(x = "Year",
       y = "Avg E.Coli value",
       title = "Annual FIB trends across all sites") +
  theme_bw()

ggsave(here("figures", "annual_box.png"), plot = annual_box, width = 6, height = 3, units = "in", dpi = 300)
```

```         
```
