---
title: "wmms_clean_data"
format: 
 html:
    embed-resources: true
    code-line-numbers: true
    code-wrap: true
    code-fold: true
    toc: true
author: Tina Tran 
editor: visual
warning: false
messages: false 
---

# WMMS Clean Data

**Load Libraries**

```{r, warning = FALSE, message = FALSE}
# Load library 
library(tidyverse)
library(here)
library(janitor)
library(ggplot2)
library(dplyr)
library(stringr)
library(readxl) # Read excel files
library(purrr)
```

**Overview**

The standard output model was selected for WMMS 2.0. WMMS 2.0 modeled the following parameters for the 20 total jurisheds (10 parks and 10 school recommendations) selected for this project's recommendations.

The data ouput filles include a jurished file, landuse, and stream (Note: some jurisheds have a pointsource output file, but it will not be used for the analysis for this project).

[**Output Parameters for Jurished Data:**]{.underline}\
TT Time interval: 60 min Output option: day\
TT PREC precipitation (rain + snow) volume (in-acre/day)\
TT SURO surface outflow volume (in-acre/day)\
TT IFWO interflow outflow volume (in-acre/day)\
TT AGWO groundwater outflow volume (in-acre/day)\
TT PERO total outflow rate volume (SURO+IFWO+AGWO) (in-acre/day)\
TT DEP stream depth (ft)\
TT AVDEP stream average depth (ft)\
TT TAU bed shear stress (kg/m\^2)\
TT RO total rate of outflow from RCHRES (cfs)\
TT SOSED sediments load from land (english tons/da**y)**\
TT SSEDOUT1 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT2 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT3 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT total suspended solid concentration in outflow from the RCHRES (mg/l)\
TT POQUAL1 total flux of QUAL from the PLS_TN (lb/day)\
TT POQUAL2 total flux of QUAL from the PLS_TP (lb/day)\
TT POQUAL3 total flux of QUAL from the PLS_TCd (lb/day)\
TT POQUAL4 total flux of QUAL from the PLS_TCu (lb/day)\
TT POQUAL5 total flux of QUAL from the PLS_TPb (lb/day)\
TT POQUAL6 total flux of QUAL from the PLS_TZn (lb/day)\
TT CONC1 TN dissolved concentration (average) in RCHRES (mg/l)**\
**TT CONC2 TP dissolved concentration (average) in RCHRES (mg/l)\
TT CONC3 TCd dissolved concentration (average) in RCHRES (ug/l)\
TT CONC4 TCu dissolved concentration (average) in RCHRES (ug/l)\
TT CONC5 TPb dissolved concentration (average) in RCHRES (ug/l)\
TT CONC6 TZn dissolved concentration (average) in RCHRES (ug/l)

For the purpose of estimating potential fecal indicator bacteria (FIB) loading in the jurished, sediment (SOSED), nitrogen (CONC1 TN), and surface outflow volume (SURO) have been selected as a proxy. WMMS 2.0 uses daily precipitation data from 2006-2018 to estimate these output parameters for 2008-2018.

## **Folder Pathways**

**Park Recommendations**

```{r}
# Locate the Dominguez Channel 2113 Folder
dc_2113_folder <- here("data", "wmms", "park_rec", "dc_2113")

# Locate the Dominguez Channel 2074 Folder
dc_2074_folder <- here("data", "wmms", "park_rec", "dc_2074")

# Locate the Los Angeles River 6387 Folder
lar_6387_folder <- here("data", "wmms", "park_rec", "lar_6387")

# Locate the Los Angeles River 6396 Folder
lar_6396_folder <- here("data", "wmms", "park_rec", "lar_6396")

# Locate the Los Angeles River 6480 Folder
lar_6480_folder <- here("data", "wmms", "park_rec", "lar_6480")

# Locate the San Gabriel 5109 Folder
sg_5109_folder <- here("data", "wmms", "park_rec", "sg_5109")

# Locate the San Gabriel 5118 Folder
sg_5118_folder <- here("data", "wmms", "park_rec", "sg_5118")

# Locate the San Gabriel 5120 Folder
sg_5120_folder <- here("data", "wmms", "park_rec", "sg_5120")

# Locate the Santa Monica 1030 Folder
sm_1030_folder <- here("data", "wmms", "park_rec", "sm_1030")

# Locate the Santa Monica 1077 Folder
sm_1077_folder <- here("data", "wmms", "park_rec", "sm_1077")
```

**School Recommendations**

```{r}
# Locate the Dominguez Channel 2034 Folder
dc_2034_folder <- here("data", "wmms", "school_rec", "dc_2034")

# Locate the Dominguez Channel 2088 Folder
dc_2088_folder <- here("data", "wmms", "school_rec", "dc_2088")

#Locate the Dominguez Channel 2122 Folder
dc_2122_folder <- here("data", "wmms", "school_rec", "dc_2122")

# Locate the Los Angeles River 6873 Folder
lar_6873_folder <- here("data", "wmms", "school_rec", "lar_6873")

# Locate the Los Angeles River 6682 Folder
lar_6682_folder <- here("data", "wmms", "school_rec", "lar_6682")

# Locate the Los Angeles River 6697 Folder
lar_6697_folder <- here("data", "wmms", "school_rec", "lar_6697")

# Locate the Los Angeles River 6925 Folder
lar_6925_folder <- here("data", "wmms", "school_rec", "lar_6925")

# Locate the Santa Monica 1067 Folder
sm_1067_folder <- here("data", "wmms", "school_rec", "sm_1067")

# Locate the Santa Monica 1110 Folder
sm_1110_folder <- here("data", "wmms", "school_rec", "sm_1110")

# Locate the Santa Monica 1061 Folder
sm_1061_folder <- here("data", "wmms", "school_rec", "sm_1061")

```

## **CSV File from the excel sheets**

## **Process All Jurisheds**

```{r}
# Create a Jurished List 
jurisheds <- list(
  # Park Recommendations
  juri2074 = list(folder = dc_2074_folder, 
                  file="juri_dc_2074.csv"),
  juri2113 = list(folder = dc_2113_folder, 
                  file="juri_dc_2113.csv"),
  juri6387 = list(folder = lar_6387_folder, 
                  file="juri_lar_6387.csv"),
  juri6396 = list(folder = lar_6396_folder, 
                  file="juri_lar_6396.csv"),
  juri6480 = list(folder = lar_6480_folder, 
                  file="juri_lar_6480.csv"),
  juri5109 = list(folder = sg_5109_folder, 
                  file="juri_sg_5109.csv"),
  juri5118 = list(folder = sg_5118_folder, 
                  file="juri_sg_5118.csv"),
  juri5120 = list(folder = sg_5120_folder, 
                  file="juri_sg_5120.csv"),
  juri1030 = list(folder = sm_1030_folder, 
                  file="juri_sm_1030.csv"),
  juri1077 = list(folder = sm_1077_folder, 
                  file="juri_sm_1077.csv"),
  
  # School Recommendations
  juri2034 = list(folder = dc_2034_folder, 
                  file="juri_dc_2034.csv"),
  juri2088 = list(folder = dc_2088_folder, 
                  file="juri_dc_2088.csv"),
  juri2122 = list(folder = dc_2122_folder, 
                  file="juri_dc_2122.csv"),
  juri6873 = list(folder = lar_6873_folder, 
                  file="juri_lar_6873.csv"),
  juri6682 = list(folder = lar_6682_folder, 
                  file="juri_lar_6682.csv"),
  juri6697 = list(folder = lar_6697_folder, 
                  file="juri_lar_6697.csv"),
  juri6925 = list(folder = lar_6925_folder, 
                  file="juri_lar_6925.csv"),
  juri1067 = list(folder = sm_1067_folder, 
                  file="juri_sm_1067.csv"),
  juri1110 = list(folder = sm_1110_folder, 
                  file="juri_sm_1110.csv"),
  juri1061 = list(folder = sm_1061_folder, 
                  file="juri_sm_1061.csv"))
```

```{r}
# Convert all existing jurished excel files into a csv and add it to the existing folder

#walk(jurisheds, function(j){

#  excel_file <- sub("\\.csv$", ".xlsx", j$file)
#  excel_path <- here(j$folder, excel_file)

#  if(file.exists(excel_path)){

#    message("Converting: ", excel_file)

#    juri_xl <- read_excel(excel_path, skip = 51)

#    write.csv(juri_xl,
#      here(j$folder, j$file),
#      row.names = FALSE)

#  } else {

#    message("Missing file: ", excel_file)}})
```

## **Loading Calcualtions**

**Function**

This code reads and cleans in all of the WMMS 2.0 jurished csv files (n = 20) that had estimated the daily loading parameters for various pollutants and precipitation from 2008-2018 using the standard model output setting. The function also converts units based on the methods from the Los Angeles County Department of Public Works (LACDPW) excel sheet calculations.

To estimate the potential watershed capture, the following information was calculated from the daily 2008-2018 output:

-   **Average**: average daily surface outflow volume (acre-ft/day)

-   **High**: maximum daily surface outflow volume (acre-ft/day)

-   **10-year storm:** daily storm runoff volume corresponding to the 90th percentile of wet-day storm volumes (acre-ft/day)

-   **100-year storm:** daily storm runoff volume corresponding to the 99th percentile of wet-day storm volumes (acre-ft/day)

-   **Total 85th Percentile Runoff Volume:** daily storm runoff volume corresponding to the 85th percentile of a wet-day storm volume (acre-ft/day), used as as a treatment capture threshold.

```{r}
# Create a loop to process all jurished files 
process_juri <- function(folder, file_name){

  # Read and clean data  
  juri_load <- read.csv(here(folder, file_name)) |>
    clean_names() |> # make everything lowersnakecase
    rename_with(~ str_remove(.x, "^tt_") |> # removes "tt_" from names
                  str_extract("^[^_]+"), # keep the abbreviated name before "_"
                starts_with("tt_"))|> # renaming only for columns with tt
    select(subbasin, year, month, day, prec,
           suro, ifwo, agwo, pero, dep, avdep, ro,
           sosed, conc1, conc2) |> # keep these columns 
    rename(depth = dep, # depth of the stream (ft)
      tn_mg_l = conc1, # conc1 is total nitrogen (mg/L)
      tp_mg_l = conc2) |> # conc2 is total phosphorous (mg/L)
    mutate(
      date = as.Date(paste(year, month, day, sep="-")),
      suro_ft_acre_day = suro / 12, # convert surface outflow volume to ft-acre/day from in-acre/day
      pero_ft_acre_day = pero / 12, # convert total outflow rate volume to ft-acre/day from in-acre/day
      tn_lb_ac_ft = tn_mg_l * 2.71936, # convert total nitrogen to ac-lb/ft
      tp_lb_ac_ft = tp_mg_l * 2.71936, # convert total phosphorous to ac-lb/ft
      
      # Add new column for storm days and storm volume 
      storm_volume_ac_ft_day = if_else(prec > 0, #dry days = 0
                                       suro_ft_acre_day, 0),
      
      # Total Nitrogen Loading 
      tn_load_lb_day = tn_lb_ac_ft * suro_ft_acre_day)  
  
  

  
# Calculate Watershed Capture Analysis Information 
storm_vals <- juri_load$storm_volume_ac_ft_day[juri_load$prec > 0]

  # Create the 10-year storm 
  storm_90th <- quantile(storm_vals, .90, na.rm=TRUE)
  
  # Create the 100-yr storm 
  storm_99th <- quantile(storm_vals, .99, na.rm=TRUE)
  
  # Create the Runoff 85th Percentile 
  runoff_85th <- quantile(storm_vals, .85, na.rm=TRUE)
  
  
  
# Watershed capture Analysis Table
  capture_summary <- juri_load |>
    summarise(
      avg_suro_acft_day = mean(suro_ft_acre_day, na.rm = TRUE),
      max_suro_acft_day = max(suro_ft_acre_day, na.rm = TRUE),

      # Only storms (wet days)
      avg_storm_vol_acft_day = mean(storm_vals, na.rm = TRUE),
      max_storm_vol_acft_day = max(storm_vals, na.rm = TRUE),

      perc_85_acft_day = runoff_85th,
      perc_90_acft_day = storm_90th,
      perc_99_acft_day = storm_99th)


# Table - Estimate Loading Per Day Per Year
loading_table <- juri_load |>
  group_by(year) |>
  
            # Dissolved Nitrogen Loading 
  summarise(total_tn_lb_yr = sum(tn_load_lb_day, na.rm = TRUE),
            avg_tn_lb_day = mean(tn_load_lb_day, na.rm = TRUE), 
            
            # Sediment loading
            total_sed_lb_yr = sum(sosed, na.rm = TRUE),
            avg_sed_lb_day = mean(sosed, na.rm = TRUE),
            
            # Surface Outflow Volume
            total_suro_acft_yr = sum(suro_ft_acre_day, 
                                      na.rm = TRUE),
            avg_suro_acft_day = mean(suro_ft_acre_day, 
                                     na.rm = TRUE),
            .groups = "drop")
                              

  
# Calulcate Loading Reductions Per Day
  juri_load <- juri_load |>
    
    mutate(
      
      # Calculate the potential capture fraction
      capture_frac = if_else(suro_ft_acre_day > 0,
                             pmin(runoff_85th / suro_ft_acre_day, 
                                  1), 0),
      tn_reduce_lb_day = tn_load_lb_day * capture_frac,
      sed_reduce_tons_day = sosed * capture_frac)

  # Table - Wet Days Reduction Calculations Per Day Per Year
  reduction_table <- juri_load |>
    filter(prec > 0) |>
    group_by(year) |>
    summarise(
      total_tn_reduce_per_wet_yr = sum(tn_reduce_lb_day,  # total nitrogen reeduction per wet day per year (lb/year)
                             na.rm=TRUE), 
      avg_tn_reduce_per_wet_day = mean(tn_reduce_lb_day, 
                                na.rm=TRUE),
      
      total_sed_reduce_per_wet_yr = sum(sed_reduce_tons_day , # total sediment per wet day
                              na.rm=TRUE), 
      avg_sed_reduce_per_wet_day = mean(sed_reduce_tons_day, # average sediment per wet day
                                 na.rm=TRUE), 
      total_suro_wet_yr = sum(suro_ft_acre_day, na.rm=TRUE), # surface runoff volume
      avg_suro_wet_day = mean(suro_ft_acre_day, na.rm=TRUE),

      total_pero = sum(pero_ft_acre_day, na.rm=TRUE), # total outflow
      avg_pero = mean(pero_ft_acre_day, na.rm=TRUE),

      wet_days = n(), # count number of wet days 
      .groups="drop")

  
# Table - Percent Reduction based on 85th Percentile Capture 
  percent_reduction_table <- loading_table |>
    left_join(reduction_table, by = "year") |>
    mutate(
      
      # Calculate Nitrogen Percent Reduction
      pct_tn_reduction = (total_tn_reduce_per_wet_yr / total_tn_lb_yr)*100,
      
      # Calculate Sediment Percent Reduction
      pct_sed_reduction = (total_sed_reduce_per_wet_yr / total_sed_lb_yr)*100,
      
      # Surface runoff capture percentage (volume)
      pct_volume_capture = (total_suro_wet_yr / total_suro_acft_yr) * 100)
  
  
  
  # Table - 10-year averages (menas of means)
annual_avg_table <- percent_reduction_table |>
  summarise(
    total_tn_10yr = mean(total_tn_reduce_per_wet_yr),
    avg_tn_per_wet_day_10yr = mean(avg_tn_reduce_per_wet_day),

    total_sed_10yr = mean(total_sed_reduce_per_wet_yr),
    avg_sed_per_wet_day_10yr = mean(avg_sed_reduce_per_wet_day),

    total_suro_10yr = mean(total_suro_wet_yr),
    avg_suro_10yr = mean(avg_suro_wet_day),

    total_pero_10yr = mean(total_pero),
    avg_pero_10yr = mean(avg_pero),
    
    avg_pct_tn_reduction = mean(pct_tn_reduction),
    avg_pct_sed_reduction = mean(pct_sed_reduction),
    avg_pct_volume_capture = mean(pct_volume_capture),
    wet_days_10yr = mean(wet_days))


  return(list(
    watershed_capture = capture_summary,
    loading = loading_table,
    reduction = reduction_table,
    percent = percent_reduction_table,
    annual = annual_avg_table)) 
}
```

**Extract the Jurished Data**

This code extracts the results from the looped function that calcualted the values from each jurished and makes it into a table.

```{r}
# Loop the function for all jurished data 
avg_10_juri <- imap(jurisheds, ~process_juri(.x$folder, .x$file))

# Extract the results from the loop into a table
avg10_all <- imap_dfr(avg_10_juri, function(x, name){
  x$avg10 |> mutate(jurished = name)})
```

**Create A Table for all 20 Jurisheds**

```{r}
results <- imap(jurisheds, ~process_juri(.x$folder, .x$file))

loading_all <- imap_dfr(results, ~mutate(.x$loading, jurished=.y))
reduction_all <- imap_dfr(results, ~mutate(.x$reduction, jurished=.y))
annual_reduction_all <- imap_dfr(results, ~mutate(.x$annual, jurished=.y))

```

# Park Recommendations

## Dominguez Channel Watershed

### 2113 - Banning Park and Museum

Subbasin 2113 was modeled for Banning Park and Museum (Jurished: 211349, City: Los Angeles City, Acres: 21.071).

#### **Landuse**

```{r}
# Landuse Data 
dc_lu_2113_raw <- read.csv(here(dc_2113_folder, "landuse_dc_2113.csv"))


# Read the delineation excel sheet and convert to csv
landuse_deluid_2113 <- read_excel(here(dc_2113_folder,
                                       "landuse_deluid_2113.xlsx"))

#write.csv(landuse_deluid_2113, here(dc_2113_folder,
#                                       "landuse_deluid_2113.csv"),
#          row.names = FALSE)


#Check the data
unique(dc_lu_2113_raw$deluid) #total of 96

# Pivot the long table
dc_lu_2113_clean <- dc_lu_2113_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1) 
head(dc_lu_2113_clean) |>
  clean_names()


# Check shared names prior to joining 
names(dc_lu_2113_clean)
names(landuse_deluid_2113)
intersect(names(dc_lu_2113_clean), names(landuse_deluid_2113))


# Join Tables 
dc_lu_2113_join <- dc_lu_2113_clean |>
  left_join(landuse_deluid_2113, by = c("subbasin", "deluid")) |>
  clean_names()


# Check number of rows 
nrow(dc_lu_2113_clean)
nrow(dc_lu_2113_join)

sum(is.na(dc_lu_2113_join[[names(landuse_deluid_2113)[3]]]))


# Categorize the delineations into main classes for easier data manipulation
dc_plot_2113 <- dc_lu_2113_join |>
  mutate(main_class = str_extract(deluname, "^[^_-]+")) |>
  rename(Vegetation = Veg,
         Developed = Dev)
 # summarise(total_volume = area_ac*
```

```{r}
# Summarize the data
lu_area_2113_sum <- dc_plot_2113 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Landuse Type Distribution Plot 
lu_2113_plot <- ggplot(lu_area_2113_sum, aes(x = main_class, y = total_area)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Area (acres)", 
       title = "Jurished 2113 Landuse Distribution") +
  theme_minimal()

print(lu_2113_plot)

# Sediment Loading Plot
lu_2113_sed <- ggplot(lu_area_2113_sum, aes(x = main_class, y = total_avg_sed)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Sediment (tons/year)", 
       title = "Jurished 2113 Average Sediment Loading 2008-2018") +
  theme_minimal()
print(lu_2113_sed)


# Nitrogen FLux Plot
lu_2113_n <- ggplot(lu_area_2113_sum, aes(x = main_class, y = total_avg_n)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Nitrogen Flux (lbs/year)", 
       title = "Jurished 2113 Average Nitrogen Flux 2008-2018") +
  theme_minimal()
print(lu_2113_n)
```

#### **Loading**

### 2074 - Jesse Owens Community Regional Park

Subbasin 2074 was modeled for Jesse Owens Community Regional Park (Jurished: 207449, City: Los Angeles City, Acres: 19.118).

#### **Landuse**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_2074 <- read_excel(here(dc_2074_folder,
                                       "landuse_deluid_2074.xlsx"))

#write.csv(landuse_deluid_2074, here(dc_2074_folder,
#                                       "landuse_deluid_2074.csv"),
#          row.names = FALSE)
```

#### **Loading**

## Los Angeles River Watershed

### 6387 - Pecan Playground

Subbasin 6387 was modeled for Pecan Playground (Jurished: 638749, City: Los Angeles City, Acres: 4.282).

#### Landuse

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_6387 <- read_excel(here(lar_6387_folder,
                                       "landuse_deluid_6387.xlsx"))

#write.csv(landuse_deluid_6387, here(lar_6387_folder,
#                                       "landuse_deluid_6387.csv"),
#          row.names = FALSE)
```

#### Loading

### 6396 - State Street Recreation Center

Subbasin 6396 was modeled for State Street Recreation Center (Jurished: 639649, City: Los Angeles City, Acres: 2.617).

#### **Landuse**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_6396 <- read_excel(here(lar_6396_folder,
                                       "landuse_deluid_6396.xlsx"))

#write.csv(landuse_deluid_6396, here(lar_6396_folder,
#                                       "landuse_deluid_6396.csv"),
#          row.names = FALSE)
```

#### **Loading**

### 6480 - Glassel Park

Subbasin 6480 was modeled for Glassel Park (Jurished: 648049, City: Los Angeles City, Acres: 12.663).

#### Landuse

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_6480 <- read_excel(here(lar_6480_folder,
                                       "landuse_deluid_6480.xlsx"))

#write.csv(landuse_deluid_6480, here(lar_6480_folder,
#                                       "landuse_deluid_6480.csv"),
#          row.names = FALSE)
```

#### Loading

## San Gabriel Watershed

### 5109 - Rosewood Park

Subbasin 5109 was modeled for Rosewood Park (Jurished: 510916, City: Cerritos, Acres: 5.447).

**Create CSV Files**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_5109 <- read_excel(here(sg_5109_folder,
                                       "landuse_deluid_5109.xlsx"))

#write.csv(landuse_deluid_5109, here(sg_5109_folder,
#                                       "landuse_deluid_5109.csv"),
#          row.names = FALSE)
```

#### Landuse

#### Loading

### 5118 - Byron Zinn Park

Subbasin 5118 was modeled for Byron Zinn Park (Jurished: 511810, City: Bellflower, Acres: 4.827).

#### Landuse

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_5118 <- read_excel(here(sg_5118_folder,
                                       "landuse_deluid_5118.xlsx"))

#write.csv(landuse_deluid_5118, here(sg_5118_folder,
#                                       "landuse_deluid_5118.csv"),
#          row.names = FALSE)
```

#### Loading

### 5120 - New River Park

Subbasin 5120 was modeled for New River Park (Jurished: 512057, City: Norwalk, Acres: 4.840).

#### **Loading**

[**Goal:**]{.underline} Estimate the total average annual loading for sediment, nitrogen, runoff volume (total surface outflow rate \* areas)

#### **Landuse**

The delineations used for this model include 96 types to calculate the average area based on landuse from 2008-2018 using input data from 2006-2018. We will group the delineations based on major land use types: road, developed, agriculture, vegetation, and water before plotting the data and analysis.

[**Goal**]{.underline}: Understand how much total average area in acres is distributed in this jurished based on landuse type.

```{r}
# San Gabriel Landuse Data 
sg_lu_5120_raw <- read.csv(here("data", "wmms", "park_rec", "sg_5120", "landuse_sg_5120.csv"))

# San Gabriel Delineation Data for Landuse
sg_deluid_5120 <- read.csv(here("data", "wmms", "park_rec", "sg_5120", "landuse_deluid_5120.csv"))


#Check the data
unique(sg_lu_5120_raw$deluid) #total of 96

# Pivot the long table
sg_lu_5120_clean <- sg_lu_5120_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1) 
head(sg_lu_5120_clean)


# Check shared names prior to joining 
names(sg_lu_5120_clean)
names(sg_deluid_5120)
intersect(names(sg_lu_5120_clean), names(sg_deluid_5120))


# Join Tables 
sg_lu_5120_join <- sg_lu_5120_clean |>
  left_join(sg_deluid_5120, by = c("subbasin", "deluid"))


# Check number of rows 
nrow(sg_lu_5120_clean)
nrow(sg_lu_5120_join)

sum(is.na(sg_lu_5120_join[[names(sg_deluid_5120)[3]]]))

```

```{r}
# Categorize the delineations into main classes for easier data manipulation
sg_plot_5120 <- sg_lu_5120_join |>
  mutate(main_class = str_extract(deluname, "^[^_-]+"))
 # summarise(total_volume = area_ac*
```

```{r}
# Summarize the data
lu_area_5120_sum <- sg_plot_5120 |>
  group_by(main_class) |>
  summarise(total_area = sum(AREA, na.rm = TRUE),
            total_avg_sed = sum(SEDLOAD, na.rm = TRUE),
            total_avg_n = sum(PO_TN, na.rm = TRUE))

# Landuse Type Distribution Plot 
lu_5120_plot <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_area)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Area (acres)", 
       title = "Jurished 5120 Landuse Distribution") +
  theme_minimal()

print(lu_5120_plot)

# Sediment Loading Plot
lu_5120_sed <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_avg_sed)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Sediment (tons/year)", 
       title = "Jurished 5120 Average Sediment Loading 2008-2018") +
  theme_minimal()
print(lu_5120_sed)


# Nitrogen FLux Plot
lu_5120_n <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_avg_n)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Nitrogen Flux (lbs/year)", 
       title = "Jurished 5120 Average Nitrogen Flux 2008-2018") +
  theme_minimal()
print(lu_5120_n)
```

## Santa Monica Watershed

### 1030 - Rogers Park

Subbasin 1030 was modeled for Rogers Park (Jurished: 103037, City: Inglewood, Acres: 12.792).

**Create CSV Files**

```{r}
# Locate the Santa Monica 1030 Folder
sm_1030_folder <- here("data", "wmms", "park_rec", "sm_1030")


# Read the delineation excel sheet and convert to csv
landuse_deluid_1030 <- read_excel(here(sm_1030_folder,
                                       "landuse_deluid_1030.xlsx"))

#write.csv(landuse_deluid_1030, here(sm_1030_folder,
#                                       "landuse_deluid_1030.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

### 1077 - Exposition Park

Subbasin 1077 modeled for Exposition Park (Jurished: 107749, City: Los Angeles City, Acres: 10.394).

**Create CSV Files**

```{r}
# Locate the Santa Monica 1077 Folder
sm_1077_folder <- here("data", "wmms", "park_rec", "sm_1077")


# Read the delineation excel sheet and convert to csv
landuse_deluid_1077 <- read_excel(here(sm_1077_folder,
                                       "landuse_deluid_1077.xlsx"))

#write.csv(landuse_deluid_1077, here(sm_1077_folder,
#                                       "landuse_deluid_1077.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

# School Recommendations

## Dominguez Channel Watershed

### 2034 - Gardena High School

Subbasin 2034 modeled for Gardena High School (Jurished: 203428, City: Gardena).

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_2034 <- read_excel(here(dc_2034_folder,
                                       "landuse_deluid_2034.xlsx"))

write.csv(landuse_deluid_2034, here(dc_2034_folder,
                                       "landuse_deluid_2034.csv"),
          row.names = FALSE)
```

#### Loading

#### Landuse

### 2088 - Narbonne High School

Subbasin 2088 modeled for Narbonne High School (Jurished: 208849, City: Harbor City).

**Create CSV Files**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_2088 <- read_excel(here(dc_2088_folder,
                                       "landuse_deluid_2088.xlsx"))

#write.csv(landuse_deluid_2088, here(dc_2088_folder,
#                                       "landuse_deluid_2088.csv"),
#          row.names = FALSE)
```

#### **Loading**

#### **Landuse**

### 2122 - San Pedro High School

Subbasin 2122 modeled for San Pedro High School (Jurished: 212249, City: San Pedro).

**Create CSV Files**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_2122 <- read_excel(here(dc_2122_folder,
                                       "landuse_deluid_2122.xlsx"))

#write.csv(landuse_deluid_2122, here(dc_2122_folder,
#                                       "landuse_deluid_2122.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

## Los Angeles River Watershed

### 6873 - Birmingham Community Charter High School

Subbasin 6873 modeled for Birmingham Community Charter High School (Jurished: 687349, City: Van Nuys).

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_6873 <- read_excel(here(lar_6873_folder,
                                       "landuse_deluid_6873.xlsx"))

#write.csv(landuse_deluid_6873, here(lar_6873_folder,
#                                       "landuse_deluid_6873.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

### 6682 - Francis Polytechnic High School

Subbasin 6682 modeled for Francis Polytechnic High School (Jurished: 668249, City: Sun Valley).

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_6682 <- read_excel(here(lar_6682_folder,
                                       "landuse_deluid_6682.xlsx"))

#write.csv(landuse_deluid_6682, here(lar_6682_folder,
#                                       "landuse_deluid_6682.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

### 6697 - San Fernando High School

Subbasin 6697 modeled for San Fernando High School (Jurished: 669749, City: San Fernando).

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_6697 <- read_excel(here(lar_6697_folder,
                                       "landuse_deluid_6697.xlsx"))

#write.csv(landuse_deluid_6697, here(lar_6697_folder,
#                                       "landuse_deluid_6697.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

### 6925 - Cleveland Charter High School

Subbasin 6925 modeled for Cleveland Charter High School (Jurished: 692549, City: Reseda).

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_6925 <- read_excel(here(lar_6925_folder,
                                       "landuse_deluid_6925.xlsx"))

#write.csv(landuse_deluid_6925, here(lar_6925_folder,
#                                       "landuse_deluid_6925.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

## Santa Monica Watershed

### 1067 - Crenshaw High School STEMM Magnet

Subbasin 1067 modeled for Crenshaw High School STEMM Magnet (Jurished: 106749, City: Los Angeles).

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_1067 <- read_excel(here(sm_1067_folder,
                                       "landuse_deluid_1067.xlsx"))

write.csv(landuse_deluid_1067, here(sm_1067_folder,
                                       "landuse_deluid_1067.csv"),
          row.names = FALSE)
```

#### Loading

#### Landuse

### 1110 - Kennedy Community of Schools

Subbasin 1110 modeled for Kennedy Community of Schools (Jurished: 111049, City: Los Angeles).

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_1110 <- read_excel(here(sm_1110_folder,
                                       "landuse_deluid_1110.xlsx"))

#write.csv(landuse_deluid_1110, here(sm_1110_folder,
#                                       "landuse_deluid_1110.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

### 1061 - Dorsey High School

Subbasin 1061 modeled for Dorsey High School (Jurished: 106149, City: Los Angeles).

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_1061 <- read_excel(here(sm_1061_folder,
                                       "landuse_deluid_1061.xlsx"))

#write.csv(landuse_deluid_1061, here(sm_1061_folder,
#                                       "landuse_deluid_1061.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

## San Gabriel Watershed

No schools were selected as a recommendation for the San Gabriel watershed.
