---
title: "wmms_clean_data"
format: 
 html:
    embed-resources: true
    code-line-numbers: true
    code-wrap: true
    code-fold: true
    toc: true
author: Tina Tran 
editor: visual
warning: false
messages: false 
---

# WMMS Clean Data

**Load Libraries**

```{r, warning = FALSE, message = FALSE}
# Load library 
library(tidyverse)
library(here)
library(janitor)
library(ggplot2)
library(dplyr)
library(stringr)
library(readxl) # Read excel files
```

**Overview**

The standard output model was selected for WMMS 2.0. WMMS 2.0 modeled the following parameters for the 20 total jurisheds (10 parks and 10 school recommendations) selected for this project's recommendations.

The data ouput filles include a jurished file, landuse, and stream (Note: some jurisheds have a pointsource output file, but it will not be used for the analysis for this project).

[**Output Parameters for Jurished Data:**]{.underline}\
TT Time interval: 60 min Output option: day\
TT PREC precipitation (rain + snow) volume (in-acre/day)\
TT SURO surface outflow volume (in-acre/day)\
TT IFWO interflow outflow volume (in-acre/day)\
TT AGWO groundwater outflow volume (in-acre/day)\
TT PERO total outflow rate volume (SURO+IFWO+AGWO) (in-acre/day)\
TT DEP stream depth (ft)\
TT AVDEP stream average depth (ft)\
TT TAU bed shear stress (kg/m\^2)\
TT RO total rate of outflow from RCHRES (cfs)\
TT SOSED sediments load from land (english tons/da**y)**\
TT SSEDOUT1 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT2 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT3 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT total suspended solid concentration in outflow from the RCHRES (mg/l)\
TT POQUAL1 total flux of QUAL from the PLS_TN (lb/day)\
TT POQUAL2 total flux of QUAL from the PLS_TP (lb/day)\
TT POQUAL3 total flux of QUAL from the PLS_TCd (lb/day)\
TT POQUAL4 total flux of QUAL from the PLS_TCu (lb/day)\
TT POQUAL5 total flux of QUAL from the PLS_TPb (lb/day)\
TT POQUAL6 total flux of QUAL from the PLS_TZn (lb/day)\
TT CONC1 TN dissolved concentration (average) in RCHRES (mg/l)**\
**TT CONC2 TP dissolved concentration (average) in RCHRES (mg/l)\
TT CONC3 TCd dissolved concentration (average) in RCHRES (ug/l)\
TT CONC4 TCu dissolved concentration (average) in RCHRES (ug/l)\
TT CONC5 TPb dissolved concentration (average) in RCHRES (ug/l)\
TT CONC6 TZn dissolved concentration (average) in RCHRES (ug/l)

For the purpose of estimating potential fecal indicator bacteria (FIB) loading in the jurished, sediment (SOSED), nitrogen (CONC1 TN), and surface outflow volume (SURO) have been selected as a proxy. WMMS 2.0 uses daily precipitation data from 2006-2018 to estimate these output parameters for 2008-2018.

# Park Recommendations

## Dominguez Channel Watershed

### Subbasin: 2113 

Subbasin 2113 was modeled for Banning Park and Museum (Jurished: 211349, City: Los Angeles City, Acres: 21.071).

**Create CSV files**

```{r}
# Locate the Dominguez Channel 2113 Folder
dc_2113_folder <- here("data", "wmms", "park_rec", "dc_2113")


# Read the delineation excel sheet and convert to csv
landuse_deluid_2113 <- read_excel(here(dc_2113_folder,
                                       "landuse_deluid_2113.xlsx"))

write.csv(landuse_deluid_2113, here(dc_2113_folder,
                                       "landuse_deluid_2113.csv"),
          row.names = FALSE)


```

```{r}
# Read the excel file and convert it into a csv
juri_dc_2113 <- read_excel(here(dc_2113_folder, 
                                "juri_dc_2113.xlsx"),
                           skip = 51)

write.csv(juri_dc_2113, here(dc_2113_folder,"juri_dc_2113.csv"),
          row.names = FALSE)

# Double check the way the csv imports
juri_dc_2113 <- read.csv(here(dc_2113_folder, 
                              "juri_dc_2113.csv")) |>
  clean_names() |>
  rename_with(~ str_remove("^tt_", .x)) |>
  rename_with(~ str_extract(.x, "^[^_]+"))
```

**Landuse**

```{r}
# Landuse Data 
dc_lu_2113_raw <- read.csv(here("data", "wmms", "park_rec", "dc_2113", "landuse_dc_2113.csv"))

# Delineation Data for Landuse
landuse_deluid_2113 <- read.delim("landuse.out",
                   header = FALSE,
                   sep = "\t",
                   stringsAsFactors = FALSE)

sg_deluid_5120 <- read.csv(here("data", "wmms", "park_rec", "sg_5120", "landuse_deluid_5120.csv"))


#Check the data
unique(sg_lu_5120_raw$deluid) #total of 96

# Pivot the long table
sg_lu_5120_clean <- sg_lu_5120_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1) 
head(sg_lu_5120_clean)


# Check shared names prior to joining 
names(sg_lu_5120_clean)
names(sg_deluid_5120)
intersect(names(sg_lu_5120_clean), names(sg_deluid_5120))


# Join Tables 
sg_lu_5120_join <- sg_lu_5120_clean |>
  left_join(sg_deluid_5120, by = c("subbasin", "deluid"))


# Check number of rows 
nrow(sg_lu_5120_clean)
nrow(sg_lu_5120_join)

sum(is.na(sg_lu_5120_join[[names(sg_deluid_5120)[3]]]))
```

**Loading Calculations**

```{r}

```

### Subbasin: 2074

Subbasin 2074 was modeled for Jesse Owens Community Regional Park (Jurished: 207449, City: Los Angeles City, Acres: 19.118).

**Landuse**

```{r}

```

**Loading**

```{r}

```

## Los Angeles River Watershed

### Subbasin: 6387

Subbasin 6387 was modeled for Pecan Playground (Jurished: 638749, City: Los Angeles City, Acres: 4.282).

### Subbasin: 6396

Subbasin 6396 was modeled for State Street Recreation Center (Jurished: 639649, City: Los Angeles City, Acres: 2.617).

### Subbasin: 6480

Subbasin 6480 was modeled for Glassel Park (Jurished: 648049, City: Los Angeles City, Acres: 12.663).

## San Gabriel Watershed

### Subbasin: 5109

Subbasin 5109 was modeled for Rosewood Park (Jurished: 510916, City: Cerritos, Acres: 5.447).

### Subbasin: 5118

Subbasin 5118 was modeled for Byron Zinn Park (Jurished: 511810, City: Bellflower, Acres: 4.827).

### Subbasin: 5120

Subbasin 5120 was modeled for New River Park (Jurished: 512057, City: Norwalk, Acres: 4.840).

**Loading**

[**Goal:**]{.underline} Estimate the total average annual loading for sediment, nitrogen, runoff volume (total surface outflow rate \* areas)

**Landuse Based on Area for 5120**

The delineations used for this model include 96 types to calculate the average area based on landuse from 2008-2018 using input data from 2006-2018. We will group the delineations based on major land use types: road, developed, agriculture, vegetation, and water before plotting the data and analysis.

[**Goal**]{.underline}: Understand how much total average area in acres is distributed in this jurished based on landuse type.

```{r}
# San Gabriel Landuse Data 
sg_lu_5120_raw <- read.csv(here("data", "wmms", "park_rec", "sg_5120", "landuse_sg_5120.csv"))

# San Gabriel Delineation Data for Landuse
sg_deluid_5120 <- read.csv(here("data", "wmms", "park_rec", "sg_5120", "landuse_deluid_5120.csv"))


#Check the data
unique(sg_lu_5120_raw$deluid) #total of 96

# Pivot the long table
sg_lu_5120_clean <- sg_lu_5120_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1) 
head(sg_lu_5120_clean)


# Check shared names prior to joining 
names(sg_lu_5120_clean)
names(sg_deluid_5120)
intersect(names(sg_lu_5120_clean), names(sg_deluid_5120))


# Join Tables 
sg_lu_5120_join <- sg_lu_5120_clean |>
  left_join(sg_deluid_5120, by = c("subbasin", "deluid"))


# Check number of rows 
nrow(sg_lu_5120_clean)
nrow(sg_lu_5120_join)

sum(is.na(sg_lu_5120_join[[names(sg_deluid_5120)[3]]]))

```

```{r}
# Categorize the delineations into main classes for easier data manipulation
sg_plot_5120 <- sg_lu_5120_join |>
  mutate(main_class = str_extract(deluname, "^[^_-]+"))
 # summarise(total_volume = area_ac*
```

```{r}
# Summarize the data
lu_area_5120_sum <- sg_plot_5120 |>
  group_by(main_class) |>
  summarise(total_area = sum(AREA, na.rm = TRUE),
            total_avg_sed = sum(SEDLOAD, na.rm = TRUE),
            total_avg_n = sum(PO_TN, na.rm = TRUE))

# Landuse Type Distribution Plot 
lu_5120_plot <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_area)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Area (acres)", 
       title = "Jurished 5120 Landuse Distribution") +
  theme_minimal()

print(lu_5120_plot)

# Sediment Loading Plot
lu_5120_sed <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_avg_sed)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Sediment (tons/year)", 
       title = "Jurished 5120 Average Sediment Loading 2008-2018") +
  theme_minimal()
print(lu_5120_sed)


# Nitrogen FLux Plot
lu_5120_n <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_avg_n)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Nitrogen Flux (lbs/year)", 
       title = "Jurished 5120 Average Nitrogen Flux 2008-2018") +
  theme_minimal()
print(lu_5120_n)
```

## Santa Monica Watershed

### Subbasin: 1030

Subbasin 1030 was modeled for Rogers Park (Jurished: 103037, City: Inglewood, Acres: 12.792).

### Subbasin: 1077

Subbasin 1077 modeled for Exposition Park (Jurished: 107749, City: Los Angeles City, Acres: 10.394).

# School Recommendations

## Dominguez Channel Watershed

### Subbasin: 2034

Subbasin 2034 modeled for Gardena High School (Jurished: 203428, City: Gardena).

### Subbasin: 2088

Subbasin 2088 modeled for Narbonne High School (Jurished: 208849, City: Harbor City).

### Subbasin: 2122

Subbasin 2122 modeled for San Pedro High School (Jurished: 212249, City: San Pedro).

## Los Angeles River Watershed

### Subbasin: 6873

Subbasin 6873 modeled for Birmingham Community Charter High School (Jurished: 687349, City: Van Nuys).

### Subbasin: 6682

Subbasin 6682 modeled for Francis Polytechnic High School (Jurished: 668249, City: Sun Valley).

### Subbasin: 6697

Subbasin 6697 modeled for San Fernando High School (Jurished: 669749, City: San Fernando).

### Subbasin: 6925

Subbasin 6925 modeled for Cleveland Charter High School (Jurished: 692549, City: Reseda).

## San Gabriel Watershed

No schools were selected as a recommendation for the San Gabriel watershed.

## Santa Monica Watershed

### Subbasin: 1067

Subbasin 1067 modeled for Crenshaw High School STEMM Magnet (Jurished: 106749, City: Los Angeles).

### Subbasin: 1110

Subbasin 1110 modeled for Kennedy Community of Schools (Jurished: 111049, City: Los Angeles).

### Subbasin: 1061

Subbasin 1061 modeled for Dorsey High School (Jurished: 106149, City: Los Angeles).
