---
title: "wmms_clean_data"
format: 
 html:
    embed-resources: true
    code-line-numbers: true
    code-wrap: true
    code-fold: true
    toc: true
author: Tina Tran 
editor: visual
warning: false
messages: false 
---

# WMMS Clean Data

**Load Libraries**

```{r, warning = FALSE, message = FALSE}
# Load library 
library(tidyverse)
library(here)
library(janitor)
library(ggplot2)
library(dplyr)
library(stringr)
library(readxl) # Read excel files
library(purrr)
```

**Overview**

The standard output model was selected for WMMS 2.0. WMMS 2.0 modeled the following parameters for the 20 total jurisheds (10 parks and 10 school recommendations) selected for this project's recommendations.

The data ouput filles include a jurished file, landuse, and stream (Note: some jurisheds have a pointsource output file, but it will not be used for the analysis for this project).

[**Output Parameters for Jurished Data:**]{.underline}\
TT Time interval: 60 min Output option: day\
TT PREC precipitation (rain + snow) volume (in-acre/day)\
TT SURO surface outflow volume (in-acre/day)\
TT IFWO interflow outflow volume (in-acre/day)\
TT AGWO groundwater outflow volume (in-acre/day)\
TT PERO total outflow rate volume (SURO+IFWO+AGWO) (in-acre/day)\
TT DEP stream depth (ft)\
TT AVDEP stream average depth (ft)\
TT TAU bed shear stress (kg/m\^2)\
TT RO total rate of outflow from RCHRES (cfs)\
TT SOSED sediments load from land (english tons/da**y)**\
TT SSEDOUT1 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT2 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT3 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT total suspended solid concentration in outflow from the RCHRES (mg/l)\
TT POQUAL1 total flux of QUAL from the PLS_TN (lb/day)\
TT POQUAL2 total flux of QUAL from the PLS_TP (lb/day)\
TT POQUAL3 total flux of QUAL from the PLS_TCd (lb/day)\
TT POQUAL4 total flux of QUAL from the PLS_TCu (lb/day)\
TT POQUAL5 total flux of QUAL from the PLS_TPb (lb/day)\
TT POQUAL6 total flux of QUAL from the PLS_TZn (lb/day)\
TT CONC1 TN dissolved concentration (average) in RCHRES (mg/l)**\
**TT CONC2 TP dissolved concentration (average) in RCHRES (mg/l)\
TT CONC3 TCd dissolved concentration (average) in RCHRES (ug/l)\
TT CONC4 TCu dissolved concentration (average) in RCHRES (ug/l)\
TT CONC5 TPb dissolved concentration (average) in RCHRES (ug/l)\
TT CONC6 TZn dissolved concentration (average) in RCHRES (ug/l)

For the purpose of estimating potential fecal indicator bacteria (FIB) loading in the jurished, sediment (SOSED), nitrogen (CONC1 TN), and surface outflow volume (SURO) have been selected as a proxy. WMMS 2.0 uses daily precipitation data from 2006-2018 to estimate these output parameters for 2008-2018.

## **Folder Pathways**

**Park Recommendations**

```{r}
# Locate the Dominguez Channel 2113 Folder
dc_2113_folder <- here("data", "wmms", "park_rec", "dc_2113")

# Locate the Dominguez Channel 2074 Folder
dc_2074_folder <- here("data", "wmms", "park_rec", "dc_2074")

# Locate the Los Angeles River 6387 Folder
lar_6387_folder <- here("data", "wmms", "park_rec", "lar_6387")

# Locate the Los Angeles River 6396 Folder
lar_6396_folder <- here("data", "wmms", "park_rec", "lar_6396")

# Locate the Los Angeles River 6480 Folder
lar_6480_folder <- here("data", "wmms", "park_rec", "lar_6480")

# Locate the San Gabriel 5109 Folder
sg_5109_folder <- here("data", "wmms", "park_rec", "sg_5109")

# Locate the San Gabriel 5118 Folder
sg_5118_folder <- here("data", "wmms", "park_rec", "sg_5118")

# Locate the San Gabriel 5120 Folder
sg_5120_folder <- here("data", "wmms", "park_rec", "sg_5120")

```

**School Recommendations**

```{r}
# Locate the Dominguez Channel 2034 Folder
dc_2034_folder <- here("data", "wmms", "school_rec", "dc_2034")

# Locate the Dominguez Channel 2088 Folder
dc_2088_folder <- here("data", "wmms", "school_rec", "dc_2088")

#Locate the Dominguez Channel 2122 Folder
dc_2122_folder <- here("data", "wmms", "school_rec", "dc_2122")

# Locate the Los Angeles River 6873 Folder
lar_6873_folder <- here("data", "wmms", "school_rec", "lar_6873")

# Locate the Los Angeles River 6682 Folder
lar_6682_folder <- here("data", "wmms", "school_rec", "lar_6682")

# Locate the Los Angeles River 6697 Folder
lar_6697_folder <- here("data", "wmms", "school_rec", "lar_6697")

# Locate the Los Angeles River 6925 Folder
lar_6925_folder <- here("data", "wmms", "school_rec", "lar_6925")

# Locate the Santa Monica 1067 Folder
sm_1067_folder <- here("data", "wmms", "school_rec", "sm_1067")

# Locate the Santa Monica 1110 Folder
sm_1110_folder <- here("data", "wmms", "school_rec", "sm_1110")

# Locate the Santa Monica 1061 Folder
sm_1061_folder <- here("data", "wmms", "school_rec", "sm_1061")

```

## **CSV File from the excel sheets**

Park Recommendations

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_2113 <- read_excel(here(dc_2113_folder,
                                       "landuse_deluid_2113.xlsx"))

#write.csv(landuse_deluid_2113, here(dc_2113_folder,
#                                       "landuse_deluid_2113.csv"),
#          row.names = FALSE)


# Read the delineation excel sheet and convert to csv
landuse_deluid_2074 <- read_excel(here(dc_2074_folder,
                                       "landuse_deluid_2074.xlsx"))

#write.csv(landuse_deluid_2074, here(dc_2074_folder,
#                                       "landuse_deluid_2074.csv"),
#          row.names = FALSE)


# Read the delineation excel sheet and convert to csv
landuse_deluid_6387 <- read_excel(here(lar_6387_folder,
                                       "landuse_deluid_6387.xlsx"))

#write.csv(landuse_deluid_6387, here(lar_6387_folder,
#                                       "landuse_deluid_6387.csv"),
#          row.names = FALSE)

# Read the delineation excel sheet and convert to csv
landuse_deluid_6396 <- read_excel(here(lar_6396_folder,
                                       "landuse_deluid_6396.xlsx"))

#write.csv(landuse_deluid_6396, here(lar_6396_folder,
#                                       "landuse_deluid_6396.csv"),
#          row.names = FALSE)

# Read the delineation excel sheet and convert to csv
landuse_deluid_6480 <- read_excel(here(lar_6480_folder,
                                       "landuse_deluid_6480.xlsx"))

#write.csv(landuse_deluid_6480, here(lar_6480_folder,
#                                       "landuse_deluid_6480.csv"),
#          row.names = FALSE)

# Read the delineation excel sheet and convert to csv
landuse_deluid_5109 <- read_excel(here(sg_5109_folder,
                                       "landuse_deluid_5109.xlsx"))

#write.csv(landuse_deluid_5109, here(sg_5109_folder,
#                                       "landuse_deluid_5109.csv"),
#          row.names = FALSE)

# Read the delineation excel sheet and convert to csv
landuse_deluid_5118 <- read_excel(here(sg_5118_folder,
                                       "landuse_deluid_5118.xlsx"))

#write.csv(landuse_deluid_5118, here(sg_5118_folder,
#                                       "landuse_deluid_5118.csv"),
#          row.names = FALSE)
```

## **Process All Jurisheds**

```{r}
# Create a Jurished List 
jurisheds <- list(
  # Park Recommendations
  juri2074 = list(folder = dc_2074_folder, 
                  file="juri_dc_2074.csv"),
  juri2113 = list(folder = dc_2113_folder, 
                  file="juri_dc_2113.csv"),
  juri6387 = list(folder = lar_6387_folder, 
                  file="juri_lar_6387.csv"),
  juri6396 = list(folder = lar_6396_folder, 
                  file="juri_lar_6396.csv"),
  juri6480 = list(folder = lar_6480_folder, 
                  file="juri_lar_6480.csv"),
  juri5109 = list(folder = sg_5109_folder, 
                  file="juri_sg_5109.csv"),
  juri5118 = list(folder = sg_5118_folder, 
                  file="juri_sg_5118.csv"),
  juri5120 = list(folder = sg_5120_folder, 
                  file="juri_sg_5120.csv"),
  juri1030 = list(folder = sm_1030_folder, 
                  file="juri_sm_1030.csv"),
  juri1077 = list(folder = sm_1077_folder, 
                  file="juri_sm_1077.csv"),
  
  # School Recommendations
  juri2034 = list(folder = dc_2034_folder, 
                  file="juri_dc_2034.csv"),
  juri2088 = list(folder = dc_2088_folder, 
                  file="juri_dc_2088.csv"),
  juri2122 = list(folder = dc_2122_folder, 
                  file="juri_dc_2122.csv"),
  juri6873 = list(folder = lar_6873_folder, 
                  file="juri_lar_6873.csv"),
  juri6682 = list(folder = lar_6682_folder, 
                  file="juri_lar_6682.csv"),
  juri6697 = list(folder = lar_6697_folder, 
                  file="juri_lar_6697.csv"),
  juri6925 = list(folder = lar_6925_folder, 
                  file="juri_lar_6925.csv"),
  juri1067 = list(folder = sm_1067_folder, 
                  file="juri_sm_1067.csv"),
  juri1110 = list(folder = sm_1110_folder, 
                  file="juri_sm_1110.csv"),
  juri1061 = list(folder = sm_1061_folder, 
                  file="juri_sm_1061.csv"))
```

```{r}
# Convert all existing jurished excel files into a csv and add it to the existing folder

#walk(jurisheds, function(j){

#  excel_file <- sub("\\.csv$", ".xlsx", j$file)
#  excel_path <- here(j$folder, excel_file)

#  if(file.exists(excel_path)){

#    message("Converting: ", excel_file)

#    juri_xl <- read_excel(excel_path, skip = 51)

#    write.csv(juri_xl,
#      here(j$folder, j$file),
#      row.names = FALSE)

#  } else {

#    message("Missing file: ", excel_file)}})
```

**Function**

```{r}
# Create a loop to process all jurished files 
process_juri <- function(folder, file_name){

  # Read & clean 
  juri_load <- read.csv(here(folder, file_name)) |>
    clean_names() |>
    rename_with(~ str_remove(.x, "^tt_") |> 
                  str_extract("^[^_]+"),
                starts_with("tt_"))|>
    select(subbasin, year, month, day, prec,
           suro, ifwo, agwo, pero, dep, avdep, ro,
           sosed, conc1, conc2) |>
    rename(
      depth = dep,
      tn_mg_l = conc1,
      tp_mg_l = conc2) |>
    mutate(
      date = as.Date(paste(year, month, day, sep="-")),
      suro_ft_acre_day = suro / 12,
      pero_ft_acre_day = pero / 12,
      tn_lb_ac_ft = tn_mg_l * 2.71936,
      tp_lb_ac_ft = tp_mg_l * 2.71936,
      storm_volume_ac_ft_day = if_else(prec > 0, suro_ft_acre_day, 0))

  # Create the Runoff 85th Percentile 
  runoff_85th <- quantile(
    juri_load$storm_volume_ac_ft_day[juri_load$prec > 0],
    0.85,
    type = 7)

  # Total Nitrogen Reduction Calculations
  juri_load <- juri_load |>
    mutate(
      tn_reduce_lb_day = if_else(
        suro_ft_acre_day > runoff_85th,
        tn_lb_ac_ft * runoff_85th,
        tn_lb_ac_ft * suro_ft_acre_day))

  # Annual wet day stats
  wet_day_calc <- juri_load |>
    filter(storm_volume_ac_ft_day > 0) |>
    group_by(year) |>
    summarise(
      total_tn_wet_day = sum(tn_reduce_lb_day, na.rm=TRUE),
      avg_tn_per_wet_day = mean(tn_reduce_lb_day, na.rm=TRUE),

      total_sed_wet_day = sum(sosed, na.rm=TRUE),
      avg_sed_per_wet_day = mean(sosed, na.rm=TRUE),

      total_suro = sum(suro_ft_acre_day, na.rm=TRUE),
      avg_suro = mean(suro_ft_acre_day, na.rm=TRUE),

      total_pero = sum(pero_ft_acre_day, na.rm=TRUE),
      avg_pero = mean(pero_ft_acre_day, na.rm=TRUE),

      wet_days = n(), # count number of wet days 
      .groups="drop")

  # 10-year averages (menas of means)
  avg10 <- wet_day_calc |>
    summarise(
      total_tn_10yr = mean(total_tn_wet_day),
      avg_tn_per_wet_day_10yr = mean(avg_tn_per_wet_day),
      total_sed_10yr = mean(total_sed_wet_day),
      avg_sed_per_wet_day_10yr = mean(avg_sed_per_wet_day),
      total_suro_10yr = mean(total_suro),
      avg_suro_10yr = mean(avg_suro),
      total_pero_10yr = mean(total_pero),
      avg_pero_10yr = mean(avg_pero),
      wet_days_10yr = mean(wet_days)
    )

  return(list(
    yearly = wet_day_calc,
    avg10 = avg10))
}
```

```{r}
# Loop the function for all jurished data 
avg_10_juri <- imap(jurisheds, ~process_juri(.x$folder, .x$file))

# Extract the results from the loop into a table
avg10_all <- imap_dfr(avg_10_juri, function(x, name){
  x$avg10 |> mutate(jurished = name)})
```

# Park Recommendations

## Dominguez Channel Watershed

### 2113 - Banning Park and Museum

Subbasin 2113 was modeled for Banning Park and Museum (Jurished: 211349, City: Los Angeles City, Acres: 21.071).

#### **Landuse**

#### **Loading** 

### 2074 - Jesse Owens Community Regional Park 

Subbasin 2074 was modeled for Jesse Owens Community Regional Park (Jurished: 207449, City: Los Angeles City, Acres: 19.118).

#### **Landuse**

```{r}

```

#### **Loading**

## Los Angeles River Watershed

### 6387 - Pecan Playground

Subbasin 6387 was modeled for Pecan Playground (Jurished: 638749, City: Los Angeles City, Acres: 4.282).

#### Landuse

#### Loading

### 6396 - State Street Recreation Center

Subbasin 6396 was modeled for State Street Recreation Center (Jurished: 639649, City: Los Angeles City, Acres: 2.617).

#### **Landuse**

#### **Loading**

### 6480 - Glassel Park

Subbasin 6480 was modeled for Glassel Park (Jurished: 648049, City: Los Angeles City, Acres: 12.663).

**Create CSV Files**

```{r}

```

#### Landuse

#### Loading

## San Gabriel Watershed

### 5109 - Rosewood Park 

Subbasin 5109 was modeled for Rosewood Park (Jurished: 510916, City: Cerritos, Acres: 5.447).

**Create CSV Files**

```{r}

```

#### Landuse

#### Loading

### 5118 - Byron Zinn Park

Subbasin 5118 was modeled for Byron Zinn Park (Jurished: 511810, City: Bellflower, Acres: 4.827).

**Create CSV File**

```{r}

```

#### Landuse

#### Loading

### 5120 - New River Park

Subbasin 5120 was modeled for New River Park (Jurished: 512057, City: Norwalk, Acres: 4.840).

```{r}

```

#### **Loading**

[**Goal:**]{.underline} Estimate the total average annual loading for sediment, nitrogen, runoff volume (total surface outflow rate \* areas)

#### **Landuse** 

The delineations used for this model include 96 types to calculate the average area based on landuse from 2008-2018 using input data from 2006-2018. We will group the delineations based on major land use types: road, developed, agriculture, vegetation, and water before plotting the data and analysis.

[**Goal**]{.underline}: Understand how much total average area in acres is distributed in this jurished based on landuse type.

```{r}
# San Gabriel Landuse Data 
sg_lu_5120_raw <- read.csv(here("data", "wmms", "park_rec", "sg_5120", "landuse_sg_5120.csv"))

# San Gabriel Delineation Data for Landuse
sg_deluid_5120 <- read.csv(here("data", "wmms", "park_rec", "sg_5120", "landuse_deluid_5120.csv"))


#Check the data
unique(sg_lu_5120_raw$deluid) #total of 96

# Pivot the long table
sg_lu_5120_clean <- sg_lu_5120_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1) 
head(sg_lu_5120_clean)


# Check shared names prior to joining 
names(sg_lu_5120_clean)
names(sg_deluid_5120)
intersect(names(sg_lu_5120_clean), names(sg_deluid_5120))


# Join Tables 
sg_lu_5120_join <- sg_lu_5120_clean |>
  left_join(sg_deluid_5120, by = c("subbasin", "deluid"))


# Check number of rows 
nrow(sg_lu_5120_clean)
nrow(sg_lu_5120_join)

sum(is.na(sg_lu_5120_join[[names(sg_deluid_5120)[3]]]))

```

```{r}
# Categorize the delineations into main classes for easier data manipulation
sg_plot_5120 <- sg_lu_5120_join |>
  mutate(main_class = str_extract(deluname, "^[^_-]+"))
 # summarise(total_volume = area_ac*
```

```{r}
# Summarize the data
lu_area_5120_sum <- sg_plot_5120 |>
  group_by(main_class) |>
  summarise(total_area = sum(AREA, na.rm = TRUE),
            total_avg_sed = sum(SEDLOAD, na.rm = TRUE),
            total_avg_n = sum(PO_TN, na.rm = TRUE))

# Landuse Type Distribution Plot 
lu_5120_plot <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_area)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Area (acres)", 
       title = "Jurished 5120 Landuse Distribution") +
  theme_minimal()

print(lu_5120_plot)

# Sediment Loading Plot
lu_5120_sed <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_avg_sed)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Sediment (tons/year)", 
       title = "Jurished 5120 Average Sediment Loading 2008-2018") +
  theme_minimal()
print(lu_5120_sed)


# Nitrogen FLux Plot
lu_5120_n <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_avg_n)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Nitrogen Flux (lbs/year)", 
       title = "Jurished 5120 Average Nitrogen Flux 2008-2018") +
  theme_minimal()
print(lu_5120_n)
```

## Santa Monica Watershed

### 1030 - Rogers Park

Subbasin 1030 was modeled for Rogers Park (Jurished: 103037, City: Inglewood, Acres: 12.792).

**Create CSV Files**

```{r}
# Locate the Santa Monica 1030 Folder
sm_1030_folder <- here("data", "wmms", "park_rec", "sm_1030")


# Read the delineation excel sheet and convert to csv
landuse_deluid_1030 <- read_excel(here(sm_1030_folder,
                                       "landuse_deluid_1030.xlsx"))

#write.csv(landuse_deluid_1030, here(sm_1030_folder,
#                                       "landuse_deluid_1030.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

### 1077 - Exposition Park

Subbasin 1077 modeled for Exposition Park (Jurished: 107749, City: Los Angeles City, Acres: 10.394).

**Create CSV Files**

```{r}
# Locate the Santa Monica 1077 Folder
sm_1077_folder <- here("data", "wmms", "park_rec", "sm_1077")


# Read the delineation excel sheet and convert to csv
landuse_deluid_1077 <- read_excel(here(sm_1077_folder,
                                       "landuse_deluid_1077.xlsx"))

#write.csv(landuse_deluid_1077, here(sm_1077_folder,
#                                       "landuse_deluid_1077.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

# School Recommendations

## Dominguez Channel Watershed

### 2034 - Gardena High School 

Subbasin 2034 modeled for Gardena High School (Jurished: 203428, City: Gardena).

**Create CSV File**

```{r}



# Read the delineation excel sheet and convert to csv
landuse_deluid_2034 <- read_excel(here(dc_2034_folder,
                                       "landuse_deluid_2034.xlsx"))

write.csv(landuse_deluid_2034, here(dc_2034_folder,
                                       "landuse_deluid_2034.csv"),
          row.names = FALSE)
```

#### Loading

#### Landuse

### 2088 - Narbonne High School

Subbasin 2088 modeled for Narbonne High School (Jurished: 208849, City: Harbor City).

**Create CSV Files**

```{r}



# Read the delineation excel sheet and convert to csv
landuse_deluid_2088 <- read_excel(here(dc_2088_folder,
                                       "landuse_deluid_2088.xlsx"))

#write.csv(landuse_deluid_2088, here(dc_2088_folder,
#                                       "landuse_deluid_2088.csv"),
#          row.names = FALSE)
```

#### **Loading**

#### **Landuse**

### 2122 - San Pedro High School 

Subbasin 2122 modeled for San Pedro High School (Jurished: 212249, City: San Pedro).

**Create CSV Files**

```{r}



# Read the delineation excel sheet and convert to csv
landuse_deluid_2122 <- read_excel(here(dc_2122_folder,
                                       "landuse_deluid_2122.xlsx"))

#write.csv(landuse_deluid_2122, here(dc_2122_folder,
#                                       "landuse_deluid_2122.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

## Los Angeles River Watershed

### 6873 - Birmingham Community Charter High School 

Subbasin 6873 modeled for Birmingham Community Charter High School (Jurished: 687349, City: Van Nuys).

**Create CSV File**

```{r}


# Read the delineation excel sheet and convert to csv
landuse_deluid_6873 <- read_excel(here(lar_6873_folder,
                                       "landuse_deluid_6873.xlsx"))

#write.csv(landuse_deluid_6873, here(lar_6873_folder,
#                                       "landuse_deluid_6873.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

### 6682 - Francis Polytechnic High School

Subbasin 6682 modeled for Francis Polytechnic High School (Jurished: 668249, City: Sun Valley).

**Create CSV File**

```{r}



# Read the delineation excel sheet and convert to csv
landuse_deluid_6682 <- read_excel(here(lar_6682_folder,
                                       "landuse_deluid_6682.xlsx"))

#write.csv(landuse_deluid_6682, here(lar_6682_folder,
#                                       "landuse_deluid_6682.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

### 6697 - San Fernando High School

Subbasin 6697 modeled for San Fernando High School (Jurished: 669749, City: San Fernando).

**Create CSV File**

```{r}



# Read the delineation excel sheet and convert to csv
landuse_deluid_6697 <- read_excel(here(lar_6697_folder,
                                       "landuse_deluid_6697.xlsx"))

#write.csv(landuse_deluid_6697, here(lar_6697_folder,
#                                       "landuse_deluid_6697.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

### 6925 - Cleveland Charter High School 

Subbasin 6925 modeled for Cleveland Charter High School (Jurished: 692549, City: Reseda).

**Create CSV File**

```{r}



# Read the delineation excel sheet and convert to csv
landuse_deluid_6925 <- read_excel(here(lar_6925_folder,
                                       "landuse_deluid_6925.xlsx"))

#write.csv(landuse_deluid_6925, here(lar_6925_folder,
#                                       "landuse_deluid_6925.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

## Santa Monica Watershed

### 1067 - Crenshaw High School STEMM Magnet 

Subbasin 1067 modeled for Crenshaw High School STEMM Magnet (Jurished: 106749, City: Los Angeles).

**Create CSV File**

```{r}



# Read the delineation excel sheet and convert to csv
landuse_deluid_1067 <- read_excel(here(sm_1067_folder,
                                       "landuse_deluid_1067.xlsx"))

write.csv(landuse_deluid_1067, here(sm_1067_folder,
                                       "landuse_deluid_1067.csv"),
          row.names = FALSE)
```

#### Loading

#### Landuse

### 1110 - Kennedy Community of Schools 

Subbasin 1110 modeled for Kennedy Community of Schools (Jurished: 111049, City: Los Angeles).

**Create CSV File**

```{r}



# Read the delineation excel sheet and convert to csv
landuse_deluid_1110 <- read_excel(here(sm_1110_folder,
                                       "landuse_deluid_1110.xlsx"))

#write.csv(landuse_deluid_1110, here(sm_1110_folder,
#                                       "landuse_deluid_1110.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

### 1061 - Dorsey High School 

Subbasin 1061 modeled for Dorsey High School (Jurished: 106149, City: Los Angeles).

**Create CSV File**

```{r}



# Read the delineation excel sheet and convert to csv
landuse_deluid_1061 <- read_excel(here(sm_1061_folder,
                                       "landuse_deluid_1061.xlsx"))

#write.csv(landuse_deluid_1061, here(sm_1061_folder,
#                                       "landuse_deluid_1061.csv"),
#          row.names = FALSE)
```

#### Loading

#### Landuse

## San Gabriel Watershed

No schools were selected as a recommendation for the San Gabriel watershed.
