---
title: "wmms_clean_data"
format: 
 html:
    embed-resources: true
    code-line-numbers: true
    code-wrap: true
    code-fold: true
    toc: true
author: Tina Tran 
editor: visual
warning: false
messages: false 
---

# WMMS Clean Data

**Load Libraries**

```{r, warning = FALSE, message = FALSE}
# Load library 
library(tidyverse)
library(here)
library(janitor)
library(patchwork)
library(ggplot2)
library(dplyr)
library(stringr)
library(readxl) # Read excel files
library(purrr)
```

**Overview**

The standard output model was selected for WMMS 2.0. WMMS 2.0 modeled the following parameters for the 20 total jurisheds (10 parks and 10 school recommendations) selected for this project's recommendations.

The data ouput filles include a jurished file, landuse, and stream (Note: some jurisheds have a pointsource output file, but it will not be used for the analysis for this project).

[**Output Parameters for Jurished Data:**]{.underline}\
TT Time interval: 60 min Output option: day\
TT PREC precipitation (rain + snow) volume (in-acre/day)\
TT SURO surface outflow volume (in-acre/day)\
TT IFWO interflow outflow volume (in-acre/day)\
TT AGWO groundwater outflow volume (in-acre/day)\
TT PERO total outflow rate volume (SURO+IFWO+AGWO) (in-acre/day)\
TT DEP stream depth (ft)\
TT AVDEP stream average depth (ft)\
TT TAU bed shear stress (kg/m\^2)\
TT RO total rate of outflow from RCHRES (cfs)\
TT SOSED sediments load from land (english tons/da**y)**\
TT SSEDOUT1 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT2 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT3 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT total suspended solid concentration in outflow from the RCHRES (mg/l)\
TT POQUAL1 total flux of QUAL from the PLS_TN (lb/day)\
TT POQUAL2 total flux of QUAL from the PLS_TP (lb/day)\
TT POQUAL3 total flux of QUAL from the PLS_TCd (lb/day)\
TT POQUAL4 total flux of QUAL from the PLS_TCu (lb/day)\
TT POQUAL5 total flux of QUAL from the PLS_TPb (lb/day)\
TT POQUAL6 total flux of QUAL from the PLS_TZn (lb/day)\
TT CONC1 TN dissolved concentration (average) in RCHRES (mg/l)**\
**TT CONC2 TP dissolved concentration (average) in RCHRES (mg/l)\
TT CONC3 TCd dissolved concentration (average) in RCHRES (ug/l)\
TT CONC4 TCu dissolved concentration (average) in RCHRES (ug/l)\
TT CONC5 TPb dissolved concentration (average) in RCHRES (ug/l)\
TT CONC6 TZn dissolved concentration (average) in RCHRES (ug/l)

For the purpose of estimating potential fecal indicator bacteria (FIB) loading in the jurished, sediment (SOSED), nitrogen (CONC1 TN), and surface outflow volume (SURO) have been selected as a proxy. WMMS 2.0 uses daily precipitation data from 2006-2018 to estimate these output parameters for 2008-2018.

## **Folder Pathways**

**Park Recommendations**

```{r}
# Locate the Dominguez Channel 2113 Folder
dc_2113_folder <- here("data", "wmms", "park_rec", "dc_2113")

# Locate the Dominguez Channel 2074 Folder
dc_2074_folder <- here("data", "wmms", "park_rec", "dc_2074")

# Locate the Los Angeles River 6387 Folder
lar_6387_folder <- here("data", "wmms", "park_rec", "lar_6387")

# Locate the Los Angeles River 6396 Folder
lar_6396_folder <- here("data", "wmms", "park_rec", "lar_6396")

# Locate the Los Angeles River 6480 Folder
lar_6480_folder <- here("data", "wmms", "park_rec", "lar_6480")

# Locate the San Gabriel 5109 Folder
sg_5109_folder <- here("data", "wmms", "park_rec", "sg_5109")

# Locate the San Gabriel 5118 Folder
sg_5118_folder <- here("data", "wmms", "park_rec", "sg_5118")

# Locate the San Gabriel 5120 Folder
sg_5120_folder <- here("data", "wmms", "park_rec", "sg_5120")

# Locate the Santa Monica 1030 Folder
sm_1030_folder <- here("data", "wmms", "park_rec", "sm_1030")

# Locate the Santa Monica 1077 Folder
sm_1077_folder <- here("data", "wmms", "park_rec", "sm_1077")
```

**School Recommendations**

```{r}
# Locate the Dominguez Channel 2034 Folder
dc_2034_folder <- here("data", "wmms", "school_rec", "dc_2034")

# Locate the Dominguez Channel 2088 Folder
dc_2088_folder <- here("data", "wmms", "school_rec", "dc_2088")

#Locate the Dominguez Channel 2122 Folder
dc_2122_folder <- here("data", "wmms", "school_rec", "dc_2122")

# Locate the Los Angeles River 6873 Folder
lar_6873_folder <- here("data", "wmms", "school_rec", "lar_6873")

# Locate the Los Angeles River 6682 Folder
lar_6682_folder <- here("data", "wmms", "school_rec", "lar_6682")

# Locate the Los Angeles River 6697 Folder
lar_6697_folder <- here("data", "wmms", "school_rec", "lar_6697")

# Locate the Los Angeles River 6925 Folder
lar_6925_folder <- here("data", "wmms", "school_rec", "lar_6925")

# Locate the Santa Monica 1067 Folder
sm_1067_folder <- here("data", "wmms", "school_rec", "sm_1067")

# Locate the Santa Monica 1110 Folder
sm_1110_folder <- here("data", "wmms", "school_rec", "sm_1110")

# Locate the Santa Monica 1061 Folder
sm_1061_folder <- here("data", "wmms", "school_rec", "sm_1061")

```

## **CSV File from the excel sheets**

## **Process All Jurisheds**

```{r}
# Convert all existing jurished excel files into a csv and add it to the existing folder

#walk(jurisheds, function(j){

#  excel_file <- sub("\\.csv$", ".xlsx", j$file)
#  excel_path <- here(j$folder, excel_file)

#  if(file.exists(excel_path)){

#    message("Converting: ", excel_file)

#    juri_xl <- read_excel(excel_path, skip = 51)

#    write.csv(juri_xl,
#      here(j$folder, j$file),
#      row.names = FALSE)

#  } else {

#    message("Missing file: ", excel_file)}})
```

```{r}
# Create a Jurished List 
jurisheds <- list(
  # Park Recommendations
  juri2074 = list(folder = dc_2074_folder, 
                  file="juri_dc_2074.csv"),
  juri2113 = list(folder = dc_2113_folder, 
                  file="juri_dc_2113.csv"),
  juri6387 = list(folder = lar_6387_folder, 
                  file="juri_lar_6387.csv"),
  juri6396 = list(folder = lar_6396_folder, 
                  file="juri_lar_6396.csv"),
  juri6480 = list(folder = lar_6480_folder, 
                  file="juri_lar_6480.csv"),
  juri5109 = list(folder = sg_5109_folder, 
                  file="juri_sg_5109.csv"),
  juri5118 = list(folder = sg_5118_folder, 
                  file="juri_sg_5118.csv"),
  juri5120 = list(folder = sg_5120_folder, 
                  file="juri_sg_5120.csv"),
  juri1030 = list(folder = sm_1030_folder, 
                  file="juri_sm_1030.csv"),
  juri1077 = list(folder = sm_1077_folder, 
                  file="juri_sm_1077.csv"),
  
  # School Recommendations
  juri2034 = list(folder = dc_2034_folder, 
                  file="juri_dc_2034.csv"),
  juri2088 = list(folder = dc_2088_folder, 
                  file="juri_dc_2088.csv"),
  juri2122 = list(folder = dc_2122_folder, 
                  file="juri_dc_2122.csv"),
  juri6873 = list(folder = lar_6873_folder, 
                  file="juri_lar_6873.csv"),
  juri6682 = list(folder = lar_6682_folder, 
                  file="juri_lar_6682.csv"),
  juri6697 = list(folder = lar_6697_folder, 
                  file="juri_lar_6697.csv"),
  juri6925 = list(folder = lar_6925_folder, 
                  file="juri_lar_6925.csv"),
  juri1067 = list(folder = sm_1067_folder, 
                  file="juri_sm_1067.csv"),
  juri1110 = list(folder = sm_1110_folder, 
                  file="juri_sm_1110.csv"),
  juri1061 = list(folder = sm_1061_folder, 
                  file="juri_sm_1061.csv"))
```

## **Loading Calcualtions**

**Function**

This code reads and cleans in all of the WMMS 2.0 jurished csv files (n = 20) that had estimated the daily loading parameters for various pollutants and precipitation from 2008-2018 using the standard model output setting. The function also converts units based on the methods from the Los Angeles County Department of Public Works (LACDPW) excel sheet calculations.

The code creates 5 data tables using the daily 2008-2018 output from WMMS 2.0:

1.  **Watershed Capture Analysis Table**

-   **Average**: average daily surface outflow volume (acre-ft/day)

-   **High**: maximum daily surface outflow volume (acre-ft/day)

-   **10-year storm:** daily storm runoff volume corresponding to the 90th percentile of wet-day storm volumes (acre-ft/day)

-   **100-year storm:** daily storm runoff volume corresponding to the 99th percentile of wet-day storm volumes (acre-ft/day)

-   **Total 85th Percentile Runoff Volume:** daily storm runoff volume corresponding to the 85th percentile of a wet-day storm volume (acre-ft/day), used as as a treatment capture threshold.

2.  **Loading Table**

2.  **Reduction Table**
3.  **Percent Reduction Table**
4.  **Annual Average Table**

```{r}
# Create a loop to process all jurished files 
process_juri <- function(folder, file_name){

  # Read and clean data  
  juri_load <- read.csv(here(folder, file_name)) |>
    clean_names() |> # make everything lowersnakecase
    rename_with(~ str_remove(.x, "^tt_") |> # removes "tt_" from names
                  str_extract("^[^_]+"), # keep the abbreviated name before "_"
                starts_with("tt_"))|> # renaming only for columns with tt
    select(subbasin, year, month, day, prec,
           suro, ifwo, agwo, pero, dep, avdep, ro,
           sosed, conc1, conc2) |> # keep these columns 
    rename(depth = dep, # depth of the stream (ft)
      tn_mg_l = conc1, # conc1 is total nitrogen (mg/L)
      tp_mg_l = conc2) |> # conc2 is total phosphorous (mg/L)
    mutate(
      date = as.Date(paste(year, month, day, sep="-")),
      suro_ft_acre_day = suro / 12, # convert surface outflow volume to ft-acre/day from in-acre/day
      pero_ft_acre_day = pero / 12, # convert total outflow rate volume to ft-acre/day from in-acre/day
      tn_lb_ac_ft = tn_mg_l * 2.71936, # convert total nitrogen to ac-lb/ft
      tp_lb_ac_ft = tp_mg_l * 2.71936, # convert total phosphorous to ac-lb/ft
      
      # Add new column for storm days and storm volume 
      storm_volume_ac_ft_day = if_else(prec > 0, #dry days = 0
                                       suro_ft_acre_day, 0),
      
      # Total Nitrogen Loading 
      tn_load_lb_day = tn_lb_ac_ft * suro_ft_acre_day)  
  
  

  
# Calculate Watershed Capture Analysis Information 
storm_vals <- juri_load$storm_volume_ac_ft_day[juri_load$prec > 0]

  # Create the 10-year storm 
  storm_90th <- quantile(storm_vals, .90, na.rm=TRUE)
  
  # Create the 100-yr storm 
  storm_99th <- quantile(storm_vals, .99, na.rm=TRUE)
  
  # Create the Runoff 85th Percentile 
  runoff_85th <- quantile(storm_vals, .85, na.rm=TRUE)
  
  
  
# Watershed capture Analysis Table
  capture_summary <- juri_load |>
    summarise(
      avg_suro_acft_day = mean(suro_ft_acre_day, na.rm = TRUE),
      max_suro_acft_day = max(suro_ft_acre_day, na.rm = TRUE),

      # Only storms (wet days)
      avg_storm_vol_acft_day = mean(storm_vals, na.rm = TRUE),
      max_storm_vol_acft_day = max(storm_vals, na.rm = TRUE),

      perc_85_acft_day = runoff_85th,
      perc_90_acft_day = storm_90th,
      perc_99_acft_day = storm_99th)


# Table - Estimate Loading Per Day Per Year For Dry + Wet Days
loading_table <- juri_load |>
  group_by(year) |>
  
            # Dissolved Nitrogen Loading 
  summarise(total_tn_lb_yr = sum(tn_load_lb_day, na.rm = TRUE),
            avg_tn_lb_day = mean(tn_load_lb_day, na.rm = TRUE), 
            avg_tn_wet_lb_day = mean(tn_load_lb_day[prec > 0], 
                                     na.rm = TRUE), 
            
            # Sediment loading
            total_sed_lb_yr = sum(sosed, na.rm = TRUE),
            avg_sed_lb_day = mean(sosed, na.rm = TRUE),
            avg_sed_wet_lb_day = mean(sosed[prec > 0],
                                      na.rm = TRUE),
            
            # Surface Outflow Volume
            total_suro_acft_yr = sum(suro_ft_acre_day, 
                                      na.rm = TRUE),
            avg_suro_acft_day = mean(suro_ft_acre_day, 
                                     na.rm = TRUE),
            avg_suro_wet_acft_day = mean(suro_ft_acre_day[prec > 0],
                                      na.rm = TRUE),
            .groups = "drop")
                              

  
# Calulcate Loading Reductions Per Day
  juri_load <- juri_load |>
    
    mutate(
      
      # Calculate the potential capture fraction
      capture_frac = if_else(suro_ft_acre_day > 0,
                             pmin(runoff_85th / suro_ft_acre_day, 
                                  1), 0),
      tn_reduce_lb_day = tn_load_lb_day * capture_frac,
      sed_reduce_tons_day = sosed * capture_frac,
      suro_reduce_acft_day = suro_ft_acre_day * capture_frac)
  
  

  # Table - Wet Days Reduction Calculations Per Day Per Year
  reduction_table <- juri_load |>
    filter(prec > 0) |>
    group_by(year) |>
    summarise(
      
      # Nitrogen
      total_tn_reduce_per_wet_yr = sum(tn_reduce_lb_day,  # total nitrogen reeduction per wet day per year (lb/year)
                             na.rm=TRUE), 
      avg_tn_reduce_per_wet_day = mean(tn_reduce_lb_day, 
                                na.rm=TRUE),
      
      # Sediment Reduction
      total_sed_reduce_per_wet_yr = sum(sed_reduce_tons_day , # total sediment per wet day
                              na.rm=TRUE), 
      avg_sed_reduce_per_wet_day = mean(sed_reduce_tons_day, # average sediment per wet day
                                 na.rm=TRUE), 
      
      # Surface Runoff Volume Reduction
      total_suro_reduce_wet_yr = sum(suro_reduce_acft_day, 
                                     na.rm=TRUE),
      avg_suro_reduce_wet_day = mean(suro_reduce_acft_day, 
                                     na.rm=TRUE),

      # Total Outflow Volume
      total_pero = sum(pero_ft_acre_day, na.rm=TRUE), # total outflow
      avg_pero = mean(pero_ft_acre_day, na.rm=TRUE),

      wet_days = n(), # count number of wet days 
      .groups="drop")

  
  
# Table - Percent Reduction based on 85th Percentile Capture For Wet Days
  percent_reduction_table <- loading_table |>
    left_join(reduction_table, by = "year") |>
    mutate(
      
      # Calculate Nitrogen Percent Reduction Per Year 
      pct_tn_reduction_yr = ((total_tn_reduce_per_wet_yr / total_tn_lb_yr)* 100),
      
      # Calculate N Percent Reduction Per Wet Day 
      pct_tn_reduction_day = ((avg_tn_reduce_per_wet_day/avg_tn_wet_lb_day)*100),
      
      
      # Calculate Sediment Percent Reduction Per Year 
      pct_sed_reduction_yr = ((total_sed_reduce_per_wet_yr / total_sed_lb_yr)*100),
      
      # Calculate Sediment Percent Reduction Per Day 
      pct_sed_reduction_day = ((avg_sed_reduce_per_wet_day/avg_sed_wet_lb_day) * 100),
      
      
      # Surface runoff capture percentage Per Year (volume)
      pct_volume_capture_yr = ((total_suro_reduce_wet_yr / total_suro_acft_yr) * 100),
      pct_volume_capture_day = ((avg_suro_reduce_wet_day / avg_suro_wet_acft_day) * 100))

  
  
  
  # Table - 10-year averages (menas of means) of Reduction & %
annual_avg_table <- percent_reduction_table |>
  summarise(
  
  # Nitrogen 
    total_tn_10yr = mean(total_tn_reduce_per_wet_yr),
    avg_tn_per_wet_day_10yr = mean(avg_tn_reduce_per_wet_day),
    pct_tn_reduction = mean(pct_tn_reduction_day, na.rm = TRUE),


  # Sediment 
    total_sed_10yr = mean(total_sed_reduce_per_wet_yr),
    avg_sed_per_wet_day_10yr = mean(avg_sed_reduce_per_wet_day),
    pct_sed_reduction = mean(pct_sed_reduction_day, na.rm = TRUE),


  # Surface Outflow Volume 
    total_suro_10yr = mean(total_suro_reduce_wet_yr),
    avg_suro_10yr = mean(avg_suro_reduce_wet_day),
    pct_volume_capture = mean(pct_volume_capture_day, na.rm = TRUE),


  # Total Outflow Volume 
    total_pero_10yr = mean(total_pero),
    avg_pero_10yr = mean(avg_pero),
  
  # Total Wet Days simulated that Year
    wet_days_10yr = sum(wet_days))


  return(list(
    watershed_capture = capture_summary,
    loading = loading_table,
    reduction = reduction_table,
    percent = percent_reduction_table,
    annual = annual_avg_table)) 
}


```

**Extract the Jurished Data**

This code extracts the results from the looped function that calcualted the values from each jurished and makes it into a table.

```{r}
# Store all the results 
all_results <- purrr::imap(jurisheds, function(j, name) {
  process_juri(j$folder, j$file)})


# Print the 5 tables for each jurished 
purrr::walk2(all_results, names(all_results), function(result, name) {
  
  cat("\n====================================\n")
  cat("Jurished:", name, "\n")
  cat("====================================\n\n")
  
  cat("Watershed Capture\n")
  print(result$watershed_capture)
  
  cat("\nLoading Table\n")
  print(result$loading)
  
  cat("\nReduction Table\n")
  print(result$reduction)
  
  cat("\nPercent Reduction Table\n")
  print(result$percent)
  
  cat("\nAnnual 10-Year Summary\n")
  print(result$annual)
})
```

**Create a Data Table Combining all 20 Jurisheds together**

This code will create 5 data tables, representing the following information:

-   Watershed Capture Analysis Summary

-   Loading Table

-   Percent Reduction Table

-   Reduction Table

-   Annual Average Reduction

```{r}
# Create Cumulative Watershed Capture Analysis 
watershed_all <- purrr::map2_dfr(
  all_results,
  names(all_results),
  ~ dplyr::mutate(
      .x$watershed_capture,
      jurished = .y,
      jurished_id = as.numeric(stringr::str_extract(.y, "\\d+"))))

table(watershed_all$jurished_id) # check n jurisheds

# Create Cumulative Loading Table
loading_all <- purrr::map2_dfr(
  all_results,
  names(all_results),
  ~ dplyr::mutate(
      .x$loading,
      jurished = .y,
      jurished_id = as.numeric(stringr::str_extract(.y, "\\d+"))))

table(loading_all$jurished_id) # check n jurisheds


# Create Cumulative Reduction Table
reduction_all <- purrr::map2_dfr(
  all_results,
  names(all_results),
  ~ dplyr::mutate(
      .x$reduction,
      jurished = .y,
      jurished_id = as.numeric(stringr::str_extract(.y, "\\d+"))))

table(reduction_all$jurished_id) # check n jurisheds


# Create Cumulative Percentage Reduction Table
percent_all <- purrr::map2_dfr(
  all_results,
  names(all_results),
  ~ dplyr::mutate(
      .x$percent,
      jurished = .y,
      jurished_id = as.numeric(stringr::str_extract(.y, "\\d+"))))


table(percent_all$jurished_id) # check n jurisheds

# Create Cumulative 10-Year Summary Table 
annual_all <- purrr::map2_dfr(
  all_results,
  names(all_results),
  ~ dplyr::mutate(
      .x$annual,
      jurished = .y,
      jurished_id = as.numeric(stringr::str_extract(.y, "\\d+"))))

table(annual_all$jurished_id) # check n jurisheds



# Write the CSV Files
#Folder location for analysis
wmms_analysis_folder <- here("data", "wmms", "analysis")



#write.csv(watershed_all, 
#          here(wmms_analysis_folder, "watershed_all.csv"),
#          row.names = FALSE)
                                    
#write.csv(loading_all, 
#          here(wmms_analysis_folder, "loading_all.csv"),
#          row.names = FALSE)

#write.csv(reduction_all, 
#          here(wmms_analysis_folder, "reduction_all.csv"), 
#          row.names = FALSE)

#write.csv(percent_all, 
#          here(wmms_analysis_folder, "percent_reduction_all.csv"),
#          row.names = FALSE)

#write.csv(annual_all, 
#          here(wmms_analysis_folder, "annual_summary_all.csv"), 
#          row.names = FALSE)
```

# Park Recommendations

```{r}
landuse_colors <- c(
  "Residential" = "#F4A3A3",
  "Commercial" = "#E31A1C",
  "Industrial" = "#A50F15",
  "Pervious(Developed)" = "#FB9A99",
  "Other Developed" = "#D6604D",
  "Road" = "#6D6D6D",
  "Agriculture" = "#FFD92F",
  "Vegetation" = "#1B9E77",
  "Water" = "#1F78B4")
```

```{r}
classify_landuse <- function(data) {
  data |>
    mutate(main_class = case_when(
      
      # Specific Developed Types
      str_starts(deluname, "Dev_ResHigh")  ~ "Residential",
      str_starts(deluname, "Dev_ResLow")   ~ "Residential",
      str_starts(deluname, "Dev_Com")      ~ "Commercial",
      str_starts(deluname, "Dev_Ind")      ~ "Industrial",
      str_starts(deluname, "Dev_Pervious") ~ "Pervious(Developed)",
      
      # Catch ALL other Dev categories
      str_starts(deluname, "Dev")          ~ "Other Developed",
      
      # Other Land Uses
      str_starts(deluname, "Road")         ~ "Road",
      str_starts(deluname, "Agriculture")  ~ "Agriculture",
      str_starts(deluname, "Veg")          ~ "Vegetation",
      str_starts(deluname, "Water")        ~ "Water",
      
      TRUE ~ "Other"))}
```

## Dominguez Channel Watershed

### 2113 - Banning Park and Museum

Subbasin 2113 was modeled for Banning Park and Museum (Jurished: 211349, City: Los Angeles City, Acres: 21.071).

#### **Landuse**

```{r}
# Landuse Data 
dc_lu_2113_raw <- read.csv(here(dc_2113_folder, "landuse_dc_2113.csv"))


# Read the delineation excel sheet and convert to csv
landuse_deluid_2113 <- read_excel(here(dc_2113_folder,
                                       "landuse_deluid_2113.xlsx"))

#write.csv(landuse_deluid_2113, here(dc_2113_folder,
#                                       "landuse_deluid_2113.csv"),
#          row.names = FALSE)


#Check the data
unique(dc_lu_2113_raw$deluid) #total of 96

# Pivot the long table
dc_lu_2113_clean <- dc_lu_2113_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1) 
head(dc_lu_2113_clean) |>
  clean_names()


# Check shared names prior to joining 
names(dc_lu_2113_clean)
names(landuse_deluid_2113)
intersect(names(dc_lu_2113_clean), names(landuse_deluid_2113))


# Join Tables 
dc_lu_2113_join <- dc_lu_2113_clean |>
  left_join(landuse_deluid_2113, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 2113) 


# Check number of rows 
nrow(dc_lu_2113_clean)
nrow(dc_lu_2113_join)

sum(is.na(dc_lu_2113_join[[names(landuse_deluid_2113)[3]]]))


# Categorize the delineations into main classes for easier data manipulation
dc_plot_2113 <- classify_landuse(dc_lu_2113_join) 

```

```{r}
# Summarize the Average Annual data
lu_area_2113_sum <- dc_plot_2113 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Landuse Type Distribution Plot 
lu_2113_plot <- ggplot(lu_area_2113_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Banning Park & Museum (Juri: 2113) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none",
        axis.title.x = element_blank())

print(lu_2113_plot)

# Sediment Loading Plot
lu_2113_sed <- ggplot(lu_area_2113_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none",
        axis.title.x = element_blank())

print(lu_2113_sed)


# Nitrogen Flux Plot
lu_2113_n <- ggplot(lu_area_2113_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Average Nitrogen Flux (lbs/year)",
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none")

print(lu_2113_n)

# Patchwork
combined_2113 <- (lu_2113_plot / lu_2113_sed /lu_2113_n) +
  plot_layout(ncol = 1)

print(combined_2113)

# Save
ggsave(here(dc_2113_folder, "lu_plot_2113.png"),
                           height = 12, width = 6, dpi = 300)
  
```

### 2074 - Jesse Owens Community Regional Park

Subbasin 2074 was modeled for Jesse Owens Community Regional Park (Jurished: 207449, City: Los Angeles City, Acres: 19.118).

#### **Landuse**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_2074 <- read_excel(here(dc_2074_folder,
                                       "landuse_deluid_2074.xlsx"))

#write.csv(landuse_deluid_2074, here(dc_2074_folder,
#                                       "landuse_deluid_2074.csv"),
#          row.names = FALSE)
```

```{r}
# Dominguez Channel 2074 Landuse Data 
dc_lu_2074_raw <- read.csv(here(dc_2074_folder, 
                                "landuse_dc_2074.csv"))

# Dominguez Channel 2074 Delineation Data
dc_deluid_2074 <- read.csv(here(dc_2074_folder, 
                                "landuse_deluid_2074.csv"))

unique(dc_lu_2074_raw$deluid)

dc_lu_2074_clean <- dc_lu_2074_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(dc_lu_2074_clean)
names(dc_deluid_2074)
intersect(names(dc_lu_2074_clean), names(dc_deluid_2074))

dc_lu_2074_join <- dc_lu_2074_clean |>
  left_join(dc_deluid_2074, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 2074) 

nrow(dc_lu_2074_clean)
nrow(dc_lu_2074_join)

sum(is.na(dc_lu_2074_join[[names(dc_deluid_2074)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
dc_plot_2074 <- classify_landuse(dc_lu_2074_join) 

```

```{r}
# Summarize the Average Annual data
lu_area_2074_sum <- dc_plot_2074 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Landuse Type Distribution Plot 
lu_2074_plot <- ggplot(lu_area_2074_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Jesse Owens Community Regional Park (Juri: 2074) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none",
        axis.title.x = element_blank())

print(lu_2074_plot)

# Sediment Loading Plot
lu_2074_sed <- ggplot(lu_area_2074_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none",
        axis.title.x = element_blank())

print(lu_2074_sed)


# Nitrogen Flux Plot
lu_2074_n <- ggplot(lu_area_2074_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Average Nitrogen Flux (lbs/year)",
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none")

print(lu_2074_n)

# Patchwork
combined_2074 <- (lu_2074_plot / lu_2074_sed /lu_2074_n) +
  plot_layout(ncol = 1)

print(combined_2074)

# Save
ggsave(here(dc_2074_folder, "lu_plot_2074.png"),
                           height = 12, width = 6, dpi = 300)


```

## Los Angeles River Watershed

### 6387 - Pecan Playground

Subbasin 6387 was modeled for Pecan Playground (Jurished: 638749, City: Los Angeles City, Acres: 4.282).

#### Landuse

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_6387 <- read_excel(here(lar_6387_folder,
                                       "landuse_deluid_6387.xlsx"))

#write.csv(landuse_deluid_6387, here(lar_6387_folder,
#                                       "landuse_deluid_6387.csv"),
#          row.names = FALSE)
```

```{r}
lar_lu_6387_raw <- read.csv(here(lar_6387_folder, 
                                 "landuse_lar_6387.csv"))
lar_deluid_6387 <- read.csv(here(lar_6387_folder, 
                                 "landuse_deluid_6387.csv")) |>
  filter(subbasin == "6387")

unique(lar_lu_6387_raw$deluid)

lar_lu_6387_clean <- lar_lu_6387_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(lar_lu_6387_clean)
names(lar_deluid_6387)
intersect(names(lar_lu_6387_clean), names(lar_deluid_6387))

lar_lu_6387_join <- lar_lu_6387_clean |>
  left_join(lar_deluid_6387, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 6387)

nrow(lar_lu_6387_clean)
nrow(lar_lu_6387_join)

sum(is.na(lar_lu_6387_join[[names(lar_deluid_6387)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
lar_plot_6387 <- classify_landuse(lar_lu_6387_join) 

```

```{r}
# Summary Statistics 
lu_area_6387_sum <- lar_plot_6387 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Land Use Distribution Plot 
lu_6387_plot <- ggplot(lu_area_6387_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Pecan Playground (Juri: 6387) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())

# Sediment Plot 
lu_6387_sed <- ggplot(lu_area_6387_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())

# Nitrogen Plot 
lu_6387_n <- ggplot(lu_area_6387_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", 
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")


#Combined Plot 
combined_6387 <- (lu_6387_plot / lu_6387_sed / lu_6387_n) + plot_layout(ncol = 1)
ggsave(here(lar_6387_folder, "lu_plot_6387.png"), combined_6387, height = 12, width = 6, dpi = 300)

```

### 6396 - State Street Recreation Center

Subbasin 6396 was modeled for State Street Recreation Center (Jurished: 639649, City: Los Angeles City, Acres: 2.617).

#### **Landuse**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_6396 <- read_excel(here(lar_6396_folder,
                                       "landuse_deluid_6396.xlsx"))

#write.csv(landuse_deluid_6396, here(lar_6396_folder,
#                                       "landuse_deluid_6396.csv"),
#          row.names = FALSE)
```

```{r}
lar_lu_6396_raw <- read.csv(here(lar_6396_folder, 
                                 "landuse_lar_6396.csv"))
lar_deluid_6396 <- read.csv(here(lar_6396_folder,
                                 "landuse_deluid_6396.csv"))

unique(lar_lu_6396_raw$deluid)

lar_lu_6396_clean <- lar_lu_6396_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(lar_lu_6396_clean)
names(lar_deluid_6396)
intersect(names(lar_lu_6396_clean), names(lar_deluid_6396))

lar_lu_6396_join <- lar_lu_6396_clean |>
  left_join(lar_deluid_6396, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 6396)

nrow(lar_lu_6396_clean)
nrow(lar_lu_6396_join)

sum(is.na(lar_lu_6396_join[[names(lar_deluid_6396)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
lar_plot_6396 <- classify_landuse(lar_lu_6396_join) 

```

```{r}
lu_area_6396_sum <- lar_plot_6396 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

lu_6396_plot <- ggplot(lu_area_6396_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", title = "State Street Recreation Center (Juri: 6396) Landuse Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none", axis.title.x = element_blank())

lu_6396_sed <- ggplot(lu_area_6396_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none", axis.title.x = element_blank())

lu_6396_n <- ggplot(lu_area_6396_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")

combined_6396 <- (lu_6396_plot / lu_6396_sed / lu_6396_n) + plot_layout(ncol = 1)
ggsave(here(lar_6396_folder, "lu_plot_6396.png"), combined_6396, height = 12, width = 6, dpi = 300)
```

### 6480 - Glassel Park

Subbasin 6480 was modeled for Glassel Park (Jurished: 648049, City: Los Angeles City, Acres: 12.663).

#### Landuse

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_6480 <- read_excel(here(lar_6480_folder,
                                       "landuse_deluid_6480.xlsx"))

#write.csv(landuse_deluid_6480, here(lar_6480_folder,
#                                       "landuse_deluid_6480.csv"),
#          row.names = FALSE)
```

```{r}
lar_lu_6480_raw <- read.csv(here(lar_6480_folder, 
                                 "landuse_lar_6480.csv"))
lar_deluid_6480 <- read.csv(here(lar_6480_folder,
                                 "landuse_deluid_6480.csv"))

unique(lar_lu_6480_raw$deluid)

lar_lu_6480_clean <- lar_lu_6480_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(lar_lu_6480_clean)
names(lar_deluid_6480)
intersect(names(lar_lu_6480_clean), names(lar_deluid_6480))

lar_lu_6480_join <- lar_lu_6480_clean |>
  left_join(lar_deluid_6480, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 6480)

nrow(lar_lu_6480_clean)
nrow(lar_lu_6480_join)

sum(is.na(lar_lu_6480_join[[names(lar_deluid_6480)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
lar_plot_6480 <- classify_landuse(lar_lu_6480_join) 

```

```{r}
lu_area_6480_sum <- lar_plot_6480 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

lu_6480_plot <- ggplot(lu_area_6480_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Glassel park (Juri: 6480) Landuse Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none", axis.title.x = element_blank())

lu_6480_sed <- ggplot(lu_area_6480_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none", axis.title.x = element_blank())

lu_6480_n <- ggplot(lu_area_6480_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")

combined_6480 <- (lu_6480_plot / lu_6480_sed / lu_6480_n) + plot_layout(ncol = 1)

ggsave(here(lar_6480_folder, "lu_plot_6480.png"), combined_6480, height = 12, width = 6, dpi = 300)
```

## San Gabriel Watershed

### 5109 - Rosewood Park

Subbasin 5109 was modeled for Rosewood Park (Jurished: 510916, City: Cerritos, Acres: 5.447).

#### Landuse

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_5109 <- read_excel(here(sg_5109_folder,
                                       "landuse_deluid_5109.xlsx"))

#write.csv(landuse_deluid_5109, here(sg_5109_folder,
#                                       "landuse_deluid_5109.csv"),
#          row.names = FALSE)
```

```{r}
sg_lu_5109_raw <- read.csv(here(sg_5109_folder, 
                                "landuse_sg_5109.csv"))
sg_deluid_5109 <- read.csv(here(sg_5109_folder, 
                                "landuse_deluid_5109.csv"))

unique(sg_lu_5109_raw$deluid)

sg_lu_5109_clean <- sg_lu_5109_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(sg_lu_5109_clean)
names(sg_deluid_5109)
intersect(names(sg_lu_5109_clean), names(sg_deluid_5109))

sg_lu_5109_join <- sg_lu_5109_clean |>
  left_join(sg_deluid_5109, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 5109)

nrow(sg_lu_5109_clean)
nrow(sg_lu_5109_join)

sum(is.na(sg_lu_5109_join[[names(sg_deluid_5109)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
sg_plot_5109 <- classify_landuse(sg_lu_5109_join) 
```

```{r}
# Summary Statistics 
lu_area_5109_sum <- sg_plot_5109 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Land Use Distribution Plot 
lu_5109_plot <- ggplot(lu_area_5109_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Rosewood Park (Juri: 5109) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_5109_plot)

# Sediment Plot 
lu_5109_sed <- ggplot(lu_area_5109_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_5109_sed)


# Nitrogen Plot 
lu_5109_n <- ggplot(lu_area_5109_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", 
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")
print(lu_5109_n)


#Combined Plot 
combined_5109  <- (lu_5109_plot / lu_5109_sed / lu_5109_n) + plot_layout(ncol = 1)
ggsave(here(sg_5109_folder, "lu_plot_5109.png"), combined_5109, height = 12, width = 6, dpi = 300)
```

### 5118 - Byron Zinn Park

Subbasin 5118 was modeled for Byron Zinn Park (Jurished: 511810, City: Bellflower, Acres: 4.827).

#### Landuse

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_5118 <- read_excel(here(sg_5118_folder,
                                       "landuse_deluid_5118.xlsx"))

#write.csv(landuse_deluid_5118, here(sg_5118_folder,
#                                       "landuse_deluid_5118.csv"),
#          row.names = FALSE)
```

```{r}
sg_lu_5118_raw <- read.csv(here(sg_5118_folder, 
                                "landuse_sg_5118.csv"))
sg_deluid_5118 <- read.csv(here(sg_5118_folder, 
                                "landuse_deluid_5118.csv"))

unique(sg_lu_5118_raw$deluid)

sg_lu_5118_clean <- sg_lu_5118_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(sg_lu_5118_clean)
names(sg_deluid_5118)
intersect(names(sg_lu_5118_clean), names(sg_deluid_5118))

sg_lu_5118_join <- sg_lu_5118_clean |>
  left_join(sg_deluid_5118, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 5118)

nrow(sg_lu_5118_clean)
nrow(sg_lu_5118_join)

sum(is.na(sg_lu_5118_join[[names(sg_deluid_5118)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
sg_plot_5118 <- classify_landuse(sg_lu_5118_join) 

```

```{r}
# Summary Statistics 
lu_area_5118_sum <- sg_plot_5118 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Land Use Distribution Plot 
lu_5118_plot <- ggplot(lu_area_5118_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Byron Zinn Park (Juri: 5118) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_5118_plot)

# Sediment Plot 
lu_5118_sed <- ggplot(lu_area_5118_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_5118_sed)


# Nitrogen Plot 
lu_5118_n <- ggplot(lu_area_5118_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", 
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")
print(lu_5118_n)


#Combined Plot 
combined_5118  <- (lu_5118_plot / lu_5118_sed / lu_5118_n) + plot_layout(ncol = 1)
ggsave(here(sg_5118_folder, "lu_plot_5118.png"), combined_5118, height = 12, width = 6, dpi = 300)
```

### 5120 - New River Park

Subbasin 5120 was modeled for New River Park (Jurished: 512057, City: Norwalk, Acres: 4.840).

#### **Loading**

[**Goal:**]{.underline} Estimate the total average annual loading for sediment, nitrogen, runoff volume (total surface outflow rate \* areas)

#### **Landuse**

The delineations used for this model include 96 types to calculate the average area based on landuse from 2008-2018 using input data from 2006-2018. We will group the delineations based on major land use types: road, developed, agriculture, vegetation, and water before plotting the data and analysis.

[**Goal**]{.underline}: Understand how much total average area in acres is distributed in this jurished based on landuse type.

```{r}
# San Gabriel Landuse Data 
sg_lu_5120_raw <- read.csv(here("data", "wmms", "park_rec", "sg_5120", "landuse_sg_5120.csv"))

# San Gabriel Delineation Data for Landuse
sg_deluid_5120 <- read.csv(here("data", "wmms", "park_rec", "sg_5120", "landuse_deluid_5120.csv"))


#Check the data
unique(sg_lu_5120_raw$deluid) #total of 96

# Pivot the long table
sg_lu_5120_clean <- sg_lu_5120_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1) 
head(sg_lu_5120_clean)


# Check shared names prior to joining 
names(sg_lu_5120_clean)
names(sg_deluid_5120)
intersect(names(sg_lu_5120_clean), names(sg_deluid_5120))


# Join Tables 
sg_lu_5120_join <- sg_lu_5120_clean |>
  left_join(sg_deluid_5120, by = c("subbasin", "deluid")) |>
  clean_names()|>
  filter(subbasin == 5120)


# Check number of rows 
nrow(sg_lu_5120_clean)
nrow(sg_lu_5120_join)

sum(is.na(sg_lu_5120_join[[names(sg_deluid_5120)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
sg_plot_5120 <- classify_landuse(sg_lu_5120_join) 

```

```{r}
# Summary Statistics 
lu_area_5120_sum <- sg_plot_5120 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Land Use Distribution Plot 
lu_5120_plot <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "New River Park (Juri: 5120) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_5120_plot)

# Sediment Plot 
lu_5120_sed <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_5120_sed)


# Nitrogen Plot 
lu_5120_n <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", 
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")
print(lu_5120_n)


#Combined Plot 
combined_5120  <- (lu_5120_plot / lu_5120_sed / lu_5120_n) + plot_layout(ncol = 1)
ggsave(here(sg_5120_folder, "lu_plot_5120.png"), combined_5120, height = 12, width = 6, dpi = 300)
```

## Santa Monica Watershed

### 1030 - Rogers Park

Subbasin 1030 was modeled for Rogers Park (Jurished: 103037, City: Inglewood, Acres: 12.792).

#### Landuse

**Create CSV Files**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_1030 <- read_excel(here(sm_1030_folder,
                                       "landuse_deluid_1030.xlsx"))

#write.csv(landuse_deluid_1030, here(sm_1030_folder,
#                                       "landuse_deluid_1030.csv"),
#          row.names = FALSE)
```

```{r}
sm_lu_1030_raw <- read.csv(here(sm_1030_folder, 
                                "landuse_sm_1030.csv"))

sm_deluid_1030 <- read.csv(here(sm_1030_folder, 
                                "landuse_deluid_1030.csv"))

unique(sm_lu_1030_raw$deluid)

sm_lu_1030_clean <- sm_lu_1030_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(sm_lu_1030_clean)
names(sm_deluid_1030)
intersect(names(sm_lu_1030_clean), names(sm_deluid_1030))

sm_lu_1030_join <- sm_lu_1030_clean |>
  left_join(sm_deluid_1030, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 1030)

nrow(sm_lu_1030_clean)
nrow(sm_lu_1030_join)

sum(is.na(sm_lu_1030_join[[names(sm_deluid_1030)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
sm_plot_1030 <- classify_landuse(sm_lu_1030_join) 
```

```{r}
# Summary Statistics 
lu_area_1030_sum <- sm_plot_1030 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Land Use Distribution Plot 
lu_1030_plot <- ggplot(lu_area_1030_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Rogers Park (Juri: 1030) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_1030_plot)

# Sediment Plot 
lu_1030_sed <- ggplot(lu_area_1030_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_1030_sed)


# Nitrogen Plot 
lu_1030_n <- ggplot(lu_area_1030_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", 
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")
print(lu_1030_n)


#Combined Plot 
combined_1030  <- (lu_1030_plot / lu_1030_sed / lu_1030_n) + plot_layout(ncol = 1)
ggsave(here(sm_1030_folder, "lu_plot_1030.png"), combined_1030, height = 12, width = 6, dpi = 300)
```

### 1077 - Exposition Park

Subbasin 1077 modeled for Exposition Park (Jurished: 107749, City: Los Angeles City, Acres: 10.394).

#### Landuse

**Create CSV Files**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_1077 <- read_excel(here(sm_1077_folder,
                                       "landuse_deluid_1077.xlsx"))

#write.csv(landuse_deluid_1077, here(sm_1077_folder,
#                                       "landuse_deluid_1077.csv"),
#          row.names = FALSE)
```

```{r}
sm_lu_1077_raw <- read.csv(here(sm_1077_folder, 
                                "landuse_sm_1077.csv"))

sm_deluid_1077 <- read.csv(here(sm_1077_folder, 
                                "landuse_deluid_1077.csv"))

unique(sm_lu_1077_raw$deluid)

sm_lu_1077_clean <- sm_lu_1077_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(sm_lu_1077_clean)
names(sm_deluid_1077)
intersect(names(sm_lu_1077_clean), names(sm_deluid_1077))

sm_lu_1077_join <- sm_lu_1077_clean |>
  left_join(sm_deluid_1077, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 1077)

nrow(sm_lu_1077_clean)
nrow(sm_lu_1077_join)

sum(is.na(sm_lu_1077_join[[names(sm_deluid_1077)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
sm_plot_1077 <- classify_landuse(sm_lu_1077_join) 
```

```{r}
# Summary Statistics 
lu_area_1077_sum <- sm_plot_1077 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Land Use Distribution Plot 
lu_1077_plot <- ggplot(lu_area_1077_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Exposition Park (Juri: 1077) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_1077_plot)

# Sediment Plot 
lu_1077_sed <- ggplot(lu_area_1077_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_1077_sed)


# Nitrogen Plot 
lu_1077_n <- ggplot(lu_area_1077_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", 
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")
print(lu_1077_n)


#Combined Plot 
combined_1077  <- (lu_1077_plot / lu_1077_sed / lu_1077_n) + plot_layout(ncol = 1)
ggsave(here(sm_1077_folder, "lu_plot_1077.png"), combined_1077, height = 12, width = 6, dpi = 300)
```

# School Recommendations

## Dominguez Channel Watershed

### 2034 - Gardena High School

Subbasin 2034 modeled for Gardena High School (Jurished: 203428, City: Gardena).

#### Landuse

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_2034 <- read_excel(here(dc_2034_folder,
                                       "landuse_deluid_2034.xlsx"))

write.csv(landuse_deluid_2034, here(dc_2034_folder,
                                       "landuse_deluid_2034.csv"),
          row.names = FALSE)

```

```{r}
# Dominguez Channel 2034 Landuse Data 
dc_lu_2034_raw <- read.csv(here(dc_2034_folder, 
                                "landuse_dc_2034.csv"))

# Dominguez Channel 2034 Delineation Data
dc_deluid_2034 <- read.csv(here(dc_2034_folder, 
                                "landuse_deluid_2034.csv"))

unique(dc_lu_2034_raw$deluid)

dc_lu_2034_clean <- dc_lu_2034_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(dc_lu_2034_clean)
names(dc_deluid_2034)
intersect(names(dc_lu_2034_clean), names(dc_deluid_2034))

dc_lu_2034_join <- dc_lu_2034_clean |>
  left_join(dc_deluid_2034, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 2034)

nrow(dc_lu_2034_clean)
nrow(dc_lu_2034_join)

sum(is.na(dc_lu_2034_join[[names(dc_deluid_2034)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
dc_plot_2034 <- classify_landuse(dc_lu_2034_join) 
```

```{r}
# Summarize the Average Annual data
lu_area_2034_sum <- dc_plot_2034 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Landuse Type Distribution Plot 
lu_2034_plot <- ggplot(lu_area_2034_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Gardena High School (Juri: 2034) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none",
        axis.title.x = element_blank())

print(lu_2034_plot)

# Sediment Loading Plot
lu_2034_sed <- ggplot(lu_area_2034_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none",
        axis.title.x = element_blank())

print(lu_2034_sed)


# Nitrogen Flux Plot
lu_2034_n <- ggplot(lu_area_2034_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Average Nitrogen Flux (lbs/year)",
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none")

print(lu_2034_n)

# Patchwork
combined_2034 <- (lu_2034_plot / lu_2034_sed /lu_2034_n) +
  plot_layout(ncol = 1)

print(combined_2034)

# Save
ggsave(here(dc_2034_folder, "lu_plot_2034.png"),
                           height = 12, width = 6, dpi = 300)

```

### 2088 - Narbonne High School

Subbasin 2088 modeled for Narbonne High School (Jurished: 208849, City: Harbor City).

#### **Landuse**

**Create CSV Files**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_2088 <- read_excel(here(dc_2088_folder,
                                       "landuse_deluid_2088.xlsx"))

#write.csv(landuse_deluid_2088, here(dc_2088_folder,
#                                       "landuse_deluid_2088.csv"),
#          row.names = FALSE)
```

```{r}
dc_lu_2088_raw <- read.csv(here(dc_2088_folder, "dc_2088",
                                "landuse_dc_2088.csv"))
dc_deluid_2088 <- read.csv(here(dc_2088_folder, "dc_2088",
                                "landuse_deluid_2088.csv"))

unique(dc_lu_2088_raw$deluid)

dc_lu_2088_clean <- dc_lu_2088_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(dc_lu_2088_clean)
names(dc_deluid_2088)
intersect(names(dc_lu_2088_clean), names(dc_deluid_2088))

dc_lu_2088_join <- dc_lu_2088_clean |>
  left_join(dc_deluid_2088, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 2088)

nrow(dc_lu_2088_clean)
nrow(dc_lu_2088_join)

sum(is.na(dc_lu_2088_join[[names(dc_deluid_2088)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
dc_plot_2088 <- classify_landuse(dc_lu_2088_join) 

```

### 2122 - San Pedro High School

Subbasin 2122 modeled for San Pedro High School (Jurished: 212249, City: San Pedro).

#### Landuse

**Create CSV Files**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_2122 <- read_excel(here(dc_2122_folder,
                                       "landuse_deluid_2122.xlsx"))

#write.csv(landuse_deluid_2122, here(dc_2122_folder,
#                                       "landuse_deluid_2122.csv"),
#          row.names = FALSE)
```

```{r}
dc_lu_2122_raw <- read.csv(here(dc_2122_folder, "landuse_dc_2122.csv"))
dc_deluid_2122 <- read.csv(here(dc_2122_folder, "dc_2122", "landuse_deluid_2122.csv"))

unique(dc_lu_2122_raw$deluid)

dc_lu_2122_clean <- dc_lu_2122_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(dc_lu_2122_clean)
names(dc_deluid_2122)
intersect(names(dc_lu_2122_clean), names(dc_deluid_2122))

dc_lu_2122_join <- dc_lu_2122_clean |>
  left_join(dc_deluid_2122, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 2122)

nrow(dc_lu_2122_clean)
nrow(dc_lu_2122_join)

sum(is.na(dc_lu_2122_join[[names(dc_deluid_2122)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
dc_plot_2122 <- classify_landuse(dc_lu_2122_join) 

```

```{r}
# Summarize the Average Annual data
lu_area_2122_sum <- dc_plot_2122 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Landuse Type Distribution Plot 
lu_2122_plot <- ggplot(lu_area_2122_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "San Pedro High School (Juri: 2122) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none",
        axis.title.x = element_blank())

print(lu_2122_plot)

# Sediment Loading Plot
lu_2122_sed <- ggplot(lu_area_2122_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none",
        axis.title.x = element_blank())

print(lu_2122_sed)


# Nitrogen Flux Plot
lu_2122_n <- ggplot(lu_area_2122_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Average Nitrogen Flux (lbs/year)",
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none")

print(lu_2122_n)

# Patchwork
combined_2122 <- (lu_2122_plot / lu_2122_sed / lu_2122_n) +
  plot_layout(ncol = 1)

print(combined_2122)

# Save
ggsave(here(dc_2122_folder, "lu_plot_2122.png"),
       height = 12, width = 6, dpi = 300)

```

## Los Angeles River Watershed

### 6873 - Birmingham Community Charter High School

Subbasin 6873 modeled for Birmingham Community Charter High School (Jurished: 687349, City: Van Nuys).

#### Landuse

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_6873 <- read_excel(here(lar_6873_folder,
                                       "landuse_deluid_6873.xlsx"))

#write.csv(landuse_deluid_6873, here(lar_6873_folder,
#                                       "landuse_deluid_6873.csv"),
#          row.names = FALSE)
```

```{r}
lar_lu_6873_raw <- read.csv(here(lar_6873_folder, 
                                 "landuse_lar_6873.csv"))
lar_deluid_6873 <- read.csv(here(lar_6873_folder,
                                 "landuse_deluid_6873.csv"))

unique(lar_lu_6873_raw$deluid)

lar_lu_6873_clean <- lar_lu_6873_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(lar_lu_6873_clean)
names(lar_deluid_6873)
intersect(names(lar_lu_6873_clean), names(lar_deluid_6873))

lar_lu_6873_join <- lar_lu_6873_clean |>
  left_join(lar_deluid_6873, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 6873)

nrow(lar_lu_6873_clean)
nrow(lar_lu_6873_join)

sum(is.na(lar_lu_6873_join[[names(lar_deluid_6873)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
lar_plot_6873 <- classify_landuse(lar_lu_6873_join) 

```

```{r}
# Summary Statistics 
lu_area_6387_sum <- lar_plot_6387 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Land Use Distribution Plot 
lu_6387_plot <- ggplot(lu_area_6387_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Birmingham Community Charter High School (Juri: 6387) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())

# Sediment Plot 
lu_6387_sed <- ggplot(lu_area_6387_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())

# Nitrogen Plot 
lu_6387_n <- ggplot(lu_area_6387_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", 
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")


#Combined Plot 
combined_6387 <- (lu_6387_plot / lu_6387_sed / lu_6387_n) + plot_layout(ncol = 1)
ggsave(here(lar_6387_folder, "lu_plot_6387.png"), combined_6387, height = 12, width = 6, dpi = 300)
```

### 6682 - Francis Polytechnic High School

Subbasin 6682 modeled for Francis Polytechnic High School (Jurished: 668249, City: Sun Valley).

#### Landuse

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_6682 <- read_excel(here(lar_6682_folder,
                                       "landuse_deluid_6682.xlsx"))

#write.csv(landuse_deluid_6682, here(lar_6682_folder,
#                                       "landuse_deluid_6682.csv"),
#          row.names = FALSE)
```

```{r}
lar_lu_6682_raw <- read.csv(here(lar_6682_folder, 
                                 "landuse_lar_6682.csv"))
lar_deluid_6682 <- read.csv(here(lar_6682_folder, "lar_6682",
                                 "landuse_deluid_6682.csv"))

unique(lar_lu_6682_raw$deluid)

lar_lu_6682_clean <- lar_lu_6682_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(lar_lu_6682_clean)
names(lar_deluid_6682)
intersect(names(lar_lu_6682_clean), names(lar_deluid_6682))

lar_lu_6682_join <- lar_lu_6682_clean |>
  left_join(lar_deluid_6682, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 6682)

nrow(lar_lu_6682_clean)
nrow(lar_lu_6682_join)

sum(is.na(lar_lu_6682_join[[names(lar_deluid_6682)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
lar_plot_6682 <- classify_landuse(lar_lu_6682_join) 

```

```{r}
# Summary Statistics 
lu_area_6682_sum <- lar_plot_6682 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Land Use Distribution Plot 
lu_6682_plot <- ggplot(lu_area_6682_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Francis Polytechnic High School (Juri: 6682) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())

# Sediment Plot 
lu_6682_sed <- ggplot(lu_area_6682_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())

# Nitrogen Plot 
lu_6682_n <- ggplot(lu_area_6682_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", 
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")

# Combined Plot 
combined_6682 <- (lu_6682_plot / lu_6682_sed / lu_6682_n) + plot_layout(ncol = 1)
ggsave(here(lar_6682_folder, "lu_plot_6682.png"), combined_6682, height = 12, width = 6, dpi = 300)

```

### 6697 - San Fernando High School

Subbasin 6697 modeled for San Fernando High School (Jurished: 669749, City: San Fernando).

#### Landuse

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_6697 <- read_excel(here(lar_6697_folder,
                                       "landuse_deluid_6697.xlsx"))

#write.csv(landuse_deluid_6697, here(lar_6697_folder,
#                                       "landuse_deluid_6697.csv"),
#          row.names = FALSE)
```

```{r}
lar_lu_6697_raw <- read.csv(here(lar_6697_folder, 
                                 "landuse_lar_6697.csv"))
lar_deluid_6697 <- read.csv(here(lar_6697_folder,
                                 "landuse_deluid_6697.csv"))

unique(lar_lu_6697_raw$deluid)

lar_lu_6697_clean <- lar_lu_6697_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(lar_lu_6697_clean)
names(lar_deluid_6697)
intersect(names(lar_lu_6697_clean), names(lar_deluid_6697))

lar_lu_6697_join <- lar_lu_6697_clean |>
  left_join(lar_deluid_6697, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 6697)

nrow(lar_lu_6697_clean)
nrow(lar_lu_6697_join)

sum(is.na(lar_lu_6697_join[[names(lar_deluid_6697)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
lar_plot_6697 <- classify_landuse(lar_lu_6697_join) 
```

```{r}
# Summary Statistics 
lu_area_6697_sum <- lar_plot_6697 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Land Use Distribution Plot 
lu_6697_plot <- ggplot(lu_area_6697_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "San Fernando High School (Juri: 6697) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())

# Sediment Plot 
lu_6697_sed <- ggplot(lu_area_6697_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())

# Nitrogen Plot 
lu_6697_n <- ggplot(lu_area_6697_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", 
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")

# Combined Plot 
combined_6697 <- (lu_6697_plot / lu_6697_sed / lu_6697_n) + plot_layout(ncol = 1)
ggsave(here(lar_6697_folder, "lu_plot_6697.png"), combined_6697, height = 12, width = 6, dpi = 300)

```

### 6925 - Cleveland Charter High School

Subbasin 6925 modeled for Cleveland Charter High School (Jurished: 692549, City: Reseda).

#### Landuse

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_6925 <- read_excel(here(lar_6925_folder,
                                       "landuse_deluid_6925.xlsx"))

#write.csv(landuse_deluid_6925, here(lar_6925_folder,
#                                       "landuse_deluid_6925.csv"),
#          row.names = FALSE)
```

```{r}
lar_lu_6925_raw <- read.csv(here(lar_6925_folder, 
                                 "landuse_lar_6925.csv"))
lar_deluid_6925 <- read.csv(here(lar_6925_folder,
                                 "landuse_deluid_6925.csv"))

unique(lar_lu_6925_raw$deluid)

lar_lu_6925_clean <- lar_lu_6925_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(lar_lu_6925_clean)
names(lar_deluid_6925)
intersect(names(lar_lu_6925_clean), names(lar_deluid_6925))

lar_lu_6925_join <- lar_lu_6925_clean |>
  left_join(lar_deluid_6925, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 6925)

nrow(lar_lu_6925_clean)
nrow(lar_lu_6925_join)

sum(is.na(lar_lu_6925_join[[names(lar_deluid_6925)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
lar_plot_6925 <- classify_landuse(lar_lu_6925_join) 
```

```{r}
# Summary Statistics 
lu_area_6925_sum <- lar_plot_6925 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Land Use Distribution Plot 
lu_6925_plot <- ggplot(lu_area_6925_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Cleveland Charter High School (Juri: 6925) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())

# Sediment Plot 
lu_6925_sed <- ggplot(lu_area_6925_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())

# Nitrogen Plot 
lu_6925_n <- ggplot(lu_area_6925_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", 
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")

# Combined Plot 
combined_6925 <- (lu_6925_plot / lu_6925_sed / lu_6925_n) + plot_layout(ncol = 1)
ggsave(here(lar_6925_folder, "lu_plot_6925.png"), combined_6925, height = 12, width = 6, dpi = 300)

```

## Santa Monica Watershed

### 1067 - Crenshaw High School STEMM Magnet

Subbasin 1067 modeled for Crenshaw High School STEMM Magnet (Jurished: 106749, City: Los Angeles).

#### Landuse

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_1067 <- read_excel(here(sm_1067_folder,
                                       "landuse_deluid_1067.xlsx"))

write.csv(landuse_deluid_1067, here(sm_1067_folder,
                                       "landuse_deluid_1067.csv"),
          row.names = FALSE)
```

```{r}
sm_lu_1067_raw <- read.csv(here(sm_1067_folder, 
                                "landuse_sm_1067.csv"))
sm_deluid_1067 <- read.csv(here(sm_1067_folder, "sm_1067",
                                "landuse_deluid_1067.csv"))

unique(sm_lu_1067_raw$deluid)

sm_lu_1067_clean <- sm_lu_1067_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(sm_lu_1067_clean)
names(sm_deluid_1067)
intersect(names(sm_lu_1067_clean), names(sm_deluid_1067))

sm_lu_1067_join <- sm_lu_1067_clean |>
  left_join(sm_deluid_1067, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 1067)

nrow(sm_lu_1067_clean)
nrow(sm_lu_1067_join)

sum(is.na(sm_lu_1067_join[[names(sm_deluid_1067)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
sm_plot_1067 <- classify_landuse(sm_lu_1067_join) 
```

```{r}
# Summary Statistics 
lu_area_1067_sum <- sm_plot_1067 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Land Use Distribution Plot 
lu_1067_plot <- ggplot(lu_area_1067_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Crenshaw High School (Juri: 1067) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_1067_plot)

# Sediment Plot 
lu_1067_sed <- ggplot(lu_area_1067_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_1067_sed)


# Nitrogen Plot 
lu_1067_n <- ggplot(lu_area_1067_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", 
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")
print(lu_1067_n)


#Combined Plot 
combined_1067  <- (lu_1067_plot / lu_1067_sed / lu_1067_n) + plot_layout(ncol = 1)
ggsave(here(sm_1067_folder, "lu_plot_1067.png"), combined_1067, height = 12, width = 6, dpi = 300)
```

### 1110 - Kennedy Community of Schools

Subbasin 1110 modeled for Kennedy Community of Schools (Jurished: 111049, City: Los Angeles).

#### Landuse

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_1110 <- read_excel(here(sm_1110_folder,
                                       "landuse_deluid_1110.xlsx"))

#write.csv(landuse_deluid_1110, here(sm_1110_folder,
#                                       "landuse_deluid_1110.csv"),
#          row.names = FALSE)
```

```{r}

sm_lu_1110_raw <- read.csv(here(sm_1110_folder, 
                                "landuse_sm_1110.csv"))
sm_deluid_1110 <- read.csv(here(sm_1110_folder, 
                                "landuse_deluid_1110.csv"))

unique(sm_lu_1110_raw$deluid)

sm_lu_1110_clean <- sm_lu_1110_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(sm_lu_1110_clean)
names(sm_deluid_1110)
intersect(names(sm_lu_1110_clean), names(sm_deluid_1110))

sm_lu_1110_join <- sm_lu_1110_clean |>
  left_join(sm_deluid_1110, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 1110)

nrow(sm_lu_1110_clean)
nrow(sm_lu_1110_join)

sum(is.na(sm_lu_1110_join[[names(sm_deluid_1110)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
sm_plot_1110 <- classify_landuse(sm_lu_1110_join) 
```

```{r}
# Summary Statistics 
lu_area_1110_sum <- sm_plot_1110 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Land Use Distribution Plot 
lu_1110_plot <- ggplot(lu_area_1110_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Kennedy Community of Schools (Juri: 1110) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_1110_plot)

# Sediment Plot 
lu_1110_sed <- ggplot(lu_area_1110_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_1110_sed)


# Nitrogen Plot 
lu_1110_n <- ggplot(lu_area_1110_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", 
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")
print(lu_1110_n)


#Combined Plot 
combined_1110  <- (lu_1110_plot / lu_1110_sed / lu_1110_n) + plot_layout(ncol = 1)
ggsave(here(sm_1110_folder, "lu_plot_1110.png"), combined_1110, height = 12, width = 6, dpi = 300)
```

### 1061 - Dorsey High School

Subbasin 1061 modeled for Dorsey High School (Jurished: 106149, City: Los Angeles).

#### Landuse

**Create CSV File**

```{r}
# Read the delineation excel sheet and convert to csv
landuse_deluid_1061 <- read_excel(here(sm_1061_folder,
                                       "landuse_deluid_1061.xlsx"))

#write.csv(landuse_deluid_1061, here(sm_1061_folder,
#                                       "landuse_deluid_1061.csv"),
#          row.names = FALSE)
```

```{r}
sm_lu_1061_raw <- read.csv(here(sm_1061_folder, 
                                "landuse_sm_1061.csv"))

sm_deluid_1061 <- read.csv(here(sm_1061_folder, 
                                "landuse_deluid_1061.csv"))

unique(sm_lu_1061_raw$deluid)

sm_lu_1061_clean <- sm_lu_1061_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1)

names(sm_lu_1061_clean)
names(sm_deluid_1061)
intersect(names(sm_lu_1061_clean), names(sm_deluid_1061))

sm_lu_1061_join <- sm_lu_1061_clean |>
  left_join(sm_deluid_1061, by = c("subbasin", "deluid")) |>
  clean_names() |>
  filter(subbasin == 1061)

nrow(sm_lu_1061_clean)
nrow(sm_lu_1061_join)

sum(is.na(sm_lu_1061_join[[names(sm_deluid_1061)[3]]]))

# Categorize the delineations into main classes for easier data manipulation
sm_plot_1061 <- classify_landuse(sm_lu_1061_join) 
```

```{r}
# Summary Statistics 
lu_area_1061_sum <- sm_plot_1061 |>
  group_by(main_class) |>
  summarise(total_area = sum(area, na.rm = TRUE),
            total_avg_sed = sum(sedload, na.rm = TRUE),
            total_avg_n = sum(po_tn, na.rm = TRUE))

# Land Use Distribution Plot 
lu_1061_plot <- ggplot(lu_area_1061_sum, aes(x = main_class, y = total_area, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(x = "Land Use", y = "Total Area (acres)", 
       title = "Kennedy Community of Schools (Juri: 1061) Land Use Distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_1061_plot)

# Sediment Plot 
lu_1061_sed <- ggplot(lu_area_1061_sum, aes(x = main_class, y = total_avg_sed, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Sediment (tons/year)", 
       title = "Average Sediment Loading 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        legend.position = "none", 
        axis.title.x = element_blank())
print(lu_1061_sed)


# Nitrogen Plot 
lu_1061_n <- ggplot(lu_area_1061_sum, aes(x = main_class, y = total_avg_n, fill = main_class)) +
  geom_col() +
  scale_fill_manual(values = landuse_colors) +
  labs(y = "Average Nitrogen Flux (lbs/year)", 
       title = "Average Nitrogen Flux 2008-2018") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")
print(lu_1061_n)


#Combined Plot 
combined_1061  <- (lu_1061_plot / lu_1061_sed / lu_1061_n) + plot_layout(ncol = 1)
ggsave(here(sm_1061_folder, "lu_plot_1061.png"), combined_1061, height = 12, width = 6, dpi = 300)
```

## San Gabriel Watershed

No schools were selected as a recommendation for the San Gabriel watershed.
