---
title: "wmms_clean_data"
format: 
 html:
    embed-resources: true
    code-line-numbers: true
    code-wrap: true
    code-fold: true
    toc: true
author: Tina Tran 
editor: visual
---

## WMMS Clean Data

**Load Libraries**

```{r, warning = FALSE, message = FALSE}
# Load library 
library(tidyverse)
library(here)
library(janitor)
library(ggplot2)
library(dplyr)
library(stringr)
```

# San Gabriel

## Jurished: 5120 (New River Park)

[**Parameters for Jurished Data:**]{.underline}\
TT This output file was created at 06:16:55pm on 02/10/2026\
TT Time interval: 60 min Output option: day\
TT Label\
**TT PREC precipitation (rain + snow) volume (in-acre/day)\
TT SURO surface outflow volume (in-acre/day)**\
TT IFWO interflow outflow volume (in-acre/day)\
TT AGWO groundwater outflow volume (in-acre/day)\
TT PERO total outflow rate volume (SURO+IFWO+AGWO) (in-acre/day)\
TT DEP stream depth (ft)\
TT AVDEP stream average depth (ft)\
TT TAU bed shear stress (kg/m\^2)\
TT RO total rate of outflow from RCHRES (cfs)\
**TT SOSED sediments load from land (english tons/day)**\
TT SSEDOUT1 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT2 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT3 suspended sediment concentration in outflow from the RCHRES (mg/l)\
TT SSEDOUT total suspended solid concentration in outflow from the RCHRES (mg/l)\
TT POQUAL1 total flux of QUAL from the PLS_TN (lb/day)\
TT POQUAL2 total flux of QUAL from the PLS_TP (lb/day)\
TT POQUAL3 total flux of QUAL from the PLS_TCd (lb/day)\
TT POQUAL4 total flux of QUAL from the PLS_TCu (lb/day)\
TT POQUAL5 total flux of QUAL from the PLS_TPb (lb/day)\
TT POQUAL6 total flux of QUAL from the PLS_TZn (lb/day)\
**TT CONC1 TN dissolved concentration (average) in RCHRES (mg/l)\
TT CONC2 TP dissolved concentration (average) in RCHRES (mg/l)**\
TT CONC3 TCd dissolved concentration (average) in RCHRES (ug/l)\
TT CONC4 TCu dissolved concentration (average) in RCHRES (ug/l)\
TT CONC5 TPb dissolved concentration (average) in RCHRES (ug/l)\
TT CONC6 TZn dissolved concentration (average) in RCHRES (ug/l)

### Loading

[**Goal:**]{.underline} Estimate the total average annual loading for sediment, nitrogen, runoff volume (total surface outflow rate \* areas)

```{r}


```

### **Landuse Based on Area for 5120**

The delineations used for this model include 96 types to calculate the average area based on landuse from 2008-2018 using input data from 2006-2018. We will group the delineations based on major land use types: road, developed, agriculture, vegetation, and water before plotting the data and analysis.

[**Goal**]{.underline}: Understand how much total average area in acres is distributed in this jurished based on landuse type.

```{r, warning = FALSE, message = FALSE}
# San Gabriel Landuse Data 
sg_lu_5120_raw <- read.csv(here("data", "wmms", "sg_5120", "landuse_sg_5120.csv"))

# San Gabriel Delineation Data for Landuse
sg_deluid_5120 <- read.csv(here("data", "wmms","sg_5120", "landuse_deluid_5120.csv"))


#Check the data
unique(sg_lu_5120_raw$deluid) #total of 96

# Pivot the long table
sg_lu_5120_clean <- sg_lu_5120_raw |>
  pivot_wider(id_cols = c(subbasin, deluid),
              names_from = parmname,
              values_from = value1) 
head(sg_lu_5120_clean)


# Check shared names prior to joining 
names(sg_lu_5120_clean)
names(sg_deluid_5120)
intersect(names(sg_lu_5120_clean), names(sg_deluid_5120))


# Join Tables 
sg_lu_5120_join <- sg_lu_5120_clean |>
  left_join(sg_deluid_5120, by = c("subbasin", "deluid"))


# Check number of rows 
nrow(sg_lu_5120_clean)
nrow(sg_lu_5120_join)

sum(is.na(sg_lu_5120_join[[names(sg_deluid_5120)[3]]]))
```

```{r}
# Categorize the delineations into main classes for easier data manipulation
sg_plot_5120 <- sg_lu_5120_join |>
  mutate(main_class = str_extract(deluname, "^[^_-]+"))
 # summarise(total_volume = area_ac*
```

```{r}
# Summarize the data
lu_area_5120_sum <- sg_plot_5120 |>
  group_by(main_class) |>
  summarise(total_area = sum(AREA, na.rm = TRUE),
            total_avg_sed = sum(SEDLOAD, na.rm = TRUE),
            total_avg_n = sum(PO_TN, na.rm = TRUE))

# Landuse Type Distribution Plot 
lu_5120_plot <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_area)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Area (acres)", 
       title = "Jurished 5120 Landuse Distribution") +
  theme_minimal()

print(lu_5120_plot)

# Sediment Loading Plot
lu_5120_sed <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_avg_sed)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Sediment (tons/year)", 
       title = "Jurished 5120 Average Sediment Loading 2008-2018") +
  theme_minimal()
print(lu_5120_sed)


# Nitrogen FLux Plot
lu_5120_n <- ggplot(lu_area_5120_sum, aes(x = main_class, y = total_avg_n)) +
  geom_col() +
  labs(x = "Land Use Type", y = "Total Average Nitrogen Flux (lbs/year)", 
       title = "Jurished 5120 Average Nitrogen Flux 2008-2018") +
  theme_minimal()
print(lu_5120_n)

```
